### 2021-04-19 doc/paper/paper.tex
added documentation dir

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai21.sty is NOT the same than previous years'
\usepackage{ijcai21}

% Use the postscript times font!
\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{stmaryrd}
\urlstyle{same}

% our packages
\usepackage{amssymb}
\usepackage{environ}
\usepackage{tabularx}
% \usepackage{todonotes}
% \presetkeys{todonotes}{inline}{}
\usepackage{pgfplotstable}
\usepackage{amsmath}
\usepackage{enumitem}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{example}{Example}

\usepackage{comment}

% Some useful macros
%\newcommand{\rednote}[1]{\footnote{\color{red}{*** #1 ***}}}
\newcommand{\inlinecite}[1]{\citeauthor{#1}~(\citeyear{#1})}
%\newcommand{\citealp}[1]{\citeauthor{#1}~\citeyear{#1}}

%\newcommand{\predicates}[1]{\ensuremath{P(#1)}}
\newcommand{\atoms}{\ensuremath{\mathcal{H}}}
\newcommand{\actions}[1]{\ensuremath{A(#1)}}
\newcommand{\objects}[1]{\ensuremath{O(#1)}}
\newcommand{\initial}[1]{\ensuremath{I(#1)}}
\newcommand{\goal}[1]{\ensuremath{G(#1)}}
%\newcommand{\states}[1]{\ensuremath{S(#1)}}
\newcommand{\free}[1]{\ensuremath{\mathrm{free}(#1)}}
\newcommand{\vars}{\ensuremath{\mathrm{vars}}}
\newcommand{\pre}{\ensuremath{\textit{pre}}}
\newcommand{\add}{\ensuremath{\textit{add}}}
\newcommand{\del}{\ensuremath{\textit{del}}}
\newcommand{\effs}{\ensuremath{\mathrm{effs}}}
\newcommand{\states}{\ensuremath{\mathcal{S}}}
\newcommand{\transitions}{\ensuremath{\mathcal{T}}}
\newcommand{\dl}{\ensuremath{\mathcal{DL}}}
\newcommand{\labels}{L}
\newcommand{\goals}{S_G}
\newcommand{\init}{s_I}
\newcommand{\constants}{{\mathcal C}}
\newcommand{\predicates}{{\mathcal P}}
\newcommand{\Q}{\ensuremath{\mathcal Q}}
\newcommand{\successors}{\textit{succ}}
\newcommand{\dlmodel}{\mathcal M}
\newcommand{\featurespace}{\mathcal{F}}
\newcommand{\featurepool}{\ensuremath{F}}
\newcommand{\complexity}{\mathcal K}
\newcommand{\mli}[1]{\ensuremath{\textit{#1}}}
\newcommand{\dist}{\textit{dist}}
\newcommand{\training}{\ensuremath{\mathbb{T}}}
\newcommand{\apply}[1]{\ensuremath{\llbracket #1\rrbracket}}
\newcommand{\msat}{Max-SAT}

\usepackage{ textcomp }

%\hypersetup{draft}

\newcommand{\tup}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\tuple}[1]{\tup{#1}}  % Just an alias
\newcommand{\set}[1]{\ensuremath{\left\{#1 \right\}}}
\newcommand{\setst}[2]{\ensuremath{\left\{#1 \mid #2 \right\}}}

\newcommand{\pplus}{\raisebox{.15ex}{\footnotesize$\uparrow$}}
\newcommand{\mminus}{\raisebox{.15ex}{\footnotesize$\downarrow$}}
\newcommand{\nils}{\raisebox{.15ex}{$\textdegree$}}

% \newcommand{\wip}[1]{{\color{red} #1}}  % From "work in progress" :-)
% \newcommand{\gfm}[1]{\footnote{\color{red}{[Guillem] #1}}}
% \newcommand{\F}{\ensuremath{\mathcal{F}}}
% \renewcommand{\S}{\mathcal{S}}
% \newcommand{\G}{\mathcal{G}}

% the following package is optional:
%\usepackage{latexsym}

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.

%PDF Info Is REQUIRED.
\pdfinfo{
/TemplateVersion (IJCAI.2021.0)
}

\title{Learning Generalized Policies Over Grid Environments}

% \title{General Polizy Learner for Grid Environments}

\author{

}

% Papers must be no longer than 7 pages in total: 6 pages for the body of the paper (including all figures/tables),
% plus up to 1 additional page with references
\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

\section{Logic Language}

The Grid Domains share the set of Objects \textit{O}, and the set of predicates \textit{P}.

\subsection{Objects}

All objects in \textit{O} belong to one sort, \textit{cell}. Then, we have an object \textit{o} for each cell in the grid. For instance, in a grid of size $i \times j$ the set \textit{O} contains the object \textit{cij}, representing the cell in the row \textit{i} and the column \textit{j}.

\subsection{Predicates}

To explain the predicates it is good to remember that each of the domains has different values contained in the grid, e.g. the domain reach-for-the-star has five possible values for each cell in the grid, which are: Empty, drawn, agent, star, right-arrow, and left-arrow. Then, let us define that for each domain there is a set of values \textit{V} which represents the values that each cell object in the grid can take. It is also good to remember the difference between static and dynamic predicates. Then, the static predicates are always the same for any state of an instance, while a dynamic predicate will change depending on the state of the instance. \textit{P} will contain both types of predicates, dynamic and static.\\

We have used the dynimic predicates to define the value of \textit{V} that any object \textit{o} can take at a given time. While we have used the static predicates to define the topology of the grid, i.e., the relative position of o with respect to o'. It is important to note that it is always preferable to have a static predicate rather than a dynamic one as this will considerably reduce the problem of the combinatorial explosion of symbols [some reference]. Finally, we define a set of relative directions \textit{D}, which contains \{right, left, down, up, right-up, right-down, left-down, left-up, horizontal, vertical\}. Then, \textit{D} is used to define the topology of the grid.\\

Then, \textit{P} contains:

\subsubsection{Dynamic predicates:}

\begin{itemize}

\item \textit{v(cij)}: Means that cell \textit{o} has the value \textit{v} at a certain time. Recall that v is a concrete value within the set \textit{V}. For instance, if \textit{v} is equalt to the value \textit{agent}, then \textit{agent(cij)} means that cell \textit{cij} has the value agent.
\item \textit{player(n)}: This is predicate used for multiplayer games where $n \in \mathbb N$, and represents the player whose turn it is this turn. For instance, the predicate \textit{player(0)} means that in a specific state is the turn of the player \textit{0}.

\end{itemize}

\subsubsection{Static predicates:}

\begin{itemize}

\item \textit{d(o, o')}: means that \textit{o} has \textit{o'} as contiguous in direction d. For example: \textit{right(cij, cij')} means that to the adjacent right of cell \textit{cij} is the cell \textit{cij'}. Notice that some directions of \textit{D} are redundan, e.g., the predicate \textit{horizontal(cij, cij')} means that to the adjacent right o left of cell \textit{cij} is the cell \textit{cij'}, and could be defined combining two of the other predicates like $\textit{right(cij, cij')} \lor \textit{left(cij, cij')}$. In a similar way \textit{vertical(cij, cij')} can be defined as $\textit{up(cij, cij')} \lor \textit{down(cij, cij')}$. Furthermore, some directions like \textit{left(cij, cij')} are also redundant, since can be redefined as the invers of its opposite direction like \textit{right(cij', cij)}. This redundancy will increase the number of possible features according to the grammar, however it will also reduce the complexity of the features.

\item \textit{same-row(o, o')}: Means that \textit{o} is in the same row as \textit{o'}. For example: \textit{same-row(cij, cij')} means that cell \textit{cij} is in the same row as cell \textit{cij'}, the row \textit{i}.

\item \textit{same-col(o, o')}: Means that \textit{o} is in the same column as \textit{o'}. For example: \textit{same-col(cij, ci'j)} means that cell \textit{cij} is in the same column as cell \textit{ci'j}, the column \textit{j}.

\end{itemize}

\subsection{Encodings}

\subsubsection{FOND Adversarial}

\subsubsection{Main Variables}
\begin{itemize}
 \item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.

 \item $V(s, d)$ for $s$ alive, and $d \in [0, D]$, where $D = \max_{s} \delta \cdot V^*(s)$,
 with intended denotation $V(s)=d$.
 Note that for states $s$ that are a goal, we know $V(s)=0$,
 and for states $s$ that are unsolvable, we know that $V(s) \neq d$ for all $d$.
 Thus, we can restrict SAT variables $V(s, d)$ to those states $s$ that are alive.

 \item $Select(f)$, for each feature $f$ in the feature pool.
\end{itemize}

%\subsubsection{Auxiliary Variables}
%\begin{itemize}
% \item We'll use $GV(s, s', d)$ to denote that $Good(s, s')$ and $V(s') \leq d$. This is enforced with the constraint
% $GV(s, s', d) \rightarrow Good(s, s') \land V(s') \leq d$ for $s, s'$ alive, $(s, s') \not\in \badtx$, $d \in [0, D)$.
% The other direction of the implication is not necessary.
%\end{itemize}

\subsection{Hard Constraints}

\smallpar{C1}
The policy has to be complete with respect to all alive states:
\begin{align}
\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
\end{align}

\smallpar{C2} $V$ is always descending along Good transitions:
\begin{align}
 Good(s, s') \land V(s', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $d \in [1, D)$.} \\
 V(s', D) \rightarrow \neg Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$.} \tag{\theequation${}^\prime$}
\end{align}

%\smallpar{C4-5} Any upper bound on $V(s)$ (for $s$ not a goal) needs to be justified:
%\begin{align}
% V(s) \leq d+1 \rightarrow \bigvee_{\substack{
% s' \text{ goal child of } s\\
% (s, s') \not\in \badtx}} Good(s, s') \lor
% \bigvee_{\substack{
% s' \text{ alive child of } s\\
% (s, s') \not\in \badtx}} GV(s, s', d),&
% \;\; \text{for $s$ alive, $d \in [0, D)$.} \\
% \neg V(s) \leq 0,&\;\; \text{for $s$ not a goal.}
%\end{align}

\smallpar{C3-4}
Variables $V(s, d)$ define a function that is total over the set of alive states,
and such that $V(s)$ is within lower bound $V^*(s)$ and upper bound $\delta \cdot V^*(s)$:
\begin{align}
 \bigvee_{V^*(s) \leq d \leq \delta \cdot V^*(s)} V(s,d),&\;\; \text{for $s$ alive.} \\
 \neg V(s, d) \lor \neg V(s, d')&\;\; \text{for $s$ alive, $1 \leq d < d' \leq D$.}
\end{align}

\smallpar{C5-6}
Good transitions can be distinguished from bad transitions.
Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
of two different equivalence classes such that $(s, s') \not\in \badtx$
(which implies that $s'$ is solvable). Then,

\begin{align}
 Good(s, s') \rightarrow Good(t, t') \lor
 Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
 Good(s, s') \rightarrow
 Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
\end{align}

\noindent where $Dist(s, s', t, t')$ is shorthand for $\bigvee_{f \in D1\&2(s, s', t, t')} Select(f)$.

\smallpar{C7 (Optional)}
Goals are distinguishable from non-goals.
\begin{align}
\bigvee_{f \in D1(s, s')} Select(f),&\;\; \text{for $s$ goal, $s$ not a goal}
\end{align}

\smallpar{C8 (Optional)}
All selected features need to have some Good transition that takes them to $0$:
\begin{align}
 Selected(f) \rightarrow \bigvee_{(s, s') \in Z(f)} Good(s, s'),&\;\; \text{for $f$ in pool}
\end{align}

\noindent where $Z(f)$ is the set transitions starting in an alive state that change the denotation of $f$ from something
larger than 0 to 0.

\subsection{Soft Constraints}
We simply post a constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.

% ... End

%\section*{Acknowledgments}

%% The file named.bst is a bibliography style file for BibTeX 0.99c
\small
\bibliographystyle{named}
\bibliography{abbrv-short,literatur,references,crossref-short}

\end{document}

### 2021-04-19 doc/paper/paper.tex
encodings updated

@@
-\documentclass{article}
-\pdfpagewidth=8.5in
-\pdfpageheight=11in
-% The file ijcai21.sty is NOT the same than previous years'
-\usepackage{ijcai21}
+\documentclass[a4paper]{article}
+%\def\year{2020}\relax
+%\usepackage{aaai20}  % DO NOT CHANGE THIS
+\usepackage{times}  % DO NOT CHANGE THIS
+\usepackage{helvet} % DO NOT CHANGE THIS
+\usepackage{courier}  % DO NOT CHANGE THIS
+\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
+\urlstyle{rm} % DO NOT CHANGE THIS
+\def\UrlFont{\rm}  % DO NOT CHANGE THIS
+\frenchspacing  % DO NOT CHANGE THIS
+%\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
+%\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
 
-% Use the postscript times font!
-\usepackage{times}
-\usepackage{soul}
-\usepackage{url}
-\usepackage[hidelinks]{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage[small]{caption}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{booktabs}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{stmaryrd}
-\urlstyle{same}
+\usepackage[margin=1in]{geometry}
 
 % our packages
+\usepackage{amsthm}
+\usepackage{amsmath}
 \usepackage{amssymb}
-\usepackage{environ}
-\usepackage{tabularx}
-% \usepackage{todonotes}
-% \presetkeys{todonotes}{inline}{}
-\usepackage{pgfplotstable}
-\usepackage{amsmath}
-\usepackage{enumitem}
-
-\newtheorem{definition}{Definition}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{example}{Example}
-
-\usepackage{comment}
+%\usepackage{bm}
+\usepackage{booktabs}
+%\usepackage[inline]{enumitem}
+%\usepackage{mathtools}
+%\usepackage{multirow}
+%\usepackage[mode=buildnew,subpreambles=true]{standalone}
+\usepackage{subcaption}
+%\usepackage{todonotes}
+\usepackage[table]{xcolor}  % TODO Comment out for final submission
+%\usepackage{pgfplots}
+%\usepackage{tikz}
+\usepackage{natbib}
+\usepackage{fancyvrb}
 
 % Some useful macros
-%\newcommand{\rednote}[1]{\footnote{\color{red}{*** #1 ***}}}
-\newcommand{\inlinecite}[1]{\citeauthor{#1}~(\citeyear{#1})}
+%\newcommand{\inlinecite}[1]{\citeauthor{#1}~(\citeyear{#1})}
 %\newcommand{\citealp}[1]{\citeauthor{#1}~\citeyear{#1}}
 
-%\newcommand{\predicates}[1]{\ensuremath{P(#1)}}
-\newcommand{\atoms}{\ensuremath{\mathcal{H}}}
-\newcommand{\actions}[1]{\ensuremath{A(#1)}}
-\newcommand{\objects}[1]{\ensuremath{O(#1)}}
-\newcommand{\initial}[1]{\ensuremath{I(#1)}}
-\newcommand{\goal}[1]{\ensuremath{G(#1)}}
-%\newcommand{\states}[1]{\ensuremath{S(#1)}}
+\newcommand{\smallpar}[1]{{\vspace{10pt}\noindent \bf #1.}}
+
 \newcommand{\free}[1]{\ensuremath{\mathrm{free}(#1)}}
 \newcommand{\vars}{\ensuremath{\mathrm{vars}}}
-\newcommand{\pre}{\ensuremath{\textit{pre}}}
-\newcommand{\add}{\ensuremath{\textit{add}}}
-\newcommand{\del}{\ensuremath{\textit{del}}}
+\newcommand{\pre}{\ensuremath{\mathrm{pre}}}
+\newcommand{\add}{\ensuremath{\mathrm{add}}}
+\newcommand{\del}{\ensuremath{\mathrm{del}}}
 \newcommand{\effs}{\ensuremath{\mathrm{effs}}}
-\newcommand{\states}{\ensuremath{\mathcal{S}}}
-\newcommand{\transitions}{\ensuremath{\mathcal{T}}}
-\newcommand{\dl}{\ensuremath{\mathcal{DL}}}
-\newcommand{\labels}{L}
-\newcommand{\goals}{S_G}
-\newcommand{\init}{s_I}
-\newcommand{\constants}{{\mathcal C}}
-\newcommand{\predicates}{{\mathcal P}}
-\newcommand{\Q}{\ensuremath{\mathcal Q}}
-\newcommand{\successors}{\textit{succ}}
-\newcommand{\dlmodel}{\mathcal M}
-\newcommand{\featurespace}{\mathcal{F}}
-\newcommand{\featurepool}{\ensuremath{F}}
-\newcommand{\complexity}{\mathcal K}
-\newcommand{\mli}[1]{\ensuremath{\textit{#1}}}
-\newcommand{\dist}{\textit{dist}}
-\newcommand{\training}{\ensuremath{\mathbb{T}}}
-\newcommand{\apply}[1]{\ensuremath{\llbracket #1\rrbracket}}
-\newcommand{\msat}{Max-SAT}
-
-\usepackage{ textcomp }
-
-%\hypersetup{draft}
 
@@
 
-\newcommand{\pplus}{\raisebox{.15ex}{\footnotesize$\uparrow$}}
-\newcommand{\mminus}{\raisebox{.15ex}{\footnotesize$\downarrow$}}
-\newcommand{\nils}{\raisebox{.15ex}{$\textdegree$}}
+\newtheorem{definition}{Definition}
+\newtheorem{definitionandtheorem}[definition]{Definition and Theorem}
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{lemma}[definition]{Lemma}
+\newtheorem{proposition}[definition]{Proposition}
+\newtheorem{corollary}[definition]{Corollary}
+\newtheorem{example}[definition]{Example}
 
-% \newcommand{\wip}[1]{{\color{red} #1}}  % From "work in progress" :-)
-% \newcommand{\gfm}[1]{\footnote{\color{red}{[Guillem] #1}}}
-% \newcommand{\F}{\ensuremath{\mathcal{F}}}
-% \renewcommand{\S}{\mathcal{S}}
-% \newcommand{\G}{\mathcal{G}}
+\newcommand{\wip}[1]{{\color{red} #1}}  % From "work in progress" :-)
+\newcommand{\gfm}[1]{\footnote{\color{red}{[Guillem] #1}}}
 
-% the following package is optional:
-%\usepackage{latexsym}
+\newcommand{\numtasks}[1]{\small{(#1)}}
 
-% Following comment is from ijcai97-submit.tex:
-% The preparation of these files was supported by Schlumberger Palo Alto
-% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
-% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
-% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
-% preparation.
+\newcommand{\badtx}{\ensuremath{\mathrm{BAD}}}
 
-% These instructions can be modified and used in other conferences as long
-% as credit to the authors and supporting agencies is retained, this notice
-% is not changed, and further modification or reuse is not restricted.
-% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
-% contacts for providing assistance without their prior permission
-
-% To use for other conferences, change references to files and the
-% conference appropriate and use other authors, contacts, publishers, and
-% organizations.
-% Also change the deadline and address for returning papers and the length and
-% page charge instructions.
-% Put where the files are available in the appropriate places.
+\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
 
 %PDF Info Is REQUIRED.
+% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
+% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
  \pdfinfo{
-/TemplateVersion (IJCAI.2021.0)
-}
+/Title ()
+/Author ()
+} %Leave this
 
-\title{Learning Generalized Policies Over Grid Environments}
+\title{Representation Learning for Generalized Planning - SAT Encodings}
+%Your title must be in mixed case, not sentence case.
+% That means all verbs (including short verbs like be, is, using,and go),
+% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
+% articles, conjunctions, and prepositions are lower case unless they
+% directly follow a colon or long dash
+%\author{GFM}
 
-% \title{General Polizy Learner for Grid Environments}
-
-\author{
-
-}
-
-% Papers must be no longer than 7 pages in total: 6 pages for the body of the paper (including all figures/tables),
-% plus up to 1 additional page with references
 \begin{document}
@@
 
-\begin{abstract}
-\end{abstract}
+\section{Learning of Generalized Features \& Policy in Adversarial FOND domains}
 
-\section{Introduction}
+Encoding is parametrized by
+\begin{itemize}
+ \item Pool $F$ of description logic features $f$, each with given feature complexity $\mathcal{K}(f)$.
+ \item Training set consisting of a sample of transitions from a number of instances of the same domain.
+       At the moment we're assuming the sample is complete, and we have full information on whether each state
+       in the sample is a goal state, an unsolvable state, or otherwise (see below for definitions). We also have access
+       to the minimum distance to a goal $V^*(s)$ for each state $s$.
+ \item A parameter $\delta$ which is a ``slack'' value to determine the maximum deviation from the optimal $V^*(s)$
+ what we will allow in our policy. This will be made clearer in the encoding below.
+\end{itemize}
 
-\section{Logic Language}
+\subsection{Terminology}
+A state is called \emph{reachable} if there is a path to it from $s_0$, and
+it is called \emph{solvable} if there is a path from it to a goal
+state.
+A state is \emph{alive} if it is solvable, reachable and not a
+goal state~\cite{frances-et-al-ijcai2019}.
 
-The Grid Domains share the set of Objects \textit{O}, and the set of predicates \textit{P}.
+We use $T$ to denote the set of all transitions $(s, s')$ in the training sample such that $s$ is alive.
 
-\subsection{Objects}
+\subsection{Improvements}
 
-All objects in \textit{O} belong to one sort, \textit{cell}.
-Then, we have an object \textit{o} for each cell in the grid.
-For instance, in a grid of size $i \times j$ the set \textit{O} contains the object \textit{cij}, representing the cell in the row \textit{i} and the column \textit{j}.
+\paragraph{Non-distinguishability of transitions as an equivalence relation.}
+Any fixed, given pool of features $F$ implicitly defines an equivalence relation where to transitions are
+equivalent iff they cannot be distinguished \emph{by any feature in $F$}.
+If two transitions cannot be distinguished by any feature, then clearly either the policy computed by the SAT solver
+considers all of them as ``good'', or as ``bad''.
+We'll exploit this by using one single SAT variable to denote whether \emph{all transitions in a given equivalence
+class} are good or bad. When exploiting this notion of equivalence (which is implemented as an optional feature of
+the CNF generator), then every mention below to SAT variable $Good(s, s')$ needs to be read as $Good(s_{\star}, s_{\star}')$,
+where $(s_{\star}, s_{\star}')$ is the \emph{representative} transition of the equivalence class to which $(s, s')$ belongs.
 
-\subsection{Predicates}
+\paragraph{``Bad'' transitions.}
+We use \badtx{} to denote the set of transitions that have been determined at preprocessing as necessarily
+\emph{not} good.
+At the moment, this set contains all transitions that go from an alive to an unsolvable state and, if using
+equivalence relations, all those other transitions in whose equivalence class there is some other ``bad'' transition.
 
-To explain the predicates it is good to remember that each of the domains has different values contained in the grid, e.g.
-the domain reach-for-the-star has five possible values for each cell in the grid, which are: Empty, drawn, agent, star, right-arrow, and left-arrow.
-Then, let us define that for each domain there is a set of values \textit{V} which represents the values that each cell object in the grid can take.
-It is also good to remember the difference between static and dynamic predicates.
-Then, the static predicates are always the same for any state of an instance, while a dynamic predicate will change depending on the state of the instance.
-\textit{P} will contain both types of predicates, dynamic and static.\\
+\paragraph{Feature dominance.}
+Work In Progress.\footnote{This is implemented, but needs to be adapted to the equivalence classes improvement.}
 
-We have used the dynimic predicates to define the value of \textit{V} that any object \textit{o} can take at a given time.
-While we have used the static predicates to define the topology of the grid, i.e., the relative position of o with respect to o'.
-It is important to note that it is always preferable to have a static predicate rather than a dynamic one as this will considerably reduce the problem of the combinatorial explosion of symbols [some reference].
-Finally, we define a set of relative directions \textit{D}, which contains \{right, left, down, up, right-up, right-down, left-down, left-up, horizontal, vertical\}.
-Then, \textit{D} is used to define the topology of the grid.\\
+\newpage
 
-Then, \textit{P} contains:
+\subsection{Variables}
 
-\subsubsection{Dynamic predicates:}
+\subsubsection{Main Variables}
+
+Let the transitions be defined as $s \rightarrow a \rightarrow s' \rightarrow s"$, where the agent executes a in the state s and goes to some $s'$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$.
+Therefore the transitions $(s, s')$ is deterministic and the transition $(s, s'')$ is non-deternimistic.
 
 \begin{itemize}
+ \item $Good(s, a)$ for $s$ alive, $s''$ solvable. Where $V(s'') < V(s)$.
 
-\item \textit{v(cij)}: Means that cell \textit{o} has the value \textit{v} at a certain time.
-Recall that v is a concrete value within the set \textit{V}.
-For instance, if \textit{v} is equalt to the value \textit{agent}, then \textit{agent(cij)} means that cell \textit{cij} has the value agent.
-\item \textit{player(n)}: This is predicate used for multiplayer games where $n \in \mathbb N$, and represents the player whose turn it is this turn.
-For instance, the predicate \textit{player(0)} means that in a specific state is the turn of the player \textit{0}.
-
-\end{itemize}
-
-\subsubsection{Static predicates:}
-
-\begin{itemize}
-
-\item \textit{d(o, o')}: means that \textit{o} has \textit{o'} as contiguous in direction d.
-For example: \textit{right(cij, cij')} means that to the adjacent right of cell \textit{cij} is the cell \textit{cij'}.
-Notice that some directions of \textit{D} are redundan, e.g., the predicate \textit{horizontal(cij, cij')} means that to the adjacent right o left of cell \textit{cij} is the cell \textit{cij'}, and could be defined combining two of the other predicates like $\textit{right(cij, cij')} \lor \textit{left(cij, cij')}$.
-In a similar way \textit{vertical(cij, cij')} can be defined as $\textit{up(cij, cij')} \lor \textit{down(cij, cij')}$.
-Furthermore, some directions like \textit{left(cij, cij')} are also redundant, since can be redefined as the invers of its opposite direction like \textit{right(cij', cij)}.
-This redundancy will increase the number of possible features according to the grammar, however it will also reduce the complexity of the features.
-
-\item \textit{same-row(o, o')}: Means that \textit{o} is in the same row as \textit{o'}.
-For example: \textit{same-row(cij, cij')} means that cell \textit{cij} is in the same row as cell \textit{cij'}, the row \textit{i}.
-
-\item \textit{same-col(o, o')}: Means that \textit{o} is in the same column as \textit{o'}.
-For example: \textit{same-col(cij, ci'j)} means that cell \textit{cij} is in the same column as cell \textit{ci'j}, the column \textit{j}.
-
-\end{itemize}
-
-\subsection{Encodings}
-
-\subsubsection{FOND Adversarial}
-
-\subsubsection{Main Variables}
-\begin{itemize}
  \item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.
@@
  V(s', D) \rightarrow \neg Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$.} \tag{\theequation${}^\prime$}
+\end{align}
+
+\smallpar{C3 (Optional)} All descending transitions must be considered Good:
+\begin{align}
+ V(s, d) \land V(s', d') \rightarrow Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $1 \leq d' < d \leq D$,} \\
+ Good(s, s'),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
 \end{align}
@@
 
-% ... End
+\section{Empirical Results}
 
-%\section*{Acknowledgments}
-
-%% The file named.bst is a bibliography style file for BibTeX 0.99c
-\small
-\bibliographystyle{named}
+\bibliographystyle{plain}
+% Cross-referenced entries need to go after the entries that cross-reference them
 \bibliography{abbrv-short,literatur,references,crossref-short}
-
 \end{document}

### 2021-04-19 doc/paper/paper.tex
minor changes in doc

@@
 
-Let the transitions be defined as $s \rightarrow a \rightarrow s' \rightarrow s"$, where the agent executes a in the state s and goes to some $s'$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$.
+In any non deterministic domain the agent can go a pull of states $S'$ by executing an action $a$ in the state $s$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$.
+Then all the transitions holds in the form $s \rightarrow a \rightarrow s'$, where $s' \epsilon~S'$.
+
+%We define the adversarial setting as transitions defined by $s \rightarrow a \rightarrow s' \rightarrow s"$, where the agent executes a in the state s and goes to some $s'$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$.
 Therefore the transitions $(s, s')$ is deterministic and the transition $(s, s'')$ is non-deternimistic.
+If there is no possible $s''$ outgoing from $s'$ we just set $s'' = s'$.
+
+%If we are in a completely non-deterministic setting we can make it hold in the previous definition just by setting $s' = s''$.
+
+%We can face two different situations.
+One in which the actions space is defined and never change from one instance to another.
+In the other situation we have no defined action space $A$.
+When we are facing a non defined $A$, we just define the actions as efects to be discovered implicitly in the transitions $s \rightarrow s'$.
 
 \begin{itemize}
- \item $Good(s, a)$ for $s$ alive, $s''$ solvable. Where $V(s'') < V(s)$.
+ \item $Good(s, a)$ for $s$ alive, $s'$ solvable for all possible $s'$ result of executing a in $s$.
 
- \item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.
+ \item $Bad(s)$ for $s$ alive.
+
+ %\item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.
 
@@
 \smallpar{C1}
-The policy has to be complete with respect to all alive states:
+The policy has to be complete with respect to all possible actions applicable in s:
 \begin{align}
-\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
+\bigvee_{a \text{ s.t. } (s, a, S') \in T} Good(s, a),&\;\; \text{for $s$ alive.}
 \end{align}
 
-\smallpar{C2} $V$ is always descending along Good transitions:
+\smallpar{C2} $V$ is always descending along Good actions:
 \begin{align}
- Good(s, s') \land V(s', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $d \in [1, D)$.} \\
- V(s', D) \rightarrow \neg Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$.} \tag{\theequation${}^\prime$}
+ Good(s, a) \land V(s', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s, a$ alive, $(s, a) \not\in \badtx$, $d \in [1, D)$.} \\
+ V(s', D) \rightarrow \neg Good(s, a),&\;\; \text{for $s, a$ alive, $(s, a) \not\in \badtx$.} \tag{\theequation${}^\prime$}
 \end{align}
 
-\smallpar{C3 (Optional)} All descending transitions must be considered Good:
+\smallpar{C3} All descending transitions must be considered Good:
 \begin{align}
- V(s, d) \land V(s', d') \rightarrow Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $1 \leq d' < d \leq D$,} \\
- Good(s, s'),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
+ V(s, d) \land V(s', d') \rightarrow Good(s, a),&\;\; \text{for $s, s'$ alive, $(s, a, s') \not\in \badtx$, $1 \leq d' < d \leq D$,} \\
+ Good(s, a),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
 \end{align}
@@
 \smallpar{C5-6}
-Good transitions can be distinguished from bad transitions.
-Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
-of two different equivalence classes such that $(s, s') \not\in \badtx$
-(which implies that $s'$ is solvable). Then,
+Good pairs (s, a) can be distinguished from bad pairs (s, a).
+Let $(s, a)$ and $(s, a')$
+of two different equivalence classes such that $(s, a, S') \not\in \badtx$
+(which implies that any $s' \in S'$ is solvable). Then,
 
-\begin{align}
- Good(s, s') \rightarrow Good(t, t') \lor
- Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
- Good(s, s') \rightarrow
- Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
-\end{align}
+%\smallpar{C5-6}
+%Good transitions can be distinguished from bad transitions.
+%Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
+%of two different equivalence classes such that $(s, s') \not\in \badtx$
+%(which implies that $s'$ is solvable). Then,
+%\begin{align}
+% Good(s, s') \rightarrow Good(t, t') \lor
+% Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
+% Good(s, s') \rightarrow
+% Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
+%\end{align}
 

### 2021-04-23 doc/paper/paper.tex
Adapt PDF encoding to fixed pool of actions

--- 2021-04-19 doc/paper/paper.tex
@@
 goal state~\cite{frances-et-al-ijcai2019}.
-
 We use $T$ to denote the set of all transitions $(s, s')$ in the training sample such that $s$ is alive.
@@
 
-\paragraph{Feature dominance.}
-Work In Progress.\footnote{This is implemented, but needs to be adapted to the equivalence classes improvement.}
-
 \newpage
 
-\subsection{Variables}
+\subsection{Fixed Pool $A$ of actions}
 
-\subsubsection{Main Variables}
+We here assume that all instances $P$ of the generalized problem have the same fixed set of actions $A$.
+We denote by $(s, a, s'') \in T$ tuples of state, action, and possible state $s''$ resulting from the adversary
+response to the application of $a$ in $s$.
 
-Let the transitions be defined as $s \rightarrow a \rightarrow s' \rightarrow s"$, where the agent executes a in the state s and goes to some $s'$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$.
-Therefore the transitions $(s, s')$ is deterministic and the transition $(s, s'')$ is non-deternimistic.
+\subsubsection{Variables}
 
 \begin{itemize}
- \item $Good(s, a)$ for $s$ alive, $s''$ solvable. Where $V(s'') < V(s)$.
+ \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.
 
- \item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.
+ \item $Bad(s)$ for $s$ alive.
+
+ %\item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.
 
@@
 
-\subsection{Hard Constraints}
+\subsubsection{Hard Constraints}
 
 \smallpar{C1}
-The policy has to be complete with respect to all alive states:
+The policy has to be complete with respect to all possible actions applicable in s:
 \begin{align}
-\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
+\bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
 \end{align}
 
-\smallpar{C2} $V$ is always descending along Good transitions:
+\smallpar{C2} $V$ is always descending along Good actions:
 \begin{align}
- Good(s, s') \land V(s', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $d \in [1, D)$.} \\
- V(s', D) \rightarrow \neg Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$.} \tag{\theequation${}^\prime$}
+ Good(s, a) \land V(s'', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$, $d \in [1, D)$.} \\
+ V(s'', D) \rightarrow \neg Good(s, a),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$.} \tag{\theequation${}^\prime$}
 \end{align}
 
-\smallpar{C3 (Optional)} All descending transitions must be considered Good:
-\begin{align}
- V(s, d) \land V(s', d') \rightarrow Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $1 \leq d' < d \leq D$,} \\
- Good(s, s'),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
-\end{align}
+%\smallpar{C3} All descending transitions must be considered Good:
+%\begin{align}
+% V(s, d) \land V(s'', d') \rightarrow Good(s, a),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$, $1 \leq d' < d \leq D$,} \\
+% Good(s, a),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
+%\end{align}
 
@@
 \smallpar{C5-6}
-Good transitions can be distinguished from bad transitions.
-Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
-of two different equivalence classes such that $(s, s') \not\in \badtx$
-(which implies that $s'$ is solvable). Then,
-
+Good pairs $(s, a)$ can be distinguished from bad pairs $(s, a)$.
+%Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
+%of two different equivalence classes such that $(s, s') \not\in \badtx$
+%(which implies that $s'$ is solvable). Then,
 \begin{align}
- Good(s, s') \rightarrow Good(t, t') \lor
- Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
- Good(s, s') \rightarrow
- Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
+ Good(s, a) \rightarrow Good(t, a) \lor
+ D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \not\in \badtx$.} \\
+ Good(s, a) \rightarrow D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \in \badtx$.}
 \end{align}
@@
 
-\smallpar{C8 (Optional)}
-All selected features need to have some Good transition that takes them to $0$:
-\begin{align}
- Selected(f) \rightarrow \bigvee_{(s, s') \in Z(f)} Good(s, s'),&\;\; \text{for $f$ in pool}
-\end{align}
-
-\noindent where $Z(f)$ is the set transitions starting in an alive state that change the denotation of $f$ from something
-larger than 0 to 0.
-
-\subsection{Soft Constraints}
+\subsubsection{Soft Constraints}
 We simply post a constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.
-
-\section{Empirical Results}
 

### 2021-04-28 doc/paper/paper.tex
Update encoding

@@
 
-\smallpar{C2} $V$ is always descending along Good actions:
+\smallpar{C2} $V$ is always descending along Good actions. For each $(s, a, s')$ in the set of non-deterministic transitions
+such that both $s$ and $s'$ are alive, post:
 \begin{align}
- Good(s, a) \land V(s'', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$, $d \in [1, D)$.} \\
- V(s'', D) \rightarrow \neg Good(s, a),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$.} \tag{\theequation${}^\prime$}
+ Good(s, a) \land V(s, k) \rightarrow \bigvee_{1 \leq k' \leq k} V(s', k'),&\;\; \text{for } k \in [1, D].
 \end{align}

### 2021-05-05 doc/paper/paper.tex
changes

@@
 
-\section{Learning of Generalized Features \& Policy in Adversarial FOND domains}
+\section{Learning of Generalized Features \& Policy in FOND domains unsipervised}
 
@@
 
+\paragraph{Bad'}
+
 \newpage
 
-\subsection{Fixed Pool $A$ of actions}
+\subsection{Encoding for FOND domains}
 
-We here assume that all instances $P$ of the generalized problem have the same fixed set of actions $A$.
-We denote by $(s, a, s'') \in T$ tuples of state, action, and possible state $s''$ resulting from the adversary
-response to the application of $a$ in $s$.
+We here assume that all instances $P$ of the generalized problem have a set of actions $A$.
+We denote by $(s, a, s') \in T$ tuples of state, action, and possible state $s'$ resulting from executing $a$ in $s$.
 
-\subsubsection{Variables}
+\subsubsection{Main Variables}
 
@@
  \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.
+ \item $Good(s, a, s')$ for $s$ alive, solvable, and $a \in A$.
 
@@
 \bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
+\end{align}
+
+\smallpar{C1}
+The policy has to be complete with respect to all alive states:
+\begin{align}
+\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
 \end{align}

### 2021-05-05 experiments/chase.py

@@ -44,7 +44,7 @@ def experiments():
         decreasing_transitions_must_be_good=False,
         allow_cycles=False,
         use_action_ids=True,
-        use_weighted_tx=True,
+        use_weighted_tx=False,
         distinguish_goals=True,
 
         sampling_strategy="goal",

### 2021-05-05 experiments/chase.py
little clean up

@@ -44,7 +44,7 @@ def experiments():
         decreasing_transitions_must_be_good=False,
         allow_cycles=False,
         use_action_ids=True,
-        use_weighted_tx=False,
+        use_weighted_tx=True,
         distinguish_goals=True,
 
         sampling_strategy="goal",

### 2021-05-06 doc/paper/paper.tex
little clean up
updated paper ¡

@@
 
-\paragraph{Bad'}
+\newpage
+
+\paragraph{Bullet points}
+\begin{itemize}
+\item Learning generalized policies in unsupervised FOND domains from small examples.
+\item FOND encoding, introducing Good(s, a) features to deal with non-determinism.
+Where $a \in A$, and $A$ is not required to be fixed.
+However, if $A$ is fixed we show a way to exploit it, reducing the number of transitions to distinguish.
+\item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
+\item Empirical results with five domains: Chase, Shoot, Space Invaders, Delivery, Wumpus world.
+\item Incremental policy learning, to address the scalability problem.
+First a random sample is taken from the whole graph and the policy is then refined incrementally by iteratively increasing the sample size.
+The strategy for increasing the size of the sample can be goal-directed or random.
+%\item Introducing the sort of novelty to choose between the different successors classified as good by our policy
+\item Use of a uniform grammar for the different grid domains.
+\end{itemize}
 
@@
 
-We here assume that all instances $P$ of the generalized problem have a set of actions $A$.
+We here assume that all instances $P$ of the generalized problem have a set of actions $A$. We do not need $A$ begin fixed.
 We denote by $(s, a, s') \in T$ tuples of state, action, and possible state $s'$ resulting from executing $a$ in $s$.
@@
  \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.
- \item $Good(s, a, s')$ for $s$ alive, solvable, and $a \in A$.
+ \item $Good(s, a, s')$ for $s$ alive, $s'$ solvable, and $(s, a, s') \not\in \badtx$.
 
@@
 \smallpar{C1}
-The policy has to be complete with respect to all possible actions applicable in s:
+The policy has to be complete with respect to all alive states:
 \begin{align}
 \bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
-\end{align}
-
-\smallpar{C1}
-The policy has to be complete with respect to all alive states:
-\begin{align}
-\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
 \end{align}
@@
 \smallpar{C5-6}
-Good pairs $(s, a)$ can be distinguished from bad pairs $(s, a)$.
+Good transitions $(s, a, s')$ can be distinguished from bad transitions $(s, a, s')$.
 %Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
@@
 %(which implies that $s'$ is solvable). Then,
+Let $(s, a, s')$ and $(t, b, t')$ be \emph{representative} transitions
+of two different equivalence classes such that $(s, a, s') \not\in \badtx$
+(which implies that $s'$ is solvable). Where $a, b \in A$. Then,
 \begin{align}
- Good(s, a) \rightarrow Good(t, a) \lor
- D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \not\in \badtx$.} \\
- Good(s, a) \rightarrow D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \in \badtx$.}
+ Good(s, a, s') \rightarrow Good(t, b, t') \lor
+ Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
+ Good(s, a, s') \rightarrow
+ Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
 \end{align}
@@
 \smallpar{C7 (Optional)}
+The transitions $(s, a, s')$ and $(s, a, t')$ will be treated as equivalent. In $C5-6$ if $a=b$ and $s=t$ we don't require this transitions to be distinguished.
+
+\smallpar{C8}
+Good pairs $(s, a)$ implies at least one transition $(s, a, s')$ labeled as good.
+\begin{align}
+\bigvee_{s' \text{ s.t. } (s, a, s') \in T \setminus \badtx} Good(s, a, s'),&\;\; \text{for $(s, a)$ where $s$ alive.}
+\end{align}
+
+\smallpar{C9 (Optional)}
 Goals are distinguishable from non-goals.
@@
 
+\smallpar{C10 (Optional)}
+All selected features need to have some Good transition that takes them to $0$:
+\begin{align}
+ Selected(f) \rightarrow \bigvee_{(s, a, s') \in Z(f)} Good(s, s'),&\;\; \text{for $f$ in pool}
+\end{align}
+
+\noindent where $Z(f)$ is the set transitions starting in an alive state that change the denotation of $f$ from something
+larger than 0 to 0.
+
 \subsubsection{Soft Constraints}
+\smallpar{C11}
 We simply post a constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.
+
+\smallpar{C12 (Optional)}
+If no action is good in state $s$ alternatively we can set the state as $Bad(s)$. Then  post a constraint $\neg Bad(s)$, with weight equal to one. Then the constraint $C1$ changes,
+\begin{align}
+Bad(s) ~ or~ \bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
+\end{align}
+
+\noindent Notice that now the policy is complete in domains where an state can not be solved or has not any $Good(s, a)$.
+
+\section{Empirical Results}
+
+\subsection{Chase}
+
+\subsection{Shoot}
+
+\subsection{Space Invaders}
+
+\subsection{Delivery}
+
+\subsection{Wumpus world}
 

### 2021-05-07 doc/paper/paper.tex
minor change
minor fix to the encoding

@@
 Where $a \in A$, and $A$ is not required to be fixed.
-However, if $A$ is fixed we show a way to exploit it, reducing the number of transitions to distinguish.
+However, if $A$ is fixed we show a way to exploit it reducing the number of transitions to distinguish.
 \item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
@@
 \smallpar{C8}
-Good pairs $(s, a)$ implies at least one transition $(s, a, s')$ labeled as good.
+If $(s, a)$ is good, then the resulting transitions must be good too:
+%(s, a, s') \in T \setminus \badtx
 \begin{align}
-\bigvee_{s' \text{ s.t. } (s, a, s') \in T \setminus \badtx} Good(s, a, s'),&\;\; \text{for $(s, a)$ where $s$ alive.}
+Good(s, a) \rightarrow Good(s, a, s'),\;\; \text{for $(s, a, s') \in T$ where $s$ alive.}
 \end{align}

### 2021-05-11 doc/paper/paper.tex
space invaders

--- 2021-05-05 doc/paper/paper.tex
@@
 \usepackage{fancyvrb}
+\usepackage{color}
 
@@
 \newcommand{\setst}[2]{\ensuremath{\left\{#1 \mid #2 \right\}}}
+\newcommand{\newcontent}{\textbf{\color{red}NEW}}
 
@@
 
-\title{Representation Learning for Generalized Planning - SAT Encodings}
+\title{Self-Supervised Learning of Generalized Policies in adversarial domains}
 %Your title must be in mixed case, not sentence case.
@@
 
-\section{Learning of Generalized Features \& Policy in FOND domains unsipervised}
+\subsection{SAT Encoding}
 
-Encoding is parametrized by
+Our encoding is parametrized by
 \begin{itemize}
  \item Pool $F$ of description logic features $f$, each with given feature complexity $\mathcal{K}(f)$.
- \item Training set consisting of a sample of transitions from a number of instances of the same domain.
-       At the moment we're assuming the sample is complete, and we have full information on whether each state
-       in the sample is a goal state, an unsolvable state, or otherwise (see below for definitions). We also have access
-       to the minimum distance to a goal $V^*(s)$ for each state $s$.
+ \item \newcontent{} A (training) set $T$ of transitions $(s, a, s') \in T$ from a number of instances of the same domain.
+       We assume $T$ is \emph{closed}: if $s$ appears in the first position of a transition, then all possible
+       transitions starting in $s$ in that instance appear in $T$ too.
+ \item \newcontent{} A set $adv(s)$ of all possible moves by the adversary on state $s$.
+
+ \item For each state $s$ appearing in some transition, full information on whether $s$
+       is a goal, unsolvable, or alive.
+       Also access to the minimum distance-to-goal $V^*(s)$ for each state $s$.
  \item A parameter $\delta$ which is a ``slack'' value to determine the maximum deviation from the optimal $V^*(s)$
  what we will allow in our policy. This will be made clearer in the encoding below.
+
+ \item \newcontent{} A Boolean parameter \texttt{allow\_bad\_states} with intended meaning ``allow the policy
+        to remain undefined for some of the states in the training set''.
+ \item \newcontent{} A parameter \texttt{action\_labels} with possible values:
+ \begin{itemize}
+   \item \texttt{ignore}: Don't exploit the info on what action induced what transition. This is necessary
+  when the set of actions changes over different instances of the domain.
+   \item \texttt{use$_1$}: Use info on action labels, reasoning only about whether taking an action in a certain
+   (abstract) state is good or not. This assumes that the action set is fixed over the entire domain.
+   \item \texttt{use$_2$}: As above, but reason too about the feature change. E.g. your policy can have rules as
+  ``When $f>0$, take action $a$ \emph{only if $f'$ increases}.
+ \end{itemize}
 \end{itemize}
 
-\subsection{Terminology}
+\subsubsection{Main Variables}
+
+\begin{itemize}
+ \item $Good(s, a, s')$, for $(s, a, s') \in T$ with $s$ being alive.
+
+ \item $Bad(s)$ for $s$ an alive state appearing in $T$.
+
+ %\item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.
+
+ \item $V(s, d)$ for $s$ alive, and $d \in [0, D]$, where $D = \max_{s} \delta \cdot V^*(s)$,
+ with intended denotation $V(s)=d$.
+ Note that for states $s$ that are a goal, we know $V(s)=0$,
+ and for states $s$ that are unsolvable, we know that $V(s) \neq d$ for all $d$.
+ Thus, we can restrict SAT variables $V(s, d)$ to those states $s$ that are alive.
+
+ \item $Select(f)$, for each feature $f$ in the feature pool.
+\end{itemize}
+
+\subsubsection{Hard Constraints}
+
+\smallpar{C1 (if $\neg$\texttt{allow\_bad\_states})}
+Policy is defined in all alive states:
+\begin{align*}
+\bigvee_{(s, a, s') \in T \text{ s.t. } s=t} Good(s, a, s'), \;\; \text{for $t$ alive in $T$.}
+\end{align*}
+
+\smallpar{C1 (if \texttt{allow\_bad\_states})}
+Policy is defined in all alive states:
+\begin{align*}
+Bad(t) \lor \bigvee_{(s, a, s') \in T \text{ s.t. } s=t} Good(s, a, s'), \;\; \text{for $t$ alive in $T$.}
+\end{align*}
+
+\smallpar{C2} $V$ is always descending along Good actions, \textbf{taking into account all possible adversary responses}.
+For each $(s, a, s')$ in the set of non-deterministic transitions
+such that both $s$ and $s'$ are alive, post:
+%Good(s, a) \land V(s, k) \rightarrow \bigvee_{1 \leq k' \leq k} V(s', k'),&\;\; \text{for } k \in [1, D].
+\begin{align*}
+Good(s, a, s') \rightarrow V(s'') < V(s)  \;\; \text{for } (s, a, s') \in T,  s'' \in adv(s').
+\end{align*}
+
+%\smallpar{C3} All descending transitions must be considered Good:
+%\begin{align*}
+% V(s, d) \land V(s'', d') \rightarrow Good(s, a),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$, $1 \leq d' < d \leq D$,} \\
+% Good(s, a),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
+%\end{align*}
+
+%\smallpar{C4-5} Any upper bound on $V(s)$ (for $s$ not a goal) needs to be justified:
+%\begin{align*}
+% V(s) \leq d+1 \rightarrow \bigvee_{\substack{
+% s' \text{ goal child of } s\\
+% (s, s') \not\in \badtx}} Good(s, s') \lor
+% \bigvee_{\substack{
+% s' \text{ alive child of } s\\
+% (s, s') \not\in \badtx}} GV(s, s', d),&
+% \;\; \text{for $s$ alive, $d \in [0, D)$.} \\
+% \neg V(s) \leq 0,&\;\; \text{for $s$ not a goal.}
+%\end{align*}
+
+\smallpar{C3}
+Variables $V(s, d)$ define a function that is total over the set of alive states,
+and such that $V(s)$ is within lower bound $V^*(s)$ and upper bound $\delta \cdot V^*(s)$:
+\begin{align*}
+ \bigvee_{V^*(s) \leq d \leq \delta \cdot V^*(s)} V(s,d),&\;\; \text{for $s$ alive.} \\
+ \neg V(s, d) \lor \neg V(s, d')&\;\; \text{for $s$ alive, $1 \leq d < d' \leq D$.}
+\end{align*}
+
+\smallpar{C4}
+Good transitions can be distinguished from bad transitions.
+%Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
+%of two different equivalence classes such that $(s, s') \not\in \badtx$
+%(which implies that $s'$ is solvable). Then,
+Let $(s, a, s')$ and $(t, b, t')$ be \emph{representative} transitions
+of two different equivalence classes such with $s$, $t$ alive. Then,
+\begin{align*}
+ Good(s, a, s') \land \neg Good(t, b, t') \rightarrow
+ D2(s, s', t, t'),&\;\; \text{  }
+% Good(s, a, s') \rightarrow
+% D2(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
+\end{align*}
+
+\noindent where $D2(s, s', t, t')$ is shorthand for $\bigvee_{} Select(f)$, with $f$ ranging over:
+\begin{itemize}
+ \item[(a)] all features that distinguish state $s$ from $t$, if \texttt{action\_labels = use$_1$}.
+ \item[(b)] all features that distinguish $s$ from $t$ \textbf{plus} all features that
+ change differently along $(s, s')$ than along $(t, t')$.
+\end{itemize}
+
+Additionally, if \texttt{action\_labels = use$_1$} or \texttt{action\_labels = use$_2$}, then
+\textbf{the above constraint is only posted for transitions such that $a=b$}.
+
+\smallpar{C5 (Optional)}
+Goals are distinguishable from non-goals.
+\begin{align*}
+\bigvee_{f \in D1(s, s')} Select(f),&\;\; \text{for $s$ goal, $s$ not a goal}
+\end{align*}
+
+% GFM: I'm commenting this out, I don't think this is needed at all, actually I don't even know where this is coming from,
+% maybe some old draft???
+%\smallpar{C10 (Optional)}
+%All selected features need to have some Good transition that takes them to $0$:
+%\begin{align*}
+% Selected(f) \rightarrow \bigvee_{(s, a, s') \in Z(f)} Good(s, s'),&\;\; \text{for $f$ in pool}
+%\end{align*}
+%
+%\noindent where $Z(f)$ is the set transitions starting in an alive state that change the denotation of $f$ from something
+%larger than 0 to 0.
+
+\subsubsection{Soft Constraints}
+\smallpar{C6}
+A constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.
+
+\smallpar{C7 (if \texttt{allow\_bad\_states})}
+A constraint $\neg Bad(s)$ for each alive state $s$, with weight equal to one.
+
+\pagebreak
+
+\section{Terminology}
 A state is called \emph{reachable} if there is a path to it from $s_0$, and
@@
 
-\subsection{Improvements}
+\subsection{Optimizations}
 
@@
 
-\paragraph{Bad'}
+\newpage
+
+\section{Empirical Results}
+
+\subsection{Space Invaders - v0}
+\subsubsection{Description}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+    (A) Num[col-hv-Agent] [k=1]
+    (B) Dist[col-hv-white_king;right_col;col-hv-black_king] [k=4]
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. B=0 AND A>0 -> {B INCs, A DECs}, {B NILs, A NILs}, {B INCs, A NILs}
+  2. B>0 AND A>0 -> {B DECs, A NILs}, {B NILs, A NILs}, {B INCs, A DECs}, {B NILs, A DECs}
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+
+\end{Verbatim}
+
+\subsection{Chase}
+\subsubsection{Description}
+In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $rightup$, $right$, $rightdown$, $down$, $leftdown$, $left$, $leftup\}$.
+The agent can move only diagonally and the adversary can move in perpendicular directions.
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col_has_Agent,Exists(right_col,col_has_Target))] [k=5]
+  (B) Bool[And(row_has_Target,Exists(up_row,row_has_Agent))] [k=5]
+  (C) Dist[row_has_Target;up_row;row_has_Agent] [k=4]
+  (D) Dist[col_has_Agent;right_col;col_has_Target] [k=4]
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A=0 AND B=0 AND D>0 AND C>0 -> {A NILs, B NILs, C DECs, D DECs}, {A INCs, B INCs, C DECs, D DECs},
+                                    {A INCs, B NILs, C DECs, D DECs}, {A NILs, B INCs, C DECs, D DECs}
+  2. A>0 AND B=0 AND D>0 AND C>0 -> {A DECs, B INCs, C DECs, D DECs}, {A DECs, B NILs, C DECs, D DECs}
+  3. A=0 AND B=0 AND D>0 AND C=0 -> {A NILs, B INCs, C INCs, D DECs}, {A INCs, B INCs, C INCs, D DECs}
+  4. A=0 AND B=0 AND D=0 AND C>0 -> {A INCs, B INCs, C DECs, D INCs}, {A INCs, B NILs, C DECs, D INCs}
+  5. A=0 AND B>0 AND D>0 AND C>0 -> {A NILs, B DECs, C DECs, D DECs}, {A INCs, B DECs, C DECs, D DECs}
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+....... # ....... # ....... # ....T.. # ...T... # ...T... #
+....... # ....... # ....T.. # ....... # ....... # ...A... #
+....... # ....T.. # ....... # ....... # ....A.. # ....... #
+....T.. # ....... # ....... # ...A... # ....... # ....... #
+....... # ....... # ..A.... # ....... # ....... # ....... #
+....... # .A..... # ....... # ....... # ....... # ....... #
+A...... # ....... # ....... # ....... # ....... # ....... #
+\end{Verbatim}
+
+\subsection{Shoot}
+\subsubsection{Description}
+In this domain an agent has to shoot an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$.
+This game would be the equivalent of a check with the rook.
+Only that both the rook and the opponent can only move one orthogonal square at a time.
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-has-Adversary,col-has-Agent)] [k=3]
+  (B) Dist[row-has-Agent;up_row;row-has-Adversary] [k=4]
+  (C) Dist[cell-has-Agent;adjacent_cell;cell-has-Adversary] [k=4]
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A=0 AND C>0 AND B>0 -> {A INCs, B NILs, C NILs}, {A NILs, B DECs, C NILs}
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  A...... # ....... # ....... # ....... # ....... # ....... #
+  ....... # A...... # ....... # ....... # ....... # ....... #
+  ....... # ....... # A...... # ....... # ....... # ....... #
+  ....... # ....... # ....... # A...... # ....... # ....... #
+  ....... # .....T. # ....... # ....... # A...... # ....... #
+  .....T. # ....... # .....T. # ....... # ....... # A.....T #
+  ....... # ....... # ....... # .....T. # ......T # ....... #
+\end{Verbatim}
 
@@
 
-\subsection{Encoding for FOND domains}
-
-We here assume that all instances $P$ of the generalized problem have a set of actions $A$.
-We denote by $(s, a, s') \in T$ tuples of state, action, and possible state $s'$ resulting from executing $a$ in $s$.
-
-\subsubsection{Main Variables}
-
+\paragraph{Bullet points}
 \begin{itemize}
- \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.
- \item $Good(s, a, s')$ for $s$ alive, solvable, and $a \in A$.
-
- \item $Bad(s)$ for $s$ alive.
-
- %\item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.
-
- \item $V(s, d)$ for $s$ alive, and $d \in [0, D]$, where $D = \max_{s} \delta \cdot V^*(s)$,
- with intended denotation $V(s)=d$.
- Note that for states $s$ that are a goal, we know $V(s)=0$,
- and for states $s$ that are unsolvable, we know that $V(s) \neq d$ for all $d$.
- Thus, we can restrict SAT variables $V(s, d)$ to those states $s$ that are alive.
-
- \item $Select(f)$, for each feature $f$ in the feature pool.
+\item Learning generalized policies in unsupervised FOND domains from small examples.
+\item FOND encoding, introducing Good(s, a) features to deal with non-determinism.
+Where $a \in A$, and $A$ is not required to be fixed.
+However, if $A$ is fixed we show a way to exploit it reducing the number of transitions to distinguish.
+\item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
+\item Empirical results with five domains: Chase, Shoot, Space Invaders, Delivery, Wumpus world.
+\item Incremental policy learning, to address the scalability problem.
+First a random sample is taken from the whole graph and the policy is then refined incrementally by iteratively increasing the sample size.
+The strategy for increasing the size of the sample can be goal-directed or random.
+%\item Introducing the sort of novelty to choose between the different successors classified as good by our policy
+\item Use of a uniform grammar for the different grid domains.
 \end{itemize}
-
-%\subsubsection{Auxiliary Variables}
-%\begin{itemize}
-% \item We'll use $GV(s, s', d)$ to denote that $Good(s, s')$ and $V(s') \leq d$. This is enforced with the constraint
-% $GV(s, s', d) \rightarrow Good(s, s') \land V(s') \leq d$ for $s, s'$ alive, $(s, s') \not\in \badtx$, $d \in [0, D)$.
-% The other direction of the implication is not necessary.
-%\end{itemize}
-
-\subsubsection{Hard Constraints}
-
-\smallpar{C1}
-The policy has to be complete with respect to all possible actions applicable in s:
-\begin{align}
-\bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
-\end{align}
-
-\smallpar{C1}
-The policy has to be complete with respect to all alive states:
-\begin{align}
-\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
-\end{align}
-
-\smallpar{C2} $V$ is always descending along Good actions. For each $(s, a, s')$ in the set of non-deterministic transitions
-such that both $s$ and $s'$ are alive, post:
-\begin{align}
- Good(s, a) \land V(s, k) \rightarrow \bigvee_{1 \leq k' \leq k} V(s', k'),&\;\; \text{for } k \in [1, D].
-\end{align}
-
-%\smallpar{C3} All descending transitions must be considered Good:
-%\begin{align}
-% V(s, d) \land V(s'', d') \rightarrow Good(s, a),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$, $1 \leq d' < d \leq D$,} \\
-% Good(s, a),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
-%\end{align}
-
-%\smallpar{C4-5} Any upper bound on $V(s)$ (for $s$ not a goal) needs to be justified:
-%\begin{align}
-% V(s) \leq d+1 \rightarrow \bigvee_{\substack{
-% s' \text{ goal child of } s\\
-% (s, s') \not\in \badtx}} Good(s, s') \lor
-% \bigvee_{\substack{
-% s' \text{ alive child of } s\\
-% (s, s') \not\in \badtx}} GV(s, s', d),&
-% \;\; \text{for $s$ alive, $d \in [0, D)$.} \\
-% \neg V(s) \leq 0,&\;\; \text{for $s$ not a goal.}
-%\end{align}
-
-\smallpar{C3-4}
-Variables $V(s, d)$ define a function that is total over the set of alive states,
-and such that $V(s)$ is within lower bound $V^*(s)$ and upper bound $\delta \cdot V^*(s)$:
-\begin{align}
- \bigvee_{V^*(s) \leq d \leq \delta \cdot V^*(s)} V(s,d),&\;\; \text{for $s$ alive.} \\
- \neg V(s, d) \lor \neg V(s, d')&\;\; \text{for $s$ alive, $1 \leq d < d' \leq D$.}
-\end{align}
-
-\smallpar{C5-6}
-Good pairs $(s, a)$ can be distinguished from bad pairs $(s, a)$.
-%Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
-%of two different equivalence classes such that $(s, s') \not\in \badtx$
-%(which implies that $s'$ is solvable). Then,
-\begin{align}
- Good(s, a) \rightarrow Good(t, a) \lor
- D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \not\in \badtx$.} \\
- Good(s, a) \rightarrow D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \in \badtx$.}
-\end{align}
-
-\noindent where $Dist(s, s', t, t')$ is shorthand for $\bigvee_{f \in D1\&2(s, s', t, t')} Select(f)$.
-
-\smallpar{C7 (Optional)}
-Goals are distinguishable from non-goals.
-\begin{align}
-\bigvee_{f \in D1(s, s')} Select(f),&\;\; \text{for $s$ goal, $s$ not a goal}
-\end{align}
-
-\subsubsection{Soft Constraints}
-We simply post a constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.
 

### 2021-05-11 experiments/ct.py

@@ -14,7 +14,7 @@ ct_params = Bunch({
     'use_player_as_feature': False,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
-    'use_adjacency': False,
+    'use_adjacency': True,
     'sorts_to_use': {CELL_S, COL_S, ROW_S},
     'unary_predicates': {STALEMATE, CHECKMATE}
 })
@@ -36,6 +36,7 @@ def experiments():
     exps["1"] = update_dict(
         base,
         instances=[0],
+        # instances=[0],
         test_instances=[0, 1, 2, 3],
         max_concept_size=5,
         distance_feature_max_complexity=4,
@@ -49,15 +50,15 @@ def experiments():
         verbosity=1,
         initial_sample_size=20,
         refinement_batch_size=50,
-        maxsat_iter=10,
+        maxsat_iter=4,
 
         allow_bad_states=False,
         decreasing_transitions_must_be_good=False,
         allow_cycles=False,
-        use_action_ids=False,
+        use_action_ids=True,
         use_weighted_tx=False,
         distinguish_goals=True,
-        sampling_strategy="goal",
+        sampling_strategy="full",
 
         # skip_train_steps=[0, 1, 2],  # do not generate features twice!
         skip_train_steps=[],

### 2021-05-11 experiments/domain_params.py

@@ -2,15 +2,6 @@ from gpl.utils import Bunch
 from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
 
 
-shoot_params = Bunch({
-    'domain_name': 'shoot',
-    'use_player_as_feature': False,
-    'map_cells': True,
-    'use_diagonals_for_map_cells': True,
-    'use_adjacency': True,
-    'sorts_to_use': {COL_S, ROW_S, CELL_S}
-})
-
 space_invaders_params = Bunch({
     'domain_name': 'space_invaders',
     'use_player_as_feature': False,

### 2021-05-11 experiments/space_invaders.py

@@ -5,13 +5,15 @@ from sltp.util.misc import update_dict
 
 from gpl.domains.grid_games.domain import Domain
 
+
 space_invaders_params = Bunch({
     'domain_name': 'space_invaders',
     'use_player_as_feature': False,
     'map_cells': False,
     'use_diagonals_for_map_cells': False,
     'use_adjacency': True,
-    'sorts_to_use': {COL_S, ROW_S, CELL_S},
+    'sorts_to_use': {CELL_S, COL_S, ROW_S},
+    'unary_predicates': {},
 })
 
 def experiments():
@@ -30,10 +32,13 @@ def experiments():
     exps = dict()
     exps["1"] = update_dict(
         base,
-        # instances=[0],
-        instances=[0, 4, 8],
-        # instances=[0, 3, 4, 8],
-        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9],
+        # instances=[0, 10],
+        instances=[0, 4, 8, 10],
+        # instances=[4],
+        # instances=[10,],
+        # instances=[10],
+        # instances=[0, 3, 4, 8, 10],
+        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12],
         max_concept_size=5,
         distance_feature_max_complexity=4,
         concept_generation_timeout=15000,
@@ -51,7 +56,7 @@ def experiments():
         allow_bad_states=True,
         decreasing_transitions_must_be_good=False,
         allow_cycles=False,
-        use_action_ids=True,
+        use_action_ids=False,
         use_weighted_tx=False,
         use_state_novelty=True,
         distinguish_goals=True,

### 2021-05-11 src/d2l/src/sltp/cnfgen.py

@@ -55,10 +55,11 @@ def run(config, data, rng):
     # policy = parse_dnf_policy(config)
     policy = parse_dnfa_policy(config)
 
-    # policy.minimize()
-    print("Policy:")
-    policy.print()
-    print("\nFINAL POLICY:")
+    policy.minimize()
+    if config.use_action_ids:
+        print("Policy (with actions):")
+        policy.print()
+    print("\nPOLICY:")
     policy.print_aaai20()
 
     return exitcode, dict(d2l_policy=policy)

### 2021-05-11 src/d2l/src/sltp/separation.py

@@ -335,6 +335,8 @@ class TransitionClassificationPolicy:
 class TransitionActionClassificationPolicy:
     def __init__(self, features):
         self.features = features
+        self.simplified_features = dict()
+        self.__assign_keys_to_featuers()
         self.dnf = set()
 
     def add_clause(self, clause, a):
@@ -369,11 +371,11 @@ class TransitionActionClassificationPolicy:
                     if explain:
                         print(f'\t\t{atom} not satisfied by transition values ({feat.denotation(m0)}, {feat.denotation(m1)})')
                     return False
-        if ma: # meaninf that we want to exploid a set of actions A (grounded, common, and fixed)
-            if (ma not in actions):
-                if explain:
-                    print(f'Action {ma} is not ({a})')
-                return False
+        # if ma: # meaninf that we want to exploid a set of actions A (grounded, common, and fixed)
+        #     if (ma not in actions):
+        #         if explain:
+        #             print(f'Action {ma} is not ({a})')
+        #         return False
         return True
 
     def print(self):
@@ -382,7 +384,7 @@ class TransitionActionClassificationPolicy:
         for i, (clause, a) in enumerate(self.dnf, start=1):
             print(f"  {i}. " + f"do({a}): " + self.print_clause(clause))
 
-    def print_aaai20(self):
+    def print_aaai20(self, simplified=False):
         self.print_header()
         # Group by state features
         grouped = defaultdict(list)
@@ -394,15 +396,36 @@ class TransitionActionClassificationPolicy:
         distinct_values = defaultdict(set)
         for key in grouped.keys():
             for atom in key:
-                distinct_values[atom.feature].add(atom.value)
+                distinct_values[self.get_feature_key(str(atom.feature))].add(atom.value)
+                # distinct_values[atom.feature].add(atom.value)
 
         invariant_value_features = {f: next(iter(vals)) for f, vals in distinct_values.items() if len(vals) == 1}
         print("Invariants: " + ','.join(f"{f}{'>0' if v is True else '=0'}" for f, v in invariant_value_features.items()))
         print("Policy:")
+        # TODO: Improve this print
         for i, (statef, transitionf) in enumerate(grouped.items(), start=1):
-            state_conds = ' AND '.join(sorted(map(str, statef)))
-            feature_conds = ', '.join(self.print_effect_list(e) for e in transitionf)
[…]

### 2021-05-11 src/gpl/domains/grid_games/envs/chase.py

@@ -10,14 +10,16 @@ BLACK = 2
 EMPTY = 'empty'
 BLACK_KING = 'black_king'
 WHITE_KING = 'white_king'
+WALL = 'wall'
 
 SIMPLIFIED_OBJECT = {
     EMPTY:'.',
     BLACK_KING:'T',
     WHITE_KING:'A',
+    WALL:'W',
 }
 
-ALL_TOKENS = [EMPTY, BLACK_KING, WHITE_KING]
+ALL_TOKENS = [EMPTY, BLACK_KING, WHITE_KING, WALL]
 
 COLOR_TO_PIECES = {
     WHITE: [WHITE_KING,],
@@ -28,8 +30,8 @@ opposite_color = lambda c: BLACK if c == WHITE else WHITE
 
 
 PIECE_VALID_ACTIONS = {
-    WHITE_KING: lambda pos, layout: king_valid_actions(pos, layout, WHITE),
-    BLACK_KING: lambda pos, layout: king_valid_actions(pos, layout, BLACK),
+    WHITE_KING: lambda pos, layout, params: king_valid_actions(pos, layout, WHITE, params),
+    BLACK_KING: lambda pos, layout, params: king_valid_actions(pos, layout, BLACK, params),
 }
 
 # Actions IDs
@@ -103,8 +105,27 @@ class Env(object):
         layout = rep.grid
         assert rep.nact < MAX_ACTIONS_BY_TURN[rep.player]
         assert not terminated(rep)
-        valid_actions = Env.available_actions(rep)
+        valid_actions = self.available_actions(rep)
         assert action in valid_actions
+        if not isinstance(action, tuple):
+            return self.__rep_after_move(rep, action)
+        else:
+            # the agent is putting a WALL
+            new_rep = copy.deepcopy(rep)
+            l = new_rep.grid
+            assert l[action] == EMPTY
+            l[action] = WALL
+            if rep.nact + 1 < MAX_ACTIONS_BY_TURN[rep.player]:
+                new_rep.grid = l
+                new_rep.nact += 1
+                return self.__update_rep(new_rep)
+            else:
+                new_rep.grid = l
+                new_rep.nact = 0
+                new_rep.player = opposite_color(rep.player)
+                return self.__update_rep(new_rep)
+
+    def __rep_after_move(self, rep, action):
         new_rep = copy.deepcopy(rep)
         l = new_rep.grid
         pos = runnable_position(rep.grid, rep.player)
[…]

### 2021-05-11 src/gpl/domains/grid_games/envs/shoot.py

@@ -1,7 +1,9 @@
+import random
 import sys
 
 import numpy as np
-
+from gpl.utils import Bunch
+import copy
 
 WHITE = 1 # player 1
 BLACK = 2 # player 2
@@ -33,10 +35,15 @@ PIECE_VALID_ACTIONS = {
 
 # Actions IDs
 
-UP = 1
-DOWN = 2
-RIGHT = 3
-LEFT = 4
+UP = 0
+DOWN = 1
+RIGHT = 2
+LEFT = 3
+LEFTUP = 4
+RIGHTUP = 5
+RIGHTDOWN = 6
+LEFTDOWN = 7
+
 
 AGENT_ACTION_SPACE = {
     UP,
@@ -50,6 +57,10 @@ ENV_ACTION_SPACE = {
     DOWN,
     RIGHT,
     LEFT,
+    # LEFTUP,
+    # RIGHTUP,
+    # RIGHTDOWN,
+    # LEFTDOWN,
 }
 
 ACTION_MOVE_DIRECTION = {
@@ -57,13 +68,21 @@ ACTION_MOVE_DIRECTION = {
     DOWN: (1, 0),
     RIGHT: (0, 1),
     LEFT: (0, -1),
+    LEFTUP: (-1, -1),
+    RIGHTUP: (-1, 1),
+    RIGHTDOWN: (1, 1),
+    LEFTDOWN: (1, -1),
 }
 
 MOVE_ACTION = {
-    (-1, 0): {WHITE: UP, BLACK: UP},
-    (1, 0): {WHITE: DOWN, BLACK: DOWN},
-    (0, 1): {WHITE: RIGHT, BLACK: RIGHT},
-    (0, -1): {WHITE: LEFT, BLACK: LEFT},
+    ACTION_MOVE_DIRECTION[UP]: UP,
+    ACTION_MOVE_DIRECTION[DOWN]: DOWN,
+    ACTION_MOVE_DIRECTION[RIGHT]: RIGHT,
+    ACTION_MOVE_DIRECTION[LEFT]: LEFT,
+    ACTION_MOVE_DIRECTION[LEFTUP]: LEFTUP,
+    ACTION_MOVE_DIRECTION[RIGHTUP]: RIGHTUP,
+    ACTION_MOVE_DIRECTION[RIGHTDOWN]: RIGHTDOWN,
+    ACTION_MOVE_DIRECTION[LEFTDOWN]: LEFTDOWN,
 }
 
[…]

### 2021-05-11 src/gpl/domains/grid_games/grammar/objects.py

@@ -2,6 +2,7 @@ from gpl.utils import Bunch
 from ..envs.pick_packages import AGENT, PACKAGE, PIT, EMPTY
 from ..envs.deliver import DESTINY, PACKAGE, AGENT, AGENT_WITH_PACKAGE, AGENT_IN_DESTINY_WITH_PACKAGE, AGENT_IN_DESTINY_WITHOUT_PACKAGE
 from ..envs.checkmate_tactic import WHITE_KING, WHITE_QUEEN, WHITE_TOWER, BLACK_KING
+from ..envs.chase import WALL
 
 NONE = 'none'
 PLAYER1 = 1
@@ -21,6 +22,16 @@ OBJECTS_CHECK = Bunch({
                 WHITE_KING,
                 WHITE_QUEEN,
                 WHITE_TOWER,},
+    'empty': EMPTY,
+    'player1': PLAYER1,
+    'player2': PLAYER2,
+    'none': NONE,
+})
+
+OBJECTS_CHASE = Bunch({
+    'general': {BLACK_KING,
+                WHITE_KING,
+                WALL,},
     'empty': EMPTY,
     'player1': PLAYER1,
     'player2': PLAYER2,
@@ -52,7 +63,7 @@ OBJECTS_DELIVER = Bunch({
 
 def get_domain_objects(domain_name):
     return {
-        'chase': OBJECTS,
+        'chase': OBJECTS_CHASE,
         'shoot': OBJECTS,
         'space_invaders': OBJECTS,
         'pick_packages': OBJECTS_PICK,

### 2021-05-11 src/gpl/domains/grid_games/task.py

@@ -62,14 +62,10 @@ class Task(ITask):
         succs = list()
         succs_reps = list()
         assert r0.player == self.objects.player1
+
         for op0 in self.env.available_actions(r0):
-            # global i
-            # i +=1
             s1 = __transition_player(s0, op0)
             succs_sp.append((op0, s1))
-            # if s1[0].deadend:
-            #     print("{}. deadend: {}, turn: {}".format(i, s1[0].deadend, s1[0].player))
-            #     print(self.get_printable_rep(s1[0]))
             if s1[0].goal or s1[0].deadend or s1[0].player == self.objects.player1:
                 if s1[1] == s0[1]:
                     continue
@@ -77,14 +73,22 @@ class Task(ITask):
             else:
                 assert s1[0].player == self.objects.player2
                 for op1 in self.env.available_actions(s1[0]):
+                    # global i
+                    # i += 1
+                    # if i == 76:
+                    #     print('H')
                     s2 = __transition_player(s1, op1)
+                    # print("{}. deadend: {}, turn: {}".format(i, s2[0].deadend, s2[0].player))
+                    # print(self.get_printable_rep(s2[0]))
                     if s2[1] == s1[1]:
                         continue
                     assert s2[0].player == self.objects.player1
                     succs.append((op0, s1, s2))
 
+
+
         # succs_reps.append(r0)
-        # for _, s in succs_sp:
+        # for _, _, s in succs:
         #     succs_reps.append(s[0])
         # self.print_path(succs_reps)
 

### 2021-05-11 src/gpl/sampling/adv.py

@@ -93,9 +93,12 @@ class TransitionSampleADV:
         return self.operators[o]
 
     def set_operators(self, ops):
+        try:
+            for o in ops:
+                self.operators[o] = o
+        except:
+            return
         self.given_action_space = True
-        for o in ops:
-            self.operators[o] = o
 
     def update_instance(self, sid, intance_id):
         self.instance[sid] = intance_id # {state_id: instance_id}
@@ -139,7 +142,8 @@ class TransitionSampleADV:
     def info(self):
         return f"roots: {len(self.roots)}, states: {len(self.states)}, " \
                f"transitions: {self.num_transitions()} ({self.num_optimal_transitions()} optimal)," \
-               f" goals: {len(self.goals)}, alive: {len(self.alive_states)}"
+               f" goals: {len(self.goals)}, alive: {len(self.alive_states)}," \
+               f" deadends: {len(self.deadends)}"
 
     def num_optimal_transitions(self):
         count = 0

### 2021-05-11 src/gpl/tester.py

@@ -108,7 +108,7 @@ def run_test(config, search_policy, task, instance_name, rng):
 
     s = task.initial_state
     expanded = 0
-    visited_sa = defaultdict(lambda: 0)
+    visited_sp = defaultdict(lambda: 0)
     # visited_sp = defaultdict(lambda: 0)
     solution = list()
     path = list()
@@ -129,39 +129,39 @@ def run_test(config, search_policy, task, instance_name, rng):
             exitcode = ExitCode.AbstractPolicyNotCompleteOnTestInstances
             break
 
-        not_novelty_sa = dict()
-        for op in goods:
-            sa_pair_enc = task.encode_sa_pair((s, op))
+        not_novelty_sp = dict()
+        for op, sp in goods:
             if config.use_state_novelty:
-                times_seen = visited_sa[sa_pair_enc]
+                times_seen = visited_sp[sp[1]]
                 if times_seen > 0:
-                    not_novelty_sa[sa_pair_enc] = times_seen
+                    not_novelty_sp[sp[1]] = times_seen
                     continue
                 else:
                     break
             break
         else:
-            op = min(not_novelty_sa, key=not_novelty_sa.get)
+            op = min(not_novelty_sp, key=not_novelty_sp.get)
             if config.verbosity>2:
                 print("WARNING: not novel transition for state:\n{}".format(task.get_printable_rep(s[0])))
             # exitcode = ExitCode.AbstractPolicyNonTerminatingOnTestInstances
             # break
 
         # Execute the selected action
-        sa_pair_enc = task.encode_sa_pair((s, op))
-        visited_sa[sa_pair_enc] += 1
-        sp = task.transition(s, op)
+        # sa_pair_enc = task.encode_sa_pair((s, op))
+        visited_sp[sp[1]] += 1
         path.append(sp[0])
+        spp = task.transition(s, op)
+        path.append(spp[0])
 
-        if sp[0].deadend:
+        if spp[0].deadend:
             exitcode = ExitCode.DeadEndReached
             break
-        if visited_sa[sa_pair_enc] > 3:
+        if visited_sp[sp[1]] > 3:
             exitcode = ExitCode.AbstractPolicyNonTerminatingOnTestInstances
             break
 
         solution.append(encode_operator(s, op, task))
-        s = sp
+        s = spp
 
     return exitcode, solution, path, expanded
 
@@ -176,7 +176,7 @@ def create_action_selection_function_from_transition_policy(config, model_factor
[…]

### 2021-05-12 doc/paper/paper.tex
some changes in encogin and documentation

@@
 
-\subsection{Space Invaders - v0}
+%\subsection{Space Invaders - v0}
+%\subsubsection{Description}
+
+%\subsubsection{Features}
+%\begin{Verbatim}[fontsize=\footnotesize]
+    %(A) Num[col-hv-Agent] [k=1]
+    %(B) Dist[col-hv-white_king;right_col;col-hv-black_king] [k=4]
+%\end{Verbatim}
+
+%\subsubsection{Policy}
+%\begin{Verbatim}[fontsize=\footnotesize]
+%  1. B=0 AND A>0 -> {B INCs, A DECs}, {B NILs, A NILs}, {B INCs, A NILs}
+%  2. B>0 AND A>0 -> {B DECs, A NILs}, {B NILs, A NILs}, {B INCs, A DECs}, {B NILs, A DECs}
+%\end{Verbatim}
+
+%\subsubsection{Example of Game}
+%\begin{Verbatim}[fontsize=\footnotesize]
+
+%\end{Verbatim}
+
+\subsection{Chase - v0}
 \subsubsection{Description}
+In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $rightup$, $right$, $rightdown$, $down$, $leftdown$, $left$, $leftup\}$.
+The agent can move only diagonally and the adversary can move in perpendicular directions.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+#A.....#
+#......#
+#......#
+#.....T#
+\end{Verbatim}
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-    (A) Num[col-hv-Agent] [k=1]
-    (B) Dist[col-hv-white_king;right_col;col-hv-black_king] [k=4]
+  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
+  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
 \end{Verbatim}
 
-\subsubsection{Policy}
+\subsubsection{Policy (without no fixed action space)}
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. B=0 AND A>0 -> {B INCs, A DECs}, {B NILs, A NILs}, {B INCs, A NILs}
-  2. B>0 AND A>0 -> {B DECs, A NILs}, {B NILs, A NILs}, {B INCs, A DECs}, {B NILs, A DECs}
+  1. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, B ↑, C ↓, D ↓}, {A ↓, B ·, C ↓, D ↓}
+  2. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, B ↑, C ↓, D ↑}, {A ↑, B ·, C ↓, D ↑}
+  3. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ↓, C ↓, D ↓}, {A ↑, B ↓, C ↓, D ↓}
+  4. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ↑, C ↑, D ↓}
+  5. A=0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ↓}, {A ↑, B ↑, C ↓, D ↓},
+                                    {A ·, B ·, C ↓, D ↓}, {A ↑, B ·, C ↓, D ↓}
+
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-
-\end{Verbatim}
-
-\subsection{Chase}
-\subsubsection{Description}
-In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $rightup$, $right$, $rightdown$, $down$, $leftdown$, $left$, $leftup\}$.
-The agent can move only diagonally and the adversary can move in perpendicular directions.
-
-\subsubsection{Features}
-\begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col_has_Agent,Exists(right_col,col_has_Target))] [k=5]
-  (B) Bool[And(row_has_Target,Exists(up_row,row_has_Agent))] [k=5]
-  (C) Dist[row_has_Target;up_row;row_has_Agent] [k=4]
-  (D) Dist[col_has_Agent;right_col;col_has_Target] [k=4]
-\end{Verbatim}
-
-\subsubsection{Policy}
-\begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND D>0 AND C>0 -> {A NILs, B NILs, C DECs, D DECs}, {A INCs, B INCs, C DECs, D DECs},
-                                    {A INCs, B NILs, C DECs, D DECs}, {A NILs, B INCs, C DECs, D DECs}
-  2. A>0 AND B=0 AND D>0 AND C>0 -> {A DECs, B INCs, C DECs, D DECs}, {A DECs, B NILs, C DECs, D DECs}
-  3. A=0 AND B=0 AND D>0 AND C=0 -> {A NILs, B INCs, C INCs, D DECs}, {A INCs, B INCs, C INCs, D DECs}
-  4. A=0 AND B=0 AND D=0 AND C>0 -> {A INCs, B INCs, C DECs, D INCs}, {A INCs, B NILs, C DECs, D INCs}
-  5. A=0 AND B>0 AND D>0 AND C>0 -> {A NILs, B DECs, C DECs, D DECs}, {A INCs, B DECs, C DECs, D DECs}
-\end{Verbatim}
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
+1.
 ....... # ....... # ....... # ....T.. # ...T... # ...T... #
@@
 A...... # ....... # ....... # ....... # ....... # ....... #
+
+2.
+T..... # T..... # ...... # ...... # T..... # T.A... # ..A... # ...... #
+...... # ...... # T..... # T..A.. # ...A.. # ...... # T..... # TA.... #
+...... # ....A. # ....A. # ...... # ...... # ...... # ...... # ...... #
+.....A # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
 \end{Verbatim}
 
-\subsection{Shoot}
+\subsection{Chase - v1}
+\subsubsection{Description}
+In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$. The agent can move twice per turn and the adversary can move only once.
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+#A.....#
+#......#
+#......#
+#.....T#
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
+  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
+\end{Verbatim}
+
+\subsubsection{Policy (without no fixed action space)}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A=0 AND B=0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
+  2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
+  3. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ·, C ·, D ↓}, {A ↑, B ·, C ·, D ↓}
+  4. B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
+  5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
+  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
+  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, B ·, C ↓, D ·}, {A ·, B ↑, C ↓, D ·}
+
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  ...... # ...... # ...... # .T.... # .T.... # .T.... # T..... # T..... # T..... #
+  .T.... # .T.... # .T.... # ...... # ....A. # ...A.. # ...A.. # ..A... # .A.... #
+  ...... # .....A # ....A. # ....A. # ...... # ...... # ...... # ...... # ...... #
+  .....A # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+\end{Verbatim}
+
+\subsection{Chase - v2}
+\subsubsection{Description}
+In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$.
+The agent and the adversary can move only once per turn.
+In this version of the Chase the agent cannot always win, because if the adversary plays optimally, the agent will never catch it, but we can compute a policy using the Bad(state) feature.
+Of course now the policy will not be complete.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+#A.....#
+#......#
+#......#
+#.....T#
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Num[Forall(adjacent_col,col-hv-AGENT)] [k=3]
+  (B) Bool[And(row-hv-AGENT,row-hv-TARGET)] [k=3]
+  (C) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (D) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
+  (E) Bool[And(row-hv-TARGET,Forall(adjacent_row,row-hv-AGENT))] [k=5]
+  (F) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
+\end{Verbatim}
+
+\subsubsection{Policy (without no fixed action space)}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. C=0 AND D>0 AND B=0 AND F>0 AND A>0 -> {A ↑, B ·, C ·, D ·, E ·, F ↓},
+                                            {A ·, B ·, C ·, D ·, E ·, F ↓}
+  2. C=0 AND D=0 AND B=0 AND E=0 AND F=0 AND A>0 -> {A ·, B ·, C ·, D ↑, E ↑, F ·}
+  3. C=0 AND D=0 AND B>0 AND E=0 AND F>0 AND A>0 -> {A ↓, B ·, C ↑, D ·, E ·, F ↓}
+  4. C=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ↓}
+  5. C=0 AND D=0 AND B=0 AND E=0 AND A>0 -> {A ·, B ·, C ·, D ↑, E ·, F ·}
+  6. C=0 AND D=0 AND E=0 AND F>0 AND A>0 -> {A ↑, B ·, C ·, D ·, E ·, F ↓},
+                                            {A ·, B ·, C ↑, D ·, E ·, F ↓},
+                                            {A ↓, B ·, C ·, D ·, E ·, F ↓},
+                                            {A ↑, B ·, C ↑, D ·, E ·, F ↓}
+  7. C=0 AND D>0 AND B=0 AND E>0 AND F>0 AND A>0 -> {A ↓, B ·, C ·, D ·, E ·, F ↓},
+                                                    {A ·, B ·, C ·, D ·, E ·, F ↓}
+  8. C>0 AND D=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ·}
+  9. C=0 AND D=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ↓}
+
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  ....... # ....... # ....... # ....... # ....... # ....... # ....T.. #
+  ....... # ....... # ....... # ....... # ....T.. # ....T.. # ....... #
+  ....... # ....... # ....T.. # ....T.. # ....... # ....... # ....... #
+  ....T.. # ....T.. # ....... # ....... # ....... # ...A... # ...A... #
+  ....... # ....... # ....... # ...A... # ...A... # ....... # ....... #
+  ....... # ...A... # ...A... # ....... # ....... # ....... # ....... #
+  ...A... # ....... # ....... # ....... # ....... # ....... # ....... # ...
+
+   ....T.. # .....T. # .....T. # ......T # ......T # ....... #
+   ....... # ....... # ....... # ....... # ....... # ......T #
+   ...A... # ...A... # ....A.. # ....A.. # .....A. # .....A. #
+   ....... # ....... # ....... # ....... # ....... # ....... #
+   ....... # ....... # ....... # ....... # ....... # ....... #
+   ....... # ....... # ....... # ....... # ....... # ....... #
+   ....... # ....... # ....... # ....... # ....... # ....... #
+\end{Verbatim}
+
+\subsection{Shoot - v0}
 \subsubsection{Description}
@@
 This game would be the equivalent of a check with the rook.
-Only that both the rook and the opponent can only move one orthogonal square at a time.
+If the agent manages to get in the opponent's row or column, the agent wins.
+Either the agent or the adversary may take one of the available actions per turn.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+#A.....#
+#......#
+#......#
+#.....T#
+\end{Verbatim}
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-has-Adversary,col-has-Agent)] [k=3]
-  (B) Dist[row-has-Agent;up_row;row-has-Adversary] [k=4]
-  (C) Dist[cell-has-Agent;adjacent_cell;cell-has-Adversary] [k=4]
+  (A) Bool[And(col-hv-AGENT,col-hv-TARGET)] [k=3]
+  (B) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
+
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND C>0 AND B>0 -> {A INCs, B NILs, C NILs}, {A NILs, B DECs, C NILs}
+  1. B>0 AND A=0 AND C>0 -> {A ↑, B ↓, C ·}
+  2. B=0 AND A=0 AND C>0 -> {A ·, B ·, C ↓}
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  A...... # ....... # ....... # ....... # ....... # ....... #
+  ....... # A...... # ....... # ....... # ....... # ....... #
+  ....... # ....... # A...... # ....... # ....... # ....... #
+  ....... # ....... # ....... # A...... # ....... # ....... #
+  ....... # .....T. # ....... # ....... # A...... # ....... #
+  .....T. # ....... # .....T. # ....... # ....... # A.....T #
+  ....... # ....... # ....... # .....T. # ......T # ....... #
+\end{Verbatim}
+
+\subsection{Shoot - v0: Policy with fixed action space}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[Exists(left_col,col-hv-AGENT)] [k=3]
+  (B) Bool[And(col-hv-AGENT,col-hv-TARGET)] [k=3]
+  (C) Bool[And(col-hv-TARGET,Forall(left_col,col-hv-AGENT))] [k=5]
+  (D) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
+
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. do((3,)): {D>0, D ·, A>0, A ·, C>0, C ·, B=0, B ·}
+  2. do((2,)): {D>0, D ·, A>0, A ↓, C>0, C ↓, B=0, B ↑}
+  3. do((2,)): {D>0, D ·, A>0, A ·, C>0, C ↓, B=0, B ↑}
+  4. do((0,)): {D>0, D ↓, A=0, A ·, C>0, C ·, B=0, B ·}
+  5. do((3,)): {D>0, D ·, A=0, A ↑, C=0, C ·, B=0, B ↑}
+  6. do((1,)): {D>0, D ↓, A>0, A ·, C=0, C ·, B=0, B ·}
+  7. do((3,)): {D>0, D ·, A>0, A ·, C ·, B=0, B ↑}
+  8. do((3,)): {D>0, D ·, A=0, A ↑, C=0, C ·, B=0, B ·}
+\end{Verbatim}
+
+\subsection{Shoot - v1}
+\subsubsection{Description}
+In this domain an agent has to shoot an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$.
+This game would be the equivalent of a check with the rook.
+The player who manages to get in the opponent's row before wins, the other player loses.
+Either the agent or the adversary may take one of the available actions per turn.
+In this version of Shoot the agent cannot always win, because if the adversary plays optimally, but we can compute a policy using the Bad(state) feature.
+Of course now the policy will not be complete.
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Num[Forall(adjacent_col,col-hv-AGENT)] [k=3]
+  (B) Bool[Exists(up_row,Exists(up_row,row-hv-AGENT))] [k=5]
+  (C) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (D) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
+  (E) Dist[row-hv-AGENT;up_row;row-hv-TARGET] [k=4]
+  (F) Dist[col-hv-AGENT;right_col;col-hv-TARGET] [k=4]
+
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. C=0 AND D=0 AND B>0 AND F>0 AND E>0 AND A>0 -> {A ↓, B ·, C ·, D ·, E ·, F ↓},
+                                                    {A ·, B ·, C ·, D ·, E ↑, F ·},
+                                                    {A ·, B ·, C ·, D ·, E ·, F ↑},
+                                                    {A ↑, B ·, C ·, D ·, E ·, F ↓}
+  2. C=0 AND D=0 AND B=0 AND F>0 AND E>0 AND A>0 -> {A ↓, B ·, C ·, D ·, E ·, F ·},
+                                                    {A ·, B ·, C ·, D ·, E ↓, F ·},
+                                                    {A ·, B ↑, C ·, D ·, E ↓, F ·}
+  3. D>0 AND F>0 AND E>0 AND A>0 -> {A ·, B ·, C ·, D ↓, E ↓, F ·}
+  4. C>0 AND B>0 AND F>0 AND E>0 AND A>0 -> {A ↑, B ·, C ↓, D ·, E ·, F ↓},
+                                            {A ↓, B ·, C ↓, D ·, E ·, F ↓}
+  5. C>0 AND D>0 AND B=0 AND F>0 AND E>0 AND A>0 -> {A ↓, B ·, C ↓, D ·, E ·, F ↓},
+                                                    {A ↑, B ·, C ↓, D ·, E ·, F ↓}
+  6. D>0 AND B=0 AND F>0 AND E>0 AND A>0 -> {A ·, B ↑, C ·, D ↓, E ↓, F ·}
+  7. C>0 AND F>0 AND E>0 AND A>0 -> {A ↓, B ·, C ↓, D ·, E ·, F ↓},
+                                    {A ↑, B ·, C ↓, D ·, E ·, F ↓},
+                                    {A ·, B ·, C ↓, D ·, E ·, F ↓}
+  8. D>0 AND B>0 AND F>0 AND E>0 AND A>0 -> {A ·, B ↓, C ·, D ↓, E ↓, F ·}
+  9. C>0 AND D>0 AND F>0 AND E>0 AND A>0 -> {A ·, B ·, C ↓, D ·, E ·, F ↓}
+  10. C>0 AND D=0 AND B>0 AND F>0 AND E>0 AND A>0 -> {A ·, B ·, C ↓, D ·, E ·, F ↓}
 \end{Verbatim}

### 2021-05-12 experiments/chase.py

@@ -14,6 +14,7 @@ chase_params = Bunch({
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
     'use_adjacency': {COL_S, ROW_S},
+    'use_bidirectional': {},
     'sorts_to_use': {COL_S, ROW_S},
     'unary_predicates': {},
     'can_build_walls': False,
@@ -48,16 +49,16 @@ def experiments():
         print_denotations=True,
         print_hstar_in_feature_matrix=False,
 
-        verbosity=1,
+        verbosity=0,
         initial_sample_size=20,
         refinement_batch_size=50,
         maxsat_iter=10,
 
-        allow_bad_states=False,
+        allow_bad_states=True,
         decreasing_transitions_must_be_good=False,
         allow_cycles=False,
         use_action_ids=False,
-        use_weighted_tx=False,
+        use_weighted_tx=True,
         distinguish_goals=True,
 
         sampling_strategy="full",

### 2021-05-12 experiments/domain_params.py

@@ -1,15 +1,0 @@
-from gpl.utils import Bunch
-from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
-
-
-space_invaders_params = Bunch({
-    'domain_name': 'space_invaders',
-    'use_player_as_feature': False,
-    'map_cells': False,
-    'use_diagonals_for_map_cells': False,
-    'use_adjacency': False,
-    'sorts_to_use': {COL_S, ROW_S},
-})
-
-
-

### 2021-05-12 experiments/shoot.py

@@ -14,8 +14,9 @@ shoot_params = Bunch({
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
     'use_adjacency': {COL_S, ROW_S},
-    'sorts_to_use': {COL_S, ROW_S, CELL_S},
-    'adv_can_shoot': False,
+    'use_bidirectional': {COL_S, ROW_S},
+    'sorts_to_use': {COL_S, ROW_S},
+    'adv_can_shoot': True,
     'unary_predicates': {}
 })
 
@@ -28,7 +29,6 @@ def experiments():
         parameter_generator=None,
         v_slack=2,
         acyclicity='topological',
-        discrete_action_space=False,
         use_incremental_refinement=False,
     )
 
@@ -36,9 +36,9 @@ def experiments():
     exps["1"] = update_dict(
         base,
         # instances=[0, 1, 2, 3, 4, 5, 6],
-        instances=[0],
+        instances=[0, 1],
         test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8],
-        max_concept_size=5,
+        max_concept_size=8,
         distance_feature_max_complexity=4,
         concept_generation_timeout=15000,
         cond_feature_max_complexity=0,
@@ -54,11 +54,11 @@ def experiments():
 
         sampling_strategy='full',
 
-        allow_bad_states=False,
+        allow_bad_states=True,
         decreasing_transitions_must_be_good=False,
         allow_cycles=False,
-        use_action_ids=False,
-        use_weighted_tx=False,
+        use_action_ids=True,
+        use_weighted_tx=True,
         use_state_novelty=True,
         distinguish_goals=True,
 

### 2021-05-12 experiments/space_invaders.py

@@ -11,9 +11,11 @@ space_invaders_params = Bunch({
     'use_player_as_feature': False,
     'map_cells': False,
     'use_diagonals_for_map_cells': False,
-    'use_adjacency': {COL_S, ROW_S},
-    'sorts_to_use': {CELL_S, COL_S, ROW_S},
+    'use_adjacency': {COL_S},
+    'use_bidirectional': {COL_S},
+    'sorts_to_use': {CELL_S, COL_S},
     'unary_predicates': {},
+    'agent_has_to_shoot': False,
 })
 
 def experiments():
@@ -34,7 +36,7 @@ def experiments():
         base,
         # instances=[0, 10],
         # instances=[0, 4, 8, 10],
-        instances=[4],
+        instances=[0, 4],
         # instances=[10,],
         # instances=[10],
         # instances=[0, 3, 4, 8, 10],
@@ -48,7 +50,7 @@ def experiments():
         print_denotations=True,
         print_hstar_in_feature_matrix=False,
 
-        verbosity=1,
+        verbosity=0,
         initial_sample_size=100,
         refinement_batch_size=200,
         maxsat_iter=20,
@@ -56,15 +58,15 @@ def experiments():
         allow_bad_states=True,
         decreasing_transitions_must_be_good=False,
         allow_cycles=False,
-        use_action_ids=False,
+        use_action_ids=True,
         use_weighted_tx=False,
         use_state_novelty=True,
         distinguish_goals=True,
 
         sampling_strategy="full",
 
-        # skip_train_steps=[0, 1, 2],  # do not generate features twice!
-        skip_train_steps=[],
+        skip_train_steps=[0, 1, 2, 3],
+        # skip_train_steps=[],
         # rollouts
         # num_episodes=1,
         # num_rollouts=1,

### 2021-05-12 src/d2l/src/sltp/separation.py

@@ -372,7 +372,7 @@ class TransitionActionClassificationPolicy:
                         print(f'\t\t{atom} not satisfied by transition values ({feat.denotation(m0)}, {feat.denotation(m1)})')
                     return False
         if ma: # meaninf that we want to exploid a set of actions A (grounded, common, and fixed)
-            if (ma not in actions):
+            if ma not in actions:
                 if explain:
                     print(f'Action {ma} is not ({a})')
                 return False
@@ -382,7 +382,7 @@ class TransitionActionClassificationPolicy:
         self.print_header()
         print("Policy:")
         for i, (clause, a) in enumerate(self.dnf, start=1):
-            print(f"  {i}. " + f"do({a}): " + self.print_clause(clause))
+            print(f"  {i}. " + f"do({a}): " + self.print_clause(clause, True))
 
     def print_aaai20(self, simplified=False):
         self.print_header()
@@ -415,7 +415,7 @@ class TransitionActionClassificationPolicy:
                 effect_tmp = list()
                 for e in effect:
                     f_s, e_s = str(e).split(' ')
-                    effect_tmp.append("{} {}".format(self.get_feature_key(f_s), e_s))
+                    effect_tmp.append("{} {}".format(self.get_feature_key(f_s), self.get_simplified_val(e_s)))
                 fc = '{' + ', '.join(sorted(effect_tmp)) + '}'
                 if fc not in feature_conds_tmp:
                     feature_conds_tmp.append(fc)
@@ -426,6 +426,15 @@ class TransitionActionClassificationPolicy:
         #     state_conds = ' AND '.join(sorted(map(str, statef)))
         #     feature_conds = ', '.join(self.print_effect_list(e) for e in transitionf)
         #     print(f"  {i}. {state_conds} -> {feature_conds}")
+
+    def get_simplified_val(self, val):
+        return {
+            "=0": "=0",
+            ">0": ">0",
+            "INCs": u"\u2191",
+            "NILs": "·",
+            "DECs": u"\u2193",
+        }[val]
 
     @staticmethod
     def print_effect_list(effect):
@@ -441,7 +450,7 @@ class TransitionActionClassificationPolicy:
 
     def __assign_keys_to_featuers(self):
         import string
-        ASCII = string.printable[36:62]
+        ASCII = string.printable[36:62] # A..Z
         for f in self.features:
             ASCII, b = ASCII[1:], ASCII[0]
[…]

### 2021-05-12 src/gpl/domains/grid_games/domain.py

@@ -48,7 +48,7 @@ def load_general_lang(lang, statics, env):
         if sort in params.use_adjacency:
             lang.predicate(f'{ADJACENT}_{sort}', sort, sort)
             statics.add(f'{ADJACENT}_{sort}')
-        else:
+        if sort in params.use_bidirectional:
             for d in GRID_DIRECTIONS[sort]:
                 lang.predicate(f'{d}_{sort}', sort, sort)
                 statics.add(f'{d}_{sort}')
@@ -91,7 +91,7 @@ def load_general_problem(problem, lang, rep, env):
             pass
         elif sort in params.use_adjacency:
             problem.init.add(lang.get(f'{ADJACENT}_{sort}'), const, lang.get(CONST[sort](new_r, new_c)))
-        else:
+        if sort in params.use_bidirectional:
             problem.init.add(lang.get(f'{direction}_{sort}'), const, lang.get(CONST[sort](new_r, new_c)))
 
     for (row, col, sort), const in map_sorts.items():

### 2021-05-12 src/gpl/domains/grid_games/envs/chase.py

@@ -44,14 +44,14 @@ LEFTDOWN = 7
 
 
 AGENT_ACTION_SPACE = {
-    # UP,
-    # DOWN,
-    # RIGHT,
-    # LEFT,
-    LEFTUP,
-    RIGHTUP,
-    RIGHTDOWN,
-    LEFTDOWN,
+    UP,
+    DOWN,
+    RIGHT,
+    LEFT,
+    # LEFTUP,
+    # RIGHTUP,
+    # RIGHTDOWN,
+    # LEFTDOWN,
 }
 
 ENV_ACTION_SPACE = {

### 2021-05-12 src/gpl/domains/grid_games/envs/shoot.py

@@ -152,30 +152,56 @@ class Env(object):
         valid_actions = self.available_actions(rep)
         r_wk, c_wk = runnable_position(rep.grid, WHITE)
         r_bk, c_bk = runnable_position(rep.grid, BLACK)
-        if r_wk - r_bk == -1:
-            if UP in valid_actions:
-                return UP
-        if r_wk - r_bk == 1:
-            if DOWN in valid_actions:
-                return DOWN
-        if c_wk - c_bk == 1:
-            if RIGHT in valid_actions:
-                return RIGHT
-        if c_wk - c_bk == -1:
-            if LEFT in valid_actions:
-                return LEFT
-        if r_wk - r_bk == -2:
-            if DOWN in valid_actions:
-                return DOWN
-        if r_wk - r_bk == 2:
-            if UP in valid_actions:
-                return UP
-        if c_wk - c_bk == 2:
-            if LEFT in valid_actions:
-                return LEFT
-        if c_wk - c_bk == -2:
-            if RIGHT in valid_actions:
-                return RIGHT
+        if self.params.adv_can_shoot:
+            if r_wk - r_bk == -1:
+                if UP in valid_actions:
+                    return UP
+            if r_wk - r_bk == 1:
+                if DOWN in valid_actions:
+                    return DOWN
+            if c_wk - c_bk == 1:
+                if RIGHT in valid_actions:
+                    return RIGHT
+            if c_wk - c_bk == -1:
+                if LEFT in valid_actions:
+                    return LEFT
+            if r_wk - r_bk == -2:
+                if DOWN in valid_actions:
+                    return DOWN
+            if r_wk - r_bk == 2:
+                if UP in valid_actions:
+                    return UP
+            if c_wk - c_bk == 2:
+                if LEFT in valid_actions:
+                    return LEFT
+            if c_wk - c_bk == -2:
+                if RIGHT in valid_actions:
+                    return RIGHT
+        else:
+            if r_wk - r_bk == 1:
+                if UP in valid_actions:
+                    return UP
+            if r_wk - r_bk == -1:
+                if DOWN in valid_actions:
+                    return DOWN
+            if c_wk - c_bk == -1:
+                if RIGHT in valid_actions:
+                    return RIGHT
+            if c_wk - c_bk == 1:
+                if LEFT in valid_actions:
+                    return LEFT
+            if r_wk - r_bk == 2:
+                if DOWN in valid_actions:
+                    return DOWN
+            if r_wk - r_bk == -2:
[…]

### 2021-05-12 src/gpl/tester.py

@@ -130,6 +130,8 @@ def run_test(config, search_policy, task, instance_name, rng):
                 # we know we are not complete
                 # TODO: take bad states into account
                 goods = successors
+                if (config.verbosity>2):
+                    logging.info("WARNING: Not complete in state")
             else:
                 exitcode = ExitCode.AbstractPolicyNotCompleteOnTestInstances
                 break
@@ -214,6 +216,15 @@ def run(config, data, rng):
 
     if data.d2l_policy is None:
         return ExitCode.NotPolicySpecified, dict()
+    else:
+        data.d2l_policy.minimize()
+        if config.use_action_ids:
+            print("Policy (with actions):")
+            data.d2l_policy.print()
+        else:
+            print("\nPOLICY:")
+            data.d2l_policy.print_aaai20()
+        print('')
 
     def get_policy(model_factory, static_atoms, data):
         policy = create_action_selection_function_from_transition_policy(config, model_factory, static_atoms,

### 2021-05-12 src/gpl/train.py

@@ -45,7 +45,13 @@ def train(config, data, rng, train_steps=[], show_steps_only=False):
 
     data = post_process_data(config, data)
 
-    return exitcode, data.to_dict()
+    try:
+        return exitcode, data.to_dict()
+    except:
+        return ExitCode.Success, dict()
+
+
+
 
 
 def run_step(step, config, data, rng):

### 2021-05-24 doc/paper/paper.tex
minor change
back

@@
 
-%\subsection{Space Invaders - v0}
-%\subsubsection{Description}
+\subsection{Space Invaders - v0}
+\subsubsection{Description}
+In this domain the agent can shoot, move to the right or to the left.
+To win the agent has to kill all the opponents, for this he must shoot each of them.
+The agent kills an opponent if he shoots while being in the same column, and he can only kill one for each shoot.
+The adversary has three possible actions, left, right and down, all the adversaries move in the same direction.
+The agent cannot be destroyed by the opponents.
 
-%\subsubsection{Features}
-%\begin{Verbatim}[fontsize=\footnotesize]
-    %(A) Num[col-hv-Agent] [k=1]
-    %(B) Dist[col-hv-white_king;right_col;col-hv-black_king] [k=4]
-%\end{Verbatim}
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  0: Num[cell-has-martian] [k=1]
+	1: Num[cell-has-target_martian] [k=1]
+	2: Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]]
+\end{Verbatim}
 
-%\subsubsection{Policy}
-%\begin{Verbatim}[fontsize=\footnotesize]
-%  1. B=0 AND A>0 -> {B INCs, A DECs}, {B NILs, A NILs}, {B INCs, A NILs}
-%  2. B>0 AND A>0 -> {B DECs, A NILs}, {B NILs, A NILs}, {B INCs, A DECs}, {B NILs, A DECs}
-%\end{Verbatim}
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. C=0 AND A>0 AND B>0 -> {A ↓, B ↑, C ↑}, {A ·, B ↓, C ·}, {A ↓, B ·, C ↑}
+  2. C=0 AND A=0 AND B>0 -> {A ·, B ↓, C ↑}
+  3. C>0 AND B>0 -> {A ·, B ·, C ↓}
+  4. C>0 AND A=0 AND B>0 -> {A ·, B ·, C ↓}
+\end{Verbatim}
 
-%\subsubsection{Example of Game}
-%\begin{Verbatim}[fontsize=\footnotesize]
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
 
-%\end{Verbatim}
+\end{Verbatim}
 
@@
 
-\subsubsection{Policy (without no fixed action space)}
+\subsubsection{Policy (with no fixed action space)}
+
 \begin{Verbatim}[fontsize=\footnotesize]
@@
 
-\subsubsection{Policy (without no fixed action space)}
+\subsubsection{Policy (with no fixed action space)}
 \begin{Verbatim}[fontsize=\footnotesize]
@@
 \subsection{Shoot - v0: Policy with fixed action space}
+
+\subsubsection{Action space}
+\begin{Verbatim}[fontsize=\footnotesize]
+UP = 0
+DOWN = 1
+RIGHT = 2
+LEFT = 3
+\end{Verbatim}
 

### 2021-05-24 experiments/chase.py

@@ -1,12 +1,11 @@
 import math
 
 from sltp.util.misc import update_dict
-
-
 from gpl.domains.grid_games.domain import Domain
-
 from gpl.utils import Bunch
 from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
+from gpl.domains.grid_games.envs.chase import RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, UP, DOWN, RIGHT, LEFT
+from gpl.domains.grid_games.grammar.objects import PLAYER1, PLAYER2
 
 chase_params = Bunch({
     'domain_name': 'chase',
@@ -18,6 +17,12 @@ chase_params = Bunch({
     'sorts_to_use': {COL_S, ROW_S},
     'unary_predicates': {},
     'can_build_walls': False,
+    'ava_actions': {
+        PLAYER1: {RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP},
+        # PLAYER1: {UP, DOWN, RIGHT, LEFT},
+        PLAYER2: {UP, DOWN, RIGHT, LEFT}},
+    'max_actions': {PLAYER1: 1,
+                    PLAYER2: 1},
 })
 
 def experiments():
@@ -31,14 +36,7 @@ def experiments():
         acyclicity='topological',
         discrete_action_space=False,
         use_incremental_refinement=False,
-    )
 
-    exps = dict()
-    exps["1"] = update_dict(
-        base,
-        instances=[0],
-        # instances=[0, 15],
-        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16],
         max_concept_size=5,
         distance_feature_max_complexity=4,
         concept_generation_timeout=15000,
@@ -48,7 +46,7 @@ def experiments():
         print_denotations=True,
         print_hstar_in_feature_matrix=False,
 
-        verbosity=0,
+        verbosity=3,
         initial_sample_size=20,
         refinement_batch_size=50,
         maxsat_iter=10,
@@ -73,6 +71,32 @@ def experiments():
         train_instances_to_expand=list(range(1000)),
         max_states_expanded=math.inf,
         use_state_novelty=True,
+    )
+
+    # version 1:
+    # Agent move diagonal, Adv Ortogonal
+    # Agent has 1 move, Adv has 1
+    exps = dict()
[…]

### 2021-05-24 experiments/ct.py

@@ -1,28 +1,24 @@
 import math
-
 from sltp.util.misc import update_dict
-
-
 from gpl.domains.grid_games.domain import Domain
-
 from gpl.utils import Bunch
-from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
-from gpl.domains.grid_games.envs.checkmate_tactic import CHECKMATE, STALEMATE, N_MOVE
+from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S, D1_S, D2_S
+from gpl.domains.grid_games.envs.checkmate_tactic import CHECKMATE, STALEMATE, N_MOVE, CHECK
 
-CHECKMATE_IN_N = 1
-MOVES = {"{}_{}".format(N_MOVE, i) for i in range(CHECKMATE_IN_N + 1)}
 
 ct_params = Bunch({
     'domain_name': 'checkmate_tactic',
-    'use_player_as_feature': False,
+    'use_player_as_feature': True,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
-    'use_adjacency': {COL_S, ROW_S, CELL_S},
-    'use_bidirectional': {COL_S, ROW_S, CELL_S},
-    'sorts_to_use': {CELL_S, COL_S, ROW_S},
-    'n_moves': CHECKMATE_IN_N,
-    'unary_predicates': MOVES,
+    'use_adjacency': {CELL_S},
+    'use_bidirectional': {},
+    'sorts_to_use': {COL_S, ROW_S, CELL_S},
+    'n_moves': 1,
+    'unary_predicates': {},
+    # 'unary_predicates': {"{}_{}".format(N_MOVE, i) for i in range(CHECKMATE_IN_N + 1)},
     # 'unary_predicates': {STALEMATE, CHECKMATE}
+    'game_version': 0,
 })
 
 def experiments():
@@ -36,14 +32,7 @@ def experiments():
         acyclicity='topological',
         discrete_action_space=False,
         use_incremental_refinement=False,
-    )
 
-    exps = dict()
-    exps["1"] = update_dict(
-        base,
-        instances=[0],
-        # instances=[0],
-        test_instances=[0, 1, 2, 3],
         max_concept_size=5,
         distance_feature_max_complexity=4,
         concept_generation_timeout=15000,
@@ -53,7 +42,7 @@ def experiments():
         print_denotations=True,
         print_hstar_in_feature_matrix=False,
 
[…]

### 2021-05-24 experiments/deliver.py

@@ -1,76 +1,0 @@
-import math
-
-from sltp.util.misc import update_dict
-
-
-from gpl.domains.grid_games.domain import Domain
-
-from gpl.utils import Bunch
-from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
-
-deliver_params = Bunch({
-    'domain_name': 'deliver',
-    'use_player_as_feature': False,
-    'map_cells': True,
-    'use_diagonals_for_map_cells': True,
-    'use_adjacency': True,
-    'sorts_to_use': {CELL_S, COL_S, ROW_S},
-})
-
-def experiments():
-    base = dict(
-        domain=Domain(deliver_params),
-        maxsat_encoding="d2l",
-        num_states="all",
-        concept_generator=None,
-        parameter_generator=None,
-        v_slack=2,
-        acyclicity='topological',
-        discrete_action_space=False,
-        use_incremental_refinement=False,
-    )
-
-    exps = dict()
-    exps["1"] = update_dict(
-        base,
-        # instances=[5,],
-        instances=[0, 2, 3, 4, 5,],
-        test_instances=[0, 2, 3, 4, 5, 6],
-        max_concept_size=5,
-        distance_feature_max_complexity=4,
-        concept_generation_timeout=15000,
-        cond_feature_max_complexity=0,
-        comparison_features=False,
-        generate_goal_concepts=True,
-        print_denotations=True,
-        print_hstar_in_feature_matrix=False,
-
-        verbosity=1,
-        initial_sample_size=10,
-        refinement_batch_size=20,
-        maxsat_iter=10,
-
-        allow_bad_states=False,
-        decreasing_transitions_must_be_good=False,
-        allow_cycles=False,
-        use_action_ids=True,
-        use_weighted_tx=False,
-        use_state_novelty=True,
-        distinguish_goals=True,
-        sampling_strategy="full",
-
-        # skip_train_steps=[0, 1, 2],  # do not generate features twice!
-        skip_train_steps=[],
-        # rollouts
-        # num_episodes=1,
-        # num_rollouts=1,
-        # rollout_depth=2,
-        # train_instances_to_expand=[],
-        train_instances_to_expand=list(range(1000)),
-        max_states_expanded=math.inf,
-    )
-
-    return exps
-
-
-

### 2021-05-24 experiments/nim.py

@@ -1,3 +1,4 @@
+import copy
 import math
 
 from sltp.util.misc import update_dict
@@ -9,23 +10,25 @@ from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S, D1_S, 
 from gpl.domains.grid_games.envs.nim import ONLY_ONE_LEFT
 
 
-shoot_params = Bunch({
+nim_params = Bunch({
     'domain_name': 'nim',
     'use_player_as_feature': True,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
-    'use_adjacency': {},
+    'use_adjacency': {CELL_S},
     'use_bidirectional': {CELL_S},
     'sorts_to_use': {CELL_S},
     'last_player_win': True,
     'unary_predicates': {},
-    'mark_top_token': True,
-    'mark_bottom_token': True,
+    'predicates_arity_1': {},
+    'mark_top_token': False,
+    'mark_bottom_token': False,
+    'game_version': 0,
 })
 
 def experiments():
     base = dict(
-        domain=Domain(shoot_params),
+        domain=Domain(nim_params),
         maxsat_encoding="d2l",
         num_states="all",
         concept_generator=None,
@@ -33,23 +36,16 @@ def experiments():
         v_slack=2,
         acyclicity='topological',
         use_incremental_refinement=False,
-    )
-
-    exps = dict()
-    exps["1"] = update_dict(
-        base,
-        instances=[11],
-        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11],
         max_concept_size=5,
         distance_feature_max_complexity=4,
         concept_generation_timeout=15000,
         cond_feature_max_complexity=0,
-        comparison_features=False,
-        generate_goal_concepts=False,
+        comparison_features=True,
+        generate_goal_concepts=True,
         print_denotations=True,
         print_hstar_in_feature_matrix=False,
 
-        verbosity=3,
+        verbosity=2,
         initial_sample_size=50,
         refinement_batch_size=10,
         maxsat_iter=3,
@@ -60,7 +56,7 @@ def experiments():
         decreasing_transitions_must_be_good=False,
         allow_cycles=False,
         use_action_ids=False,
-        use_weighted_tx=True,
+        use_weighted_tx=False,
         use_state_novelty=True,
[…]

### 2021-05-24 experiments/pick_packages.py

@@ -1,73 +1,0 @@
-import math
-
-from sltp.util.misc import update_dict
-from gpl.domains.grid_games.domain import Domain
-
-from gpl.utils import Bunch
-from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
-pick_package_params = Bunch({
-    'domain_name': 'pick_packages',
-    'use_player_as_feature': False,
-    'map_cells': True,
-    'use_diagonals_for_map_cells': True,
-    'use_adjacency': False,
-    'sorts_to_use': {CELL_S, COL_S, ROW_S},
-})
-
-def experiments():
-    base = dict(
-        domain=Domain(pick_package_params),
-        maxsat_encoding="d2l",
-        num_states="all",
-        concept_generator=None,
-        parameter_generator=None,
-        v_slack=2,
-        acyclicity='topological',
-        use_incremental_refinement=False,
-    )
-
-    exps = dict()
-    exps["1"] = update_dict(
-        base,
-        # instances=[0,],
-        instances=[0, 1, 2, 3, 4, 8, 10],
-        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12],
-        max_concept_size=5,
-        distance_feature_max_complexity=4,
-        concept_generation_timeout=15000,
-        cond_feature_max_complexity=0,
-        comparison_features=False,
-        generate_goal_concepts=False,
-        print_denotations=True,
-        print_hstar_in_feature_matrix=False,
-
-        verbosity=1,
-        initial_sample_size=10,
-        refinement_batch_size=50,
-        maxsat_iter=10,
-
-        allow_bad_states=False,
-        decreasing_transitions_must_be_good=False,
-        allow_cycles=False,
-        use_action_ids=False,
-        use_weighted_tx=False,
-        use_state_novelty=True,
-        distinguish_goals=True,
-        sampling_strategy="full",
-
-        # skip_train_steps=[0, 1, 2],  # do not generate features twice!
-        skip_train_steps=[],
-
-        # rollouts
-        # num_episodes=1,
-        # num_rollouts=10,
-        # rollout_depth=10,
-        # train_instances_to_expand=[],
-        train_instances_to_expand=list(range(1000)),
-        max_states_expanded=math.inf,
-    )
-
-    return exps
-
-
-

### 2021-05-24 experiments/run.py

@@ -1,5 +1,5 @@
 #!/usr/bin/env python3
-
+import os.path
 import sys
 
 from gpl.defaults import generate_experiment
@@ -29,7 +29,7 @@ def do(expid, steps=None, workspace=None, show_steps_only=False):
     if workspace is not None:
         parameters["workspace"] = workspace
 
-    experiment = generate_experiment(expid, **parameters)
+    experiment, _ = generate_experiment(expid, **parameters)
 
     if show_steps_only:
         console.print_hello()
@@ -38,7 +38,6 @@ def do(expid, steps=None, workspace=None, show_steps_only=False):
         return
 
     experiment.run(steps)
-
 
 if __name__ == "__main__":
     args = setup_argparser().parse_args(sys.argv[1:])

### 2021-05-24 src/d2l/src/sltp/separation.py

@@ -441,12 +441,25 @@ class TransitionActionClassificationPolicy:
         return '{' + ', '.join(sorted(map(str, effect))) + '}'
 
     def print_header(self):
-        max_k = max(f.feature.complexity() for f in self.features)
-        total_k = sum(f.feature.complexity() for f in self.features)
+        max_k = 0
+        total_k = 0
+        for f in self.features:
+            try:
+                c = f.feature.complexity()
+            except:
+                c = 0
+            max_k =max({c, max_k})
+            total_k += c
+        # max_k = max(f.feature.complexity() for f in self.features)
+        # total_k = sum(f.feature.complexity() for f in self.features)
         print(f"Features (#: {len(self.features)}; total k: {total_k}; max k = {max_k}):")
         for f in self.features:
             key = self.get_feature_key(str(f))
-            print(f"  ({key}) {f} [k={f.feature.complexity()}]")
+            try:
+                c = f.feature.complexity()
+            except:
+                c = 0
+            print(f"  ({key}) {f} [k={c}]")
 
     def __assign_keys_to_featuers(self):
         import string

### 2021-05-24 src/gpl/defaults.py

@@ -8,12 +8,6 @@ from sltp.util.command import create_experiment_workspace
 from sltp.util.defaults import get_experiment_class
 from sltp.util.misc import extend_namer_to_all_features
 
-# from generalization_grid_games.envs import two_pile_nim as tpn
-# from generalization_grid_games.envs import stop_the_fall as stf
-# from generalization_grid_games.envs import chase as ec
-# from generalization_grid_games.envs import checkmate_tactic as ct
-# from generalization_grid_games.envs import reach_for_the_star as rfts
-
 BASEDIR = os.path.dirname(os.path.dirname(os.path.dirname(os.path.realpath(__file__))))
 BENCHMARK_DIR = os.path.join(BASEDIR, 'benchmarks')
 
@@ -156,7 +150,7 @@ def generate_experiment(expid, **kwargs):
         verbosity=0,
         # acyclicity='reachability',
         # acyclicity='topological',
-        encodings_dir='~/Desktop/encodings_d2l',
+        encodings_dir='',
         sampling_strategy='random',
         optimal_steps=3,
         consistency_bound=2,
@@ -178,9 +172,7 @@ def generate_experiment(expid, **kwargs):
     steps = generate_pipeline(**parameters)
     exp = parameters["experiment_class"](steps, parameters)
 
-    # train_steps = generate_train(**parameters)
-    # exp = generate_train(**parameters)
-    return exp
+    return exp, parameters
 
 
 def default_feature_namer(s):

### 2021-05-24 src/gpl/domains/adversarial_domains/task.py

@@ -24,8 +24,7 @@ class Task(ITask):
     def __init_task(self, instance_name):
         rep = self.env.init_instance(instance_name)
         self.grammar = Grammar(self.get_domain_name(), self.params)
-        encoded_s = self.grammar.encode_state(rep)
-        self.initial_state = (rep, encoded_s)
+        self.initial_state = (rep, self.encode_state(rep))
 
     def encode_state(self, rep):
         return self.grammar.encode_state(rep)

### 2021-05-24 src/gpl/domains/adversarial_domains/utils.py

@@ -1,0 +1,22 @@
+from .grammar.objects import OBJECTS, BLACK_KING, WHITE_KING
+import numpy as np
+import json
+import os.path
+
+def identify_margin(r, c, nrows, ncols):
+    if r < 0 and 0 <= c < ncols:
+        return OBJECTS.margin['m0']
+    if r == nrows and 0 <= c < ncols:
+        return OBJECTS.margin['m1']
+    if 0 <= r < nrows and c == ncols:
+        return OBJECTS.margin['m2']
+    if 0 <= r < nrows and c < 0:
+        return OBJECTS.margin['m3']
+    if r < 0 and c == ncols:
+        return OBJECTS.margin['m4']
+    if r == nrows and c == ncols:
+        return OBJECTS.margin['m5']
+    if r < 0 and c < 0:
+        return OBJECTS.margin['m6']
+    if r == nrows and c < 0:
+        return OBJECTS.margin['m7']

### 2021-05-24 src/gpl/domains/grid_games/envs/chase.py

@@ -76,11 +76,6 @@ ACTION_MOVE_DIRECTION = {
     LEFTDOWN: (1, -1),
 }
 
-MAX_ACTIONS_BY_TURN = {
-    WHITE:2,
-    BLACK:1,
-}
-
 MOVE_ACTION = {
     ACTION_MOVE_DIRECTION[UP]: UP,
     ACTION_MOVE_DIRECTION[DOWN]: DOWN,
@@ -100,7 +95,7 @@ class Env(object):
 
     def act(self, rep, action):
         layout = rep.grid
-        assert rep.nact < MAX_ACTIONS_BY_TURN[rep.player]
+        assert rep.nact < self.params.max_actions[rep.player] + 1
         assert not terminated(rep)
         valid_actions = self.available_actions(rep)
         try:
@@ -115,15 +110,13 @@ class Env(object):
             l = new_rep.grid
             assert l[action] == EMPTY
             l[action] = WALL
-            if rep.nact + 1 < MAX_ACTIONS_BY_TURN[rep.player]:
-                new_rep.grid = l
+            new_rep.grid = l
+            if rep.nact < self.params.max_actions[rep.player]:
                 new_rep.nact += 1
-                return self.__update_rep(new_rep)
             else:
-                new_rep.grid = l
-                new_rep.nact = 0
+                new_rep.nact = 1
                 new_rep.player = opposite_color(rep.player)
-                return self.__update_rep(new_rep)
+            return self.__update_rep(new_rep)
 
     def __rep_after_move(self, rep, action):
         new_rep = copy.deepcopy(rep)
@@ -143,15 +136,14 @@ class Env(object):
         #     l[new_r, new_c] = piece
         l[new_r, new_c] = piece
         l[old_r, old_c] = EMPTY
-        if rep.nact + 1 < MAX_ACTIONS_BY_TURN[rep.player]:
-            new_rep.grid = l
+        new_rep = copy.deepcopy(rep)
+        new_rep.grid = l
+        if rep.nact + 1 < self.params.max_actions[rep.player]:
             new_rep.nact += 1
-            return self.__update_rep(new_rep)
         else:
-            new_rep.grid = l
             new_rep.nact = 0
             new_rep.player = opposite_color(rep.player)
-            return self.__update_rep(new_rep)
+        return self.__update_rep(new_rep)
 
     def __update_rep(self, rep):
         updated_rep = rep.to_dict()
@@ -159,6 +151,7 @@ class Env(object):
             updated_rep['goal'] = True
[…]

### 2021-05-24 src/gpl/domains/grid_games/envs/checkmate_tactic.py

@@ -57,6 +57,7 @@ DIRECTIONS = {
 }
 
 # Unary predicates
+CHECK = 'check'
 CHECKMATE = 'checkmate'
 STALEMATE = 'stalemate'
 
@@ -169,7 +170,7 @@ class Env(object):
         rep = {u: False for u in self.params.unary_predicates}
         rep['nmoves'] = 0
         rep[f"{N_MOVE}_0"] = True
-        rep['grid'] = generate_gird(key)
+        rep['grid'] = generate_gird(key, self.params)
         rep['player'] = WHITE
         rep['goal'] = False
         rep['deadend'] = False
@@ -197,6 +198,18 @@ def checkmate(rep):
         return False
     return False
 
+def check(rep):
+    layout = rep.grid
+    assert BLACK_KING in layout
+    if rep.player == BLACK:
+        king_pos = np.argwhere(layout == BLACK_KING)[0]
+        valid_moves = PIECE_VALID_MOVES[BLACK_KING](king_pos, layout)
+        if len(valid_moves) == 0:
+            attacking_mask = get_attacking_mask(layout, opposite_color(rep.player))
+            if attacking_mask[king_pos[0], king_pos[1]]:
+                return True
+        return False
+    return False
 
 def stale_mate(rep):
     layout = rep.grid
@@ -307,8 +320,8 @@ def cool_piece_valid_moves(pos, layout, color, piece):
 #         grid[cell_white_tower] = WHITE_TOWER
 #     return grid
 
-def generate_gird(key):
-    return LAYOUTS_CHECK_IN_ONE[key]
+def generate_gird(key, params):
+    return LAYOUTS[params.game_version][key]
 
 def generate_check_in_one(shapes, piece):
     grids = list()
@@ -321,15 +334,19 @@ def generate_check_in_one(shapes, piece):
         for i in range(width + 1):
             grid_tmp = grid_blank.copy()
             if i == width:
+                if piece == WHITE_TOWER:
+                    continue
                 bk_pos = (0, i - 1)
-                wk_pos = (2, i - 2)
+                wk_pos = (2, i - 3)
             else:
                 bk_pos = (0, i)
                 wk_pos = (2, i)
[…]

### 2021-05-24 src/gpl/domains/grid_games/envs/pick_packages.py

@@ -1,221 +1,0 @@
-import copy
-import random
-import sys
-
-import numpy as np
-
-EMPTY = 'empty'
-AGENT = 'agent'
-PACKAGE = 'package'
-PIT = 'pit'
-
-SIMPLIFIED_OBJECT = {
-    EMPTY:'.',
-    PACKAGE:'P',
-    AGENT:'A',
-    PIT:'*',
-}
-
-ALL_TOKENS = [EMPTY, PACKAGE, AGENT, PIT]
-
-PLAYER_1 = 1
-PLAYER_2 = 2
-
-# Actions IDs
-
-UP = 0
-DOWN = 1
-RIGHT = 2
-LEFT = 3
-LEFTUP = 4
-RIGHTUP = 5
-RIGHTDOWN = 6
-LEFTDOWN = 7
-
-
-AGENT_ACTION_SPACE = {
-    UP,
-    DOWN,
-    RIGHT,
-    LEFT,
-    LEFTUP,
-    RIGHTUP,
-    RIGHTDOWN,
-    LEFTDOWN,
-}
-
-ACTION_MOVE_DIRECTION = {
-    UP: (-1, 0),
-    DOWN: (1, 0),
-    RIGHT: (0, 1),
-    LEFT: (0, -1),
-    LEFTUP: (-1, -1),
-    RIGHTUP: (-1, 1),
-    RIGHTDOWN: (1, 1),
-    LEFTDOWN: (1, -1),
-    # STAY: (0, 0),
-}
-
-MOVE_ACTION = {
-    ACTION_MOVE_DIRECTION[RIGHT]: RIGHT,
-    ACTION_MOVE_DIRECTION[LEFT]: LEFT,
-    ACTION_MOVE_DIRECTION[UP]: UP,
-    ACTION_MOVE_DIRECTION[DOWN]: DOWN,
-    ACTION_MOVE_DIRECTION[RIGHTUP]: RIGHTUP,
-    ACTION_MOVE_DIRECTION[RIGHTDOWN]: RIGHTDOWN,
-    ACTION_MOVE_DIRECTION[LEFTUP]: LEFTDOWN,
-    ACTION_MOVE_DIRECTION[LEFTUP]: LEFTUP,
-}
-
-PIECE_VALID_ACTIONS = {
-    AGENT: lambda pos, layout: agent_valid_actions(pos, layout),
-}
-
-class Env(object):
-    @staticmethod
-    def act(rep, action_id):
-        layout, player, nact = rep
[…]

### 2021-05-24 src/gpl/domains/grid_games/envs/space_invaders.py

@@ -12,8 +12,8 @@ BLACK = 2
 
 SIMPLIFIED_OBJECT = {
     EMPTY:' . ',
-    MARTIAN:' M ',
-    TARGET_MARTIAN:' T ',
+    MARTIAN:' m ',
+    TARGET_MARTIAN:' M ',
     AGENT:' A ',
 }
 
@@ -28,11 +28,11 @@ opposite_color = lambda c: BLACK if c == WHITE else WHITE
 
 # Actions IDs
 
-SHOOT = 0
 LEFT = 1
 RIGHT = 2
 DOWN = 3
 UP = 4
+SHOOT = 5
 
 AGENT_ACTION_SPACE = {
     SHOOT,
@@ -45,6 +45,7 @@ MARTIANS_ACTION_SPACE = {
     LEFT,
     DOWN,
     UP,
+    SHOOT,
 }
 
 ACTION_MOVE_DIRECTION = {
@@ -52,11 +53,6 @@ ACTION_MOVE_DIRECTION = {
     LEFT: (0, -1),
     DOWN: (1, 0),
     UP: (-1, 0),
-}
-
-MAX_ACTIONS_BY_TURN = {
-    WHITE:2,
-    BLACK:1,
 }
 
 MOVE_ACTION = {
@@ -69,37 +65,58 @@ PIECE_VALID_ACTIONS = {
     MARTIAN: lambda layout, params: martians_valid_actions(layout, params),
 }
 
+# Unary predicates
+LAST_TURN = 'last_turn'
+
+
 class Env(object):
     def __init__(self, params):
         self.params = params
 
     def act(self, rep, action_id):
         layout = rep.grid
-        assert rep.nact < MAX_ACTIONS_BY_TURN[rep.player]
+        assert rep.nact < self.params.max_actions[rep.player] + 1
         assert not terminated(rep)
         if rep.player == WHITE:
             l = layout_after_agent_action(layout, action_id, self.params)
         elif rep.player == BLACK:
-            l = layout_after_env_action(layout, action_id) if action_id else layout
+            l = layout_after_env_action(layout, action_id, self.params) if action_id else layout
+
+        if self.params.adv_can_kill_agent_shooting and self.__is_last_turn(rep.nact + 1, rep.player) and TARGET_MARTIAN in l:
+            pos_target_martian = np.argwhere(l == TARGET_MARTIAN)[0]
+            martian_attaking_mask = get_martian_attaking_mask(l, pos_target_martian)
[…]

### 2021-05-24 src/gpl/tester.py

@@ -161,8 +161,9 @@ def run_test(config, search_policy, task, instance_name, rng):
         # sa_pair_enc = task.encode_sa_pair((s, op))
         visited_sp[sp[1]] += 1
         path.append(sp[0])
-        spp = task.transition(s, op)
-        path.append(spp[0])
+        spp = task.transition_env(sp)
+        if spp[1] != sp[1]:
+            path.append(spp[0])
 
         if spp[0].deadend:
             exitcode = ExitCode.DeadEndReached

### 2021-05-25 doc/paper/paper.tex
domains update

--- 2021-05-11 doc/paper/paper.tex
@@
 \subsubsection{Description}
+In this domain the agent can shoot, move to the right or to the left.
+The agent has two actions per turn and the adversary one.
+To win the agent has to kill all the opponents, for this he must shoot each of them.
+The agent kills an opponent if he shoots while being in the same column, and he can only kill one for each shoot.
+The adversary has three possible actions, left, right and down, all the adversaries move in the same direction.
+The agent cannot be destroyed by the opponents.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-    (A) Num[col-hv-Agent] [k=1]
-    (B) Dist[col-hv-white_king;right_col;col-hv-black_king] [k=4]
+  0: Num[cell-has-martian] [k=1]
+	1: Num[cell-has-target_martian] [k=1]
+	2: Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]]
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. B=0 AND A>0 -> {B INCs, A DECs}, {B NILs, A NILs}, {B INCs, A NILs}
-  2. B>0 AND A>0 -> {B DECs, A NILs}, {B NILs, A NILs}, {B INCs, A DECs}, {B NILs, A DECs}
+  1. B>0 AND C=0 AND A=0 -> {A ·, B ↓, C ↑}
+  2. B>0 AND C>0 -> {A ·, B ·, C ↓}
+  3. B>0 AND C=0 AND A>0 -> {A ↓, B ·, C ·}, {A ↓, B ·, C ↑}
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-
+  M..M # M..M # M..M # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
+  T..M # T..M # T..M # M..M # T..M # ...M # ..M. # ..M. # ..M. # ...M # ...M # ...T # ..T. # ..T. # .... #
+  .... # .... # .... # T..M # ...M # ...T # ..T. # ..T. # ..T. # ...T # ...T # .... # .... # .... # .... #
+  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
+  ..A. # .A.. # A... # A... # A... # A... # A... # .A.. # ..A. # ..A. # ...A # ...A # ...A # ..A. # ..A. #
 \end{Verbatim}
 
-\subsection{Chase}
+\subsection{Space Invaders - v1}
 \subsubsection{Description}
-In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $rightup$, $right$, $rightdown$, $down$, $leftdown$, $left$, $leftup\}$.
-The agent can move only diagonally and the adversary can move in perpendicular directions.
+In this domain the agent can move to the right or to the left.
+The agent and the opponents have one action per turn.
+To win the agent has to kill all the opponents, for this he must shoot each of them.
+The agent kills an opponent if he moves into the column of the adversary, and he can only kill one for each shoot.
+The adversary has three possible actions, left, right and down, all the adversaries move in the same direction.
+The agent cannot be destroyed by the opponents.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col_has_Agent,Exists(right_col,col_has_Target))] [k=5]
-  (B) Bool[And(row_has_Target,Exists(up_row,row_has_Agent))] [k=5]
-  (C) Dist[row_has_Target;up_row;row_has_Agent] [k=4]
-  (D) Dist[col_has_Agent;right_col;col_has_Target] [k=4]
+  0: Num[cell-has-martian] [k=1]
+	1: Num[cell-has-target_martian] [k=1]
+	2: Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]]
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND D>0 AND C>0 -> {A NILs, B NILs, C DECs, D DECs}, {A INCs, B INCs, C DECs, D DECs},
-                                    {A INCs, B NILs, C DECs, D DECs}, {A NILs, B INCs, C DECs, D DECs}
-  2. A>0 AND B=0 AND D>0 AND C>0 -> {A DECs, B INCs, C DECs, D DECs}, {A DECs, B NILs, C DECs, D DECs}
-  3. A=0 AND B=0 AND D>0 AND C=0 -> {A NILs, B INCs, C INCs, D DECs}, {A INCs, B INCs, C INCs, D DECs}
-  4. A=0 AND B=0 AND D=0 AND C>0 -> {A INCs, B INCs, C DECs, D INCs}, {A INCs, B NILs, C DECs, D INCs}
-  5. A=0 AND B>0 AND D>0 AND C>0 -> {A NILs, B DECs, C DECs, D DECs}, {A INCs, B DECs, C DECs, D DECs}
+  1. B>0 AND C>0 AND A=0 -> {A ·, B ↓, C ↑}
+  2. B>0 AND C>0 -> {A ·, B ·, C ↓}
+  3. B>0 AND C>0 AND A>0 -> {A ↓, B ·, C ↓}, {A ↓, B ·, C ↑}, {A ↓, B ·, C ·}, {A ·, B ·, C ↓}
+  4. B>0 AND C=0 -> {A ·, B ·, C ↑}
+  5. B>0 AND C=0 AND A=0 -> {A ·, B ·, C ↑}
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-....... # ....... # ....... # ....T.. # ...T... # ...T... #
-....... # ....... # ....T.. # ....... # ....... # ...A... #
-....... # ....T.. # ....... # ....... # ....A.. # ....... #
-....T.. # ....... # ....... # ...A... # ....... # ....... #
-....... # ....... # ..A.... # ....... # ....... # ....... #
-....... # .A..... # ....... # ....... # ....... # ....... #
-A...... # ....... # ....... # ....... # ....... # ....... #
+  M..M # M..M # T..M # .... # .... # .... # .... # .... # .... # .... # .... #
+  T..M # T..M # ...M # T..M # T..M # ...M # ..M. # ..M. # ..T. # .T.. # .... #
+  .... # .... # .... # ...M # ...M # ...T # ..T. # ..T. # .... # .... # .... #
+  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
+  ..A. # .A.. # A... # A... # .A.. # A... # A... # .A.. # ..A. # ..A. # .A.. #
 \end{Verbatim}
 
-\subsection{Shoot}
+\subsection{Chase - v0}
 \subsubsection{Description}
-In this domain an agent has to shoot an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$.
-This game would be the equivalent of a check with the rook.
-Only that both the rook and the opponent can only move one orthogonal square at a time.
+In this domain an agent has to chase an adversary.
+The goal is defined by the agent being in a target adjacent cell.
+The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The set of possile action for the target is ~\{$up$, $right$, $down$, $left$, $leftup\}$.
+The agent can move only diagonally and the adversary can move in perpendicular directions.
+The agent and the target can move only once per turn.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+#A.....#
+#......#
+#......#
+#.....T#
+\end{Verbatim}
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-has-Adversary,col-has-Agent)] [k=3]
-  (B) Dist[row-has-Agent;up_row;row-has-Adversary] [k=4]
-  (C) Dist[cell-has-Agent;adjacent_cell;cell-has-Adversary] [k=4]
+  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
+  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
+\end{Verbatim}
+
+\subsubsection{Policy (with no fixed action space)}
+
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A=0 AND B=0 AND D>0 AND C=0 -> {A ↑, B ↑, C ↑, D ↓}, {A ·, B ↑, C ↑, D ↓}
+  2. A=0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ↓}, {A ↑, B ↑, C ↓, D ↓},
+                                    {A ·, B ·, C ↓, D ↓}, {A ↑, B ·, C ↓, D ↓}
+  3. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ↓, C ↓, D ↓}, {A ↑, B ↓, C ↓, D ↓}
+  4. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, B ·, C ↓, D ↓}, {A ↓, B ↑, C ↓, D ↓}
+  5. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, B ·, C ↓, D ↑}, {A ↑, B ↑, C ↓, D ↑}
+
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  A..... # ...... # ...... # ...... # ...... # ...... # .....T # ....AT #
+  ...... # .A.... # .A.... # ...... # .....T # ...A.T # ...A.. # ...... #
+  ...... # ...... # .....T # ..A..T # ..A... # ...... # ...... # ...... #
+  .....T # .....T # ...... # ...... # ...... # ...... # ...... # ...... #
+\end{Verbatim}
+
+\subsection{Chase - v1}
+\subsubsection{Description}
+In this domain an agent has to chase an adversary.
+The goal is defined by the agent being in a target adjacent cell.
+The set of possile actions for the agent and the target is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The agent can move twice per turn and the adversary can move once per turn.
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+#A.....#
+#......#
+#......#
+#.....T#
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
+  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
+\end{Verbatim}
+
+\subsubsection{Policy (with no fixed action space)}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A=0 AND B=0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
+  2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
+  3. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ·, C ·, D ↓}, {A ↑, B ·, C ·, D ↓}
+  4. B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
+  5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
+  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
+  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, B ·, C ↓, D ·}, {A ·, B ↑, C ↓, D ·}
+
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  ...... # ...... # ...... # .T.... # .T.... # .T.... # T..... # T..... # T..... #
+  .T.... # .T.... # .T.... # ...... # ....A. # ...A.. # ...A.. # ..A... # .A.... #
+  ...... # .....A # ....A. # ....A. # ...... # ...... # ...... # ...... # ...... #
+  .....A # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+\end{Verbatim}
+
+\subsection{Shoot - v0}
+\subsubsection{Description}
+In this domain an agent has to chase an adversary.
+The goal is defined by the agent being in the column or row of the adversary.
+The set of possile actions for the agent and the target is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The agent and the target can move only once per turn.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+#A.....#
+#......#
+#......#
+#.....T#
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
+  (B) Bool[And(col-has-AGENT,Exists(adjacent_col,col-has-TARGET))] [k=5]
+  (C) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
+
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND C>0 AND B>0 -> {A INCs, B NILs, C NILs}, {A NILs, B DECs, C NILs}
+  1. B>0 AND A=0 AND C>0 -> {A ↑, B ↓, C ·}
+  2. B=0 AND A=0 AND C>0 -> {A ·, B ·, C ↓}
 \end{Verbatim}
@@
   ....... # ....... # ....... # .....T. # ......T # ....... #
+\end{Verbatim}
+
+\subsection{Shoot - v1}
+\subsubsection{Description}
+In this domain an agent has to chase an adversary.
+The goal is defined by the agent being in the column or row of the adversary.
+The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The set of possile action for the target is ~\{$up$, $right$, $down$, $left$, $leftup\}$.  The agent and the target can move only once per turn.
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
+  (B) Bool[And(row-has-AGENT,row-has-TARGET)] [k=3]
+  (C) Dist[col-has-TARGET;adjacent_col;col-has-AGENT] [k=4]
+  (D) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
+
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ·, C ↓, D ↑}, {A ↑, B ·, C ↓, D ↓}, {A ·, B ·, C ↓, D ↓}, {A ·, B ↑, C ↓, D ↓}
+
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  A...... # ....... # ....... # ....... # ....... # ....... #
+  ....... # A...... # ....... # ....... # ....... # ....... #
+  ....... # ....... # A...... # ....... # ....... # ....... #
+  ....... # ....... # ....... # A...... # ....... # ....... #
+  ....... # .....T. # ....... # ....... # A...... # ....... #
+  .....T. # ....... # .....T. # ....... # ....... # A.....T #
+  ....... # ....... # ....... # .....T. # ......T # ....... #
+\end{Verbatim}
+
+\subsection{Nim - v0}
+\subsubsection{Description}
+In this game the action space is equal to the number of cells in the grid.
+In order to win the agent has to remove the last token in his turn.
+If the opponet removes the last token in his turn, the agent loses.
+The agent and the adversary has on action per turn.
+When one token is removed, the tokens above in the same column are removed too.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # t  . #
+  # t  . #
+  # t  t #
+  # t  t #
+  # t  t #
+  # t  t #
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]
+  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]
+  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]
+
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A>0 AND B>0 AND C>0 -> {A ·, B ↓, C ↓}
+  2. B>0 AND C>0 -> {A ·, B ↓, C ↓}
+
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
+  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+\end{Verbatim}
+
+\subsection{Checkmate - v0}
+\subsubsection{Description}
+In this game the action space is equal to the number of cells in the grid.
+In order to win the agent has to do a checkmate in one movement.
+Otherwise he loses.
+In the version v0 white pieces have the king and the queen, and black pieces have the king.
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-has-black_king,col-has-white_king)] [k=3]
+  (B) Bool[And(col-has-black_king,col-has-white_queen)] [k=3]
+  (C) Bool[And(row-has-black_king,row-has-white_king)] [k=3]
+  (D) Bool[And(row-has-black_king,row-has-white_queen)] [k=3]
+  (E) Bool[And(cell-has-black_king,Exists(adjacent_cell,cell-has-white_queen))] [k=5]
+
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. E=0 AND A>0 AND B=0 AND C=0 AND D=0 -> {A ·, B ↑, C ·, D ·, E ↑}, {A ·, B ·, C ·, D ↑, E ·}
+  2. E=0 AND A=0 AND B=0 AND C>0 AND D=0 -> {A ·, B ·, C ·, D ↑, E ↑}, {A ·, B ↑, C ·, D ·, E ·}
+  3. E=0 AND A>0 AND B>0 AND C=0 AND D=0 -> {A ·, B ↓, C ·, D ↑, E ·}
+  4. E=0 AND A=0 AND B=0 AND C=0 AND D=0 -> {A ·, B ·, C ·, D ·, E ↑}
+  5. E=0 AND A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ·, D ↓, E ·}
+
+\end{Verbatim}
+
+\subsection{Checkmate - v1}
+\subsubsection{Description}
+In this game the action space is equal to the number of cells in the grid.
+In order to win the agent has to do a checkmate in one movement.
+Otherwise he loses.
+In the version v0 white pieces have the king and the queen, and black pieces have the king.
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-has-black_king,col-has-white_king)] [k=3]
+  (B) Bool[And(col-has-black_king,col-has-white_tower)] [k=3]
+  (C) Bool[And(row-has-black_king,row-has-white_tower)] [k=3]
+
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A>0 AND B=0 AND C=0 -> {A ·, B ·, C ↑}
+  2. A=0 AND B=0 AND C=0 -> {A ·, B ↑, C ·}
+
 \end{Verbatim}

### 2021-05-25 experiments/space_invaders.py

@@ -96,12 +96,16 @@ def experiments():
 
     # version 2: the agent can not shoot, but can kill moving into the adv column, has 2 moves
     space_invaders_params_v2 = copy.deepcopy(space_invaders_params)
+    space_invaders_params_v2.unary_predicates = {}
+    space_invaders_params_v2.use_player_as_feature = True
+    space_invaders_params_v2.use_bidirectional = {}
+    space_invaders_params_v2.max_actions = {PLAYER1: 1, PLAYER2: 1}
+    space_invaders_params_v2.target_columns = False
     space_invaders_params_v2.agent_has_to_shoot = False
     exps["2"] = update_dict(
         exps["1"],
         domain=Domain(space_invaders_params_v2),
-        instances=[17],
-        # instances=[3, 4],
+        instances=[0, 17, 18],
     )
 
     # version 3:

### 2021-05-25 src/gpl/domains/grid_games/grammar/objects.py

@@ -4,8 +4,10 @@ NONE = 'none'
 PLAYER1 = 1
 PLAYER2 = 2
 
-WHITE_KING = 'white_king'
-BLACK_KING = 'black_king'
+WHITE_KING = 'AGENT'
+# WHITE_KING = 'white_king'
+BLACK_KING = 'TARGET'
+# BLACK_KING = 'black_king'
 WHITE_QUEEN = 'white_queen'
 WHITE_TOWER = 'white_tower'
 

### 2021-05-25 doc/paper/paper.tex
minor change
changes

@@
 
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+  #m...m#
+  #m...M#
+  #.....#
+  #...A.#
+\end{Verbatim}
+
 \subsubsection{Features}
 \begin{Verbatim}[fontsize=\footnotesize]
-  0: Num[cell-has-martian] [k=1]
-	1: Num[cell-has-target_martian] [k=1]
-	2: Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]]
+(A) Num[cell-has-martian] [k=1]
+(B) Bool[cell-has-target_martian] [k=1]
+(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  M..M # M..M # M..M # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
-  T..M # T..M # T..M # M..M # T..M # ...M # ..M. # ..M. # ..M. # ...M # ...M # ...T # ..T. # ..T. # .... #
-  .... # .... # .... # T..M # ...M # ...T # ..T. # ..T. # ..T. # ...T # ...T # .... # .... # .... # .... #
+  m..m # m..m # m..m # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
+  M..m # M..m # M..m # m..m # M..m # ...m # ..m. # ..m. # ..m. # ...m # ...m # ...M # ..M. # ..M. # .... #
+  .... # .... # .... # M..m # ...m # ...M # ..M. # ..M. # ..M. # ...M # ...M # .... # .... # .... # .... #
   .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
@@
 In this domain the agent can move to the right or to the left.
-The agent and the opponents have one action per turn.
+TThe agent has two actions per turn and the adversary one.
 To win the agent has to kill all the opponents, for this he must shoot each of them.
@@
 
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+  #m...m#
+  #m...M#
+  #.....#
+  #...A.#
+\end{Verbatim}
+
 \subsubsection{Features}
 \begin{Verbatim}[fontsize=\footnotesize]
-  0: Num[cell-has-martian] [k=1]
-	1: Num[cell-has-target_martian] [k=1]
-	2: Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]]
+  (A) Num[cell-has-martian] [k=1]
+  (B) Bool[cell-has-target_martian] [k=1]
+  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. B>0 AND C>0 AND A=0 -> {A ·, B ↓, C ↑}
-  2. B>0 AND C>0 -> {A ·, B ·, C ↓}
-  3. B>0 AND C>0 AND A>0 -> {A ↓, B ·, C ↓}, {A ↓, B ·, C ↑}, {A ↓, B ·, C ·}, {A ·, B ·, C ↓}
-  4. B>0 AND C=0 -> {A ·, B ·, C ↑}
+  1. B>0 AND C>0 AND A>0 -> {A ↓, B ·, C ↑},
+                            {A ↓, B ·, C ↓},
+                            {A ↓, B ·, C ·}
+  2. B>0 AND C>0 AND A=0 -> {A ·, B ↓, C ↑}
+  3. B>0 AND C=0 -> {A ·, B ·, C ↑}
+  4. B>0 AND C>0 -> {A ·, B ·, C ↓}
   5. B>0 AND C=0 AND A=0 -> {A ·, B ·, C ↑}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  M..M # M..M # T..M # .... # .... # .... # .... # .... # .... # .... # .... #
-  T..M # T..M # ...M # T..M # T..M # ...M # ..M. # ..M. # ..T. # .T.. # .... #
-  .... # .... # .... # ...M # ...M # ...T # ..T. # ..T. # .... # .... # .... #
-  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
-  ..A. # .A.. # A... # A... # .A.. # A... # A... # .A.. # ..A. # ..A. # .A.. #
+  m..m # m..M # m..M # .... # .... # .... # .... # .... # .... # .... # .... # .... #
+  m..M # m... # m... # m..M # m... # m... # .m.. # .M.. # .M.. # M... # M... # .... #
+  .... # .... # .... # m... # M... # M... # .M.. # .... # .... # .... # .... # .... #
+  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
+  ..A. # ...A # ..A. # ..A. # ...A # ..A. # ..A. # .A.. # ..A. # ..A. # .A.. # A... #
+  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ·, C ↓, D ↑}, {A ↑, B ·, C ↓, D ↓}, {A ·, B ·, C ↓, D ↓}, {A ·, B ↑, C ↓, D ↓}
+  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ·, C ↓, D ↑},
+                                    {A ↑, B ·, C ↓, D ↓}, {A ·, B ·, C ↓, D ↓},
+                                    {A ·, B ↑, C ↓, D ↓}
 
@@
 Otherwise he loses.
-In the version v0 white pieces have the king and the queen, and black pieces have the king.
+In the version v0 white pieces have the king and the tower, and black pieces have the king.
 

### 2021-05-25 experiments/wumpus.py

@@ -1,29 +1,35 @@
 import math
+
 from sltp.util.misc import update_dict
 from gpl.domains.grid_games.domain import Domain
 from gpl.utils import Bunch
-from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S, D1_S, D2_S
-from gpl.domains.grid_games.envs.checkmate_tactic import CHECKMATE, STALEMATE, N_MOVE, CHECK
+from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
+from gpl.domains.grid_games.envs.wumpus import RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, UP, DOWN, RIGHT, LEFT
+from gpl.domains.grid_games.grammar.objects import PLAYER1, PLAYER2
 
-
-ct_params = Bunch({
-    'domain_name': 'checkmate_tactic',
-    'use_player_as_feature': True,
+chase_params = Bunch({
+    'domain_name': 'wumpus',
+    'use_player_as_feature': False,
+    'use_next_player_as_feature': False,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
     'use_adjacency': {CELL_S},
     'use_bidirectional': {},
-    'sorts_to_use': {COL_S, ROW_S, CELL_S},
-    'n_moves': 1,
+    'sorts_to_use': {CELL_S},
     'unary_predicates': {},
-    # 'unary_predicates': {"{}_{}".format(N_MOVE, i) for i in range(CHECKMATE_IN_N + 1)},
-    # 'unary_predicates': {STALEMATE, CHECKMATE}
-    'game_version': 0,
+    'can_build_walls': False,
+    'wumpus_active': False,
+    'ava_actions': {
+        # PLAYER1: {RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP},
+        PLAYER1: {UP, DOWN, RIGHT, LEFT, RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP},
+        PLAYER2: {UP, DOWN, RIGHT, LEFT, RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP}},
+    'max_actions': {PLAYER1: 3te,
+                    PLAYER2: 1},
 })
 
 def experiments():
     base = dict(
-        domain=Domain(ct_params),
+        domain=Domain(chase_params),
         maxsat_encoding="d2l",
         num_states="all",
[…]

### 2021-05-25 src/gpl/domains/adversarial_domains/domain.py

@@ -1,161 +1,0 @@
-from .grammar.objects import get_domain_objects
-from gpl.domain import IDomain
-from tarski.fstrips import fstrips, create_fstrips_problem
-from .task import Task
-import copy
-from .grammar.language import *
-import importlib
-ANCHOR = 'gpl.domains.grid_games'
-OBJECTS = None
-
-class Domain(IDomain):
-    def __init__(self, params):
-        super().__init__(params.domain_name)
-        self.params = params
-        self.env = importlib.import_module(f'.envs.{params.domain_name}', ANCHOR).Env(params)
-        self.action_space = self.env.get_action_space()
-        self.type = 'adv'
-        self.set_objects()
-
-    def set_objects(self):
-        global OBJECTS
-        OBJECTS = get_domain_objects(self.get_domain_name())
-
-    def get_printable_params(self):
-        printable_params = ""
-        for p, val in self.params.to_dict().items():
-            printable_params += "{}: {}\n".format(p, str(val))
-        return printable_params[:-1]
-
-    # Generate Language
-    def generate_language(self):
-        """ Generate the Tarski language corresponding to the given domain. """
-        return generate_lang(self._domain_name, self.env)
-
-    # Generate Problem
-    def generate_problem(self, lang, instance_name):
-        """ Generate the Tarski problem corresponding to the given domain and particular layout. """
-        return generate_problem(self._domain_name, lang, self.env, instance_name)
-
-    # Generate Task
-    def generate_task(self, instance_name):
-        """ Generate a Task object, according to the Interface ITask """
-        return Task(self._domain_name, instance_name, self.env)
-
-
-def load_general_lang(lang, statics, env):
-    """ Return the FOL language corresponding to the Reach for the Star domain,
-     plus a set with the names of those predicates / functions that are static. """
-    params = env.params
-    for sort in params.sorts_to_use:
-        lang.sort(sort)
-        for o in OBJECTS.general:
-            lang.predicate(f'{sort}-has-{o}', sort)
-        if sort in params.use_adjacency:
-            lang.predicate(f'{ADJACENT}_{sort}', sort, sort)
-            statics.add(f'{ADJACENT}_{sort}')
-        if sort in params.use_bidirectional:
-            for d in GRID_DIRECTIONS[sort]:
[…]

### 2021-05-25 src/gpl/domains/adversarial_domains/grammar/grammar.py

@@ -1,78 +1,0 @@
-import string
-import sys
-
-from .state_to_atoms import state_to_atoms, atom_tuples_to_string
-from .objects import get_domain_objects
-
-# ASCII = string.printable
-MAX_NUM = 1000
-ASCII = ''.join(chr(x) for x in range(5000))
-
-
-class Grammar:
-    """
-    Wrapper of some grammar utils
-    """
-
-    def __init__(self, domain_name, params):
-
-        self.domain_name = domain_name
-        self.params = params
-        self.object_bytes = self.objects_to_bytes()
-
-    def state_to_atoms(self, state):
-        return state_to_atoms(self.domain_name, state, self.params)
-
-    def state_to_atoms_string(self, state,):
-        return atom_tuples_to_string(self.state_to_atoms(state,))
-
-    def encode_state(self, r):
-        """ Return a Python bytes object with a byte corresponding to each object type.
-        This should have roughly as many bytes as positions in the layout, which will typically be much
-        more compact than a numpy array of `object` types for encoding single characters, that uses several bytes per
-        position.
-        """
-        try:
-            b = list(self.object_bytes[obj] for obj in r.grid.flatten())
-            if self.params.use_player_as_feature:
-                b = b + [self.object_bytes[r.player]]
-            for u in self.params.unary_predicates:
-                b = b + [self.object_bytes['true']] if getattr(r, u) else b + [self.object_bytes['false']]
-            # b = b + [self.object_bytes[r.nmoves]]
-            # b = b + [self.object_bytes['true']] if info['reward'] else b + [self.object_bytes['false']]
-            # b = b + [self.object_bytes['true']] if info['goal'] else b + [self.object_bytes['false']]
-            # b = b + [self.object_bytes['true']] if info['deadend'] else b + [self.object_bytes['false']]
-            return bytes(b)
-        except:
-            for o in r.grid.flatten():
-                if o not in self.object_bytes:
-                    print('EXCEPTION: Unknown object: {}'.format(o))
-
-    def objects_to_bytes(self):
-        OBJECTS = get_domain_objects(self.domain_name)
-
-        object_bytes = dict()
-        possible_chars = ASCII
-        numbers = list(range(MAX_NUM))
-
-        for obj in OBJECTS.general | {OBJECTS.empty}:
-            possible_chars, b = possible_chars[1:], possible_chars[0]
-            object_bytes[obj] = ord(b)
-
[…]

### 2021-05-25 src/gpl/domains/adversarial_domains/grammar/language.py

@@ -1,25 +1,0 @@
-CELL_S = 'cell'
-ROW_S = 'row'
-COL_S = 'col'
-D1_S = 'd1'
-D2_S = 'd2'
-
-CONST = {
-    CELL_S: lambda r, c, nrows, ncols: f'{CELL_S}{r}-{c}',
-    ROW_S: lambda r, c, nrows, ncols: f'{ROW_S}{r}',
-    COL_S: lambda r, c, nrows, ncols: f'{COL_S}{c}',
-    D1_S: lambda r, c, nrows, ncols: f'{D1_S}_{c - r + nrows -1}',
-    D2_S: lambda r, c, nrows, ncols: f'{D2_S}_{(ncols - 1 - c) - r + nrows -1}',
-}
-
-ALL_GRID_DIRECTIONS = ['up', 'rightup', 'right', 'rightdown', 'down', 'leftdown', 'left', 'leftup']
-UP, RIGHTUP, RIGHT, RIGHTDOWN, DOWN, LEFTDOWN, LEFT, LEFTUP = [d for d in ALL_GRID_DIRECTIONS]
-ADJACENT = 'adjacent'
-
-GRID_DIRECTIONS = {
-    CELL_S: ALL_GRID_DIRECTIONS,
-    ROW_S: [UP, DOWN],
-    COL_S: [RIGHT, LEFT],
-    D1_S: [RIGHT, LEFT],
-    D2_S: [RIGHT, LEFT],
-}

### 2021-05-25 src/gpl/domains/adversarial_domains/grammar/state_to_atoms.py

@@ -1,38 +1,0 @@
-import copy
-
-from .language import *
-from .objects import OBJECTS
-
-# General State to atoms
-def state_to_atoms(domain_name, state, p):
-    rep, _ = state
-    brd = rep.grid
-    nrows, ncols = brd.shape
-
-    # These are the general atoms for all the domains
-    atoms = list()
-
-    for r in range(-1, nrows + 1):
-        for c in range(-1, ncols + 1):
-            for sort in p.sorts_to_use:
-                o = brd[r, c] if (nrows > r >= 0 and ncols > c >= 0) else OBJECTS.none
-                if o == OBJECTS.none:
-                    continue
-                if o not in {OBJECTS.empty, OBJECTS.none}:
-                    atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
-
-    for u in p.unary_predicates:
-        if getattr(rep, u):
-            atoms.append((u,))
-
-    for predicate, _ in p.predicates_arity_1:
-        o = getattr(rep, predicate)[0]
-        atoms.append((u, o))
-
-    if p.use_player_as_feature:
-        atoms.append(('player-{}'.format(rep.player),))
-
-    return atoms
-
-def atom_tuples_to_string(atom_tuples):
-    return ' '.join(f"{a[0]}({','.join(str(var) for var in a[1:])})" for a in atom_tuples)

### 2021-05-25 src/gpl/domains/grid_games/domain.py

@@ -65,6 +65,9 @@ def load_general_lang(lang, statics, env):
     if params.use_player_as_feature:
         _ = [lang.predicate('player-{}'.format(p),) for p in {OBJECTS.player1, OBJECTS.player2}]
 
+    if params.use_next_player_as_feature:
+        _ = [lang.predicate('next_player-{}'.format(p),) for p in {OBJECTS.player1, OBJECTS.player2}]
+
     return lang, statics
 
 
@@ -74,6 +77,9 @@ def load_general_problem(problem, lang, rep, env):
     params = env.params
     if params.use_player_as_feature:
         problem.init.add(lang.get('player-{}'.format(rep.player),))
+    if params.use_next_player_as_feature:
+        problem.init.add(lang.get('next_player-{}'.format(rep.next_player),))
+
     for u in params.unary_predicates:
         if getattr(rep, u):
             problem.init.add(lang.get(u,))

### 2021-05-25 src/gpl/domains/grid_games/envs/wumpus.py

@@ -1,0 +1,289 @@
+import random
+import sys
+
+import numpy as np
+from gpl.utils import Bunch
+import copy
+
+from ..grammar.objects import WUMPUS, GOLD, TARGET_GOLD, AGENT, EMPTY, PIT, PLAYER1, PLAYER2
+from ..utils import identify_next_player
+
+
+SIMPLIFIED_OBJECT = {
+    EMPTY:' . ',
+    WUMPUS:' W ',
+    AGENT:' A ',
+    GOLD:' g ',
+    TARGET_GOLD:' G ',
+    PIT:' * ',
+}
+
+TURN_TO_PIECES = {
+    PLAYER1: [AGENT,],
+    PLAYER2: [WUMPUS,],
+}
+
+opposite_player = lambda c: PLAYER2 if c == PLAYER1 else PLAYER1
+
+
+PIECE_VALID_ACTIONS = {
+    AGENT: lambda pos, layout, params: agent_valid_actions(pos, layout, params),
+    WUMPUS: lambda pos, layout, params: wumpus_valid_actions(pos, layout, params),
+}
+
+# Actions IDs
+
+UP = 0
+DOWN = 1
+RIGHT = 2
+LEFT = 3
+LEFTUP = 4
+RIGHTUP = 5
+RIGHTDOWN = 6
+LEFTDOWN = 7
+
+ACTION_MOVE_DIRECTION = {
+    UP: (-1, 0),
+    DOWN: (1, 0),
+    RIGHT: (0, 1),
+    LEFT: (0, -1),
+    LEFTUP: (-1, -1),
+    RIGHTUP: (-1, 1),
+    RIGHTDOWN: (1, 1),
+    LEFTDOWN: (1, -1),
+}
+
+MOVE_ACTION = {
+    ACTION_MOVE_DIRECTION[UP]: UP,
+    ACTION_MOVE_DIRECTION[DOWN]: DOWN,
+    ACTION_MOVE_DIRECTION[RIGHT]: RIGHT,
+    ACTION_MOVE_DIRECTION[LEFT]: LEFT,
+    ACTION_MOVE_DIRECTION[LEFTUP]: LEFTUP,
+    ACTION_MOVE_DIRECTION[RIGHTUP]: RIGHTUP,
+    ACTION_MOVE_DIRECTION[RIGHTDOWN]: RIGHTDOWN,
+    ACTION_MOVE_DIRECTION[LEFTDOWN]: LEFTDOWN,
+}
+
+
+
+# Begin Wumpus =================================
+
[…]

### 2021-05-25 src/gpl/domains/grid_games/grammar/grammar.py

@@ -36,6 +36,8 @@ class Grammar:
             b = list(self.object_bytes[obj] for obj in r.grid.flatten())
             if self.params.use_player_as_feature:
                 b = b + [self.object_bytes[r.player]]
+            if self.params.use_next_player_as_feature:
+                b = b + [self.object_bytes[r.next_player]]
             for u in self.params.unary_predicates:
                 b = b + [self.object_bytes['true']] if getattr(r, u) else b + [self.object_bytes['false']]
             # b = b + [self.object_bytes[r.nmoves]]

### 2021-05-25 src/gpl/domains/grid_games/grammar/objects.py

@@ -10,20 +10,20 @@ BLACK_KING = 'TARGET'
 # BLACK_KING = 'black_king'
 WHITE_QUEEN = 'white_queen'
 WHITE_TOWER = 'white_tower'
-
 MARTIAN = 'martian'
 TARGET_MARTIAN = 'target_martian'
-
 PACKAGE = 'package'
 DESTINY = 'destiny'
 PIT = 'pit'
 AGENT = 'agent'
 EMPTY = 'empty'
 WALL = 'wall'
-
 TOKEN = 'token'
 TOP_TOKEN = 'top_token'
 BOTTOM_TOKEN = 'bottom_token'
+WUMPUS = 'wumpus'
+GOLD = 'gold'
+TARGET_GOLD = 'target_gold'
 
 
 OBJECTS = Bunch({
@@ -50,6 +50,18 @@ OBJECTS_CHECK = Bunch({
                 WHITE_KING,
                 WHITE_QUEEN,
                 WHITE_TOWER,},
+    'empty': EMPTY,
+    'player1': PLAYER1,
+    'player2': PLAYER2,
+    'none': NONE,
+})
+
+OBJECTS_WUMPUS = Bunch({
+    'general': {AGENT,
+                WUMPUS,
+                GOLD,
+                TARGET_GOLD,
+                PIT},
     'empty': EMPTY,
     'player1': PLAYER1,
     'player2': PLAYER2,
@@ -105,4 +117,5 @@ def get_domain_objects(domain_name):
         'shoot': OBJECTS,
         'space_invaders': OBJECTS_SPACE,
         'checkmate_tactic': OBJECTS_CHECK,
+        'wumpus': OBJECTS_WUMPUS,
     }[domain_name]

### 2021-05-25 src/gpl/domains/grid_games/grammar/state_to_atoms.py

@@ -28,6 +28,9 @@ def state_to_atoms(domain_name, state, p):
     if p.use_player_as_feature:
         atoms.append(('player-{}'.format(rep.player),))
 
+    if p.use_next_player_as_feature:
+        atoms.append(('next_player-{}'.format(rep.next_player),))
+
     return atoms
 
 def atom_tuples_to_string(atom_tuples):

### 2021-05-25 src/gpl/domains/grid_games/task.py

@@ -91,6 +91,11 @@ class Task(ITask):
         #         succs_reps.append(spp[0])
         # self.print_path(succs_reps)
 
+        # succs_reps.append(r0)
+        # for _, sp in succs_sp:
+        #     succs_reps.append(sp[0])
+        # self.print_path(succs_reps)
+
         if just_sp:
             return succs_sp
         else:
@@ -134,12 +139,12 @@ class Task(ITask):
             single_rep_row += simplified_objects[o]
         size_single_row = len("{} # ".format(single_rep_row))
 
-        info_to_print = ["player", "nmoves", "last_turn"]
+        info_to_print = ["player", "nmoves", "last_turn", "next_player"]
         for info in info_to_print:
             try:
                 tmp_full_row = ""
                 for rep in reps:
-                    tmp_full_row += "{} ({})".format(getattr(rep, info), info[0]).ljust(size_single_row)
+                    tmp_full_row += "{} ({})".format(getattr(rep, info), info[:2]).ljust(size_single_row)
                 total_path_rep += "{}\n".format(tmp_full_row)
             except:
                 pass

### 2021-05-25 src/gpl/domains/grid_games/utils.py

@@ -1,4 +1,4 @@
-from .grammar.objects import OBJECTS, BLACK_KING, WHITE_KING
+from .grammar.objects import PLAYER1, PLAYER2
 import numpy as np
 import json
 import os.path
@@ -20,3 +20,11 @@ def identify_margin(r, c, nrows, ncols):
         return OBJECTS.margin['m6']
     if r == nrows and c < 0:
         return OBJECTS.margin['m7']
+
+
+def identify_next_player(rep, params):
+    opposite_player = lambda c: PLAYER2 if c == PLAYER1 else PLAYER1
+    if rep.nact < params.max_actions[rep.player]:
+        return rep.player
+    else:
+        return opposite_player(rep.player)

### 2021-05-27 doc/paper/paper.tex
add

@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. B>0 AND C=0 AND A=0 -> {A ·, B ↓, C ↑}
-  2. B>0 AND C>0 -> {A ·, B ·, C ↓}
-  3. B>0 AND C=0 AND A>0 -> {A ↓, B ·, C ·}, {A ↓, B ·, C ↑}
+    1. B>0 AND C>0 -> {A ·, B ·, C ↓}
+    2. A=0 AND B>0 AND C=0 -> {A ·, B ↓, C ↑}
+    3. A>0 AND B>0 AND C=0 -> {A ↓, B ·, C ↑}, {A ↓, B ·, C ·}
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. B>0 AND C>0 AND A>0 -> {A ↓, B ·, C ↑},
-                            {A ↓, B ·, C ↓},
+  1. B>0 AND C=0 -> {A ·, B ·, C ↑}
+  2. B>0 AND C>0 -> {A ·, B ·, C ↓}
+  3. A=0 AND B>0 AND C>0 -> {A ·, B ↓, C ↑}
+  4. A>0 AND B>0 AND C>0 -> {A ↓, B ·, C ↓},
+                            {A ↓, B ·, C ↑},
                             {A ↓, B ·, C ·}
-  2. B>0 AND C>0 AND A=0 -> {A ·, B ↓, C ↑}
-  3. B>0 AND C=0 -> {A ·, B ·, C ↑}
-  4. B>0 AND C>0 -> {A ·, B ·, C ↓}
-  5. B>0 AND C=0 AND A=0 -> {A ·, B ·, C ↑}
 \end{Verbatim}
@@
 
-\subsection{Shoot - v0}
-\subsubsection{Description}
-In this domain an agent has to chase an adversary.
-The goal is defined by the agent being in the column or row of the adversary.
-The set of possile actions for the agent and the target is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
-The agent and the target can move only once per turn.
-
-\subsubsection{Training instances:}
-\begin{Verbatim}[fontsize=\footnotesize]
-#A.....#
-#......#
-#......#
-#.....T#
-\end{Verbatim}
-
-\subsubsection{Features}
-\begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
-  (B) Bool[And(col-has-AGENT,Exists(adjacent_col,col-has-TARGET))] [k=5]
-  (C) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
-
-\end{Verbatim}
-
-\subsubsection{Policy}
-\begin{Verbatim}[fontsize=\footnotesize]
-  1. B>0 AND A=0 AND C>0 -> {A ↑, B ↓, C ·}
-  2. B=0 AND A=0 AND C>0 -> {A ·, B ·, C ↓}
-\end{Verbatim}
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  A...... # ....... # ....... # ....... # ....... # ....... #
-  ....... # A...... # ....... # ....... # ....... # ....... #
-  ....... # ....... # A...... # ....... # ....... # ....... #
-  ....... # ....... # ....... # A...... # ....... # ....... #
-  ....... # .....T. # ....... # ....... # A...... # ....... #
-  .....T. # ....... # .....T. # ....... # ....... # A.....T #
-  ....... # ....... # ....... # .....T. # ......T # ....... #
-\end{Verbatim}
-
-\subsection{Shoot - v1}
-\subsubsection{Description}
-In this domain an agent has to chase an adversary.
-The goal is defined by the agent being in the column or row of the adversary.
-The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
-The set of possile action for the target is ~\{$up$, $right$, $down$, $left$, $leftup\}$.  The agent and the target can move only once per turn.
-
-\subsubsection{Features}
-\begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
-  (B) Bool[And(row-has-AGENT,row-has-TARGET)] [k=3]
-  (C) Dist[col-has-TARGET;adjacent_col;col-has-AGENT] [k=4]
-  (D) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
-
-\end{Verbatim}
-
-\subsubsection{Policy}
-\begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ·, C ↓, D ↑},
-                                    {A ↑, B ·, C ↓, D ↓}, {A ·, B ·, C ↓, D ↓},
-                                    {A ·, B ↑, C ↓, D ↓}
-
-\end{Verbatim}
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  A...... # ....... # ....... # ....... # ....... # ....... #
-  ....... # A...... # ....... # ....... # ....... # ....... #
-  ....... # ....... # A...... # ....... # ....... # ....... #
-  ....... # ....... # ....... # A...... # ....... # ....... #
-  ....... # .....T. # ....... # ....... # A...... # ....... #
-  .....T. # ....... # .....T. # ....... # ....... # A.....T #
-  ....... # ....... # ....... # .....T. # ......T # ....... #
-\end{Verbatim}
-
 \subsection{Nim - v0}
@@
 
+\subsection{Delivery - v0}
+\subsubsection{Description}
+
+In this domain the agent has to pick up a pet and take it to a certain location.
+The pet has the option on its turn to escape from its captor to any of the cells adjacent to it.
+The goal is defined by the agent in a cell adjacent to the destination while carrying the pet.
+The agent has two actions per turn and the adversary one.
+The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The set of possile actions for the pet consist in escape to one of the adjacent cells to the agent, i.e.
+at most eight possible actions depending on the position of the agent in the grid.
+The pet can not escape to the delivey point.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # D  .  .  .  .  A #
+  # .  .  .  .  .  . #
+  # .  .  .  .  .  . #
+  # .  .  .  .  .  . #
+  # .  .  .  .  .  . #
+  # .  .  .  .  .  p #
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Atom[holding_pet] [k=1]
+  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destiny))] [k=5]
+  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destiny] [k=4]
+  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ·}
+  2. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ↓}, {A ·, B ·, C ↑, D ↓},
+                                    {A ↑, B ·, C ·, D ↑}, {A ·, B ·, C ·, D ↓}
+  3. A>0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↓, D ·}
+  4. A=0 AND B>0 AND C>0 AND D>0 -> {A ·, B ↓, C ↑, D ↓}
+
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  p.... # p.... # p.... # p.... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
+  ..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... #
+  ..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... #
+  ..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. #
+  A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D #
+\end{Verbatim}
+
+\subsection{Shoot - v0}
+\subsubsection{Description}
+In this domain an agent has to chase an adversary.
+The goal is defined by the agent being in the column or row of the adversary.
+The set of possile actions for the agent and the target is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The agent and the target can move once per turn.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+#A.....#
+#......#
+#......#
+#.....T#
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
+  (B) Bool[And(col-has-AGENT,Exists(adjacent_col,col-has-TARGET))] [k=5]
+  (C) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
+
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A=0 AND B=0 AND C>0 -> {A ·, B ·, C ↓}
+  2. A=0 AND B>0 AND C>0 -> {A ↑, B ↓, C ·}
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  A...... # ....... # ....... # ....... # ....... # ....... #
+  ....... # A...... # ....... # ....... # ....... # ....... #
+  ....... # ....... # A...... # ....... # ....... # ....... #
+  ....... # ....... # ....... # A...... # ....... # ....... #
+  ....... # .....T. # ....... # ....... # A...... # ....... #
+  .....T. # ....... # .....T. # ....... # ....... # A.....T #
+  ....... # ....... # ....... # .....T. # ......T # ....... #
+\end{Verbatim}
+
+\subsection{Shoot - v1}
+\subsubsection{Description}
+In this domain an agent has to chase an adversary.
+The goal is defined by the agent being in the column or row of the adversary.
+The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The set of possile action for the target is ~\{$up$, $right$, $down$, $left$, $leftup\}$.  The agent and the target can move once per turn.
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
+  (B) Bool[And(row-has-AGENT,row-has-TARGET)] [k=3]
+  (C) Dist[col-has-TARGET;adjacent_col;col-has-AGENT] [k=4]
+  (D) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
+
+\end{Verbatim}
+
+\subsubsection{Policy}
+\begin{Verbatim}[fontsize=\footnotesize]
+  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ·, C ↓, D ↑},
+                                    {A ↑, B ·, C ↓, D ↓}, {A ·, B ·, C ↓, D ↓},
+                                    {A ·, B ↑, C ↓, D ↓}
+
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  A...... # ....... # ....... # ....... # ....... # ....... #
+  ....... # A...... # ....... # ....... # ....... # ....... #
+  ....... # ....... # A...... # ....... # ....... # ....... #
+  ....... # ....... # ....... # A...... # ....... # ....... #
+  ....... # .....T. # ....... # ....... # A...... # ....... #
+  .....T. # ....... # .....T. # ....... # ....... # A.....T #
+  ....... # ....... # ....... # .....T. # ......T # ....... #
+\end{Verbatim}
+
 \subsection{Checkmate - v0}
@@
 In the version v0 white pieces have the king and the queen, and black pieces have the king.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  k  .  .  . #
+  # .  .  .  .  . #
+  # .  K  .  .  . #
+  # .  .  .  .  . #
+  # .  .  .  .  Q #
+\end{Verbatim}
 
@@
   (E) Bool[And(cell-has-black_king,Exists(adjacent_cell,cell-has-white_queen))] [k=5]
-
+  (F) Bool[And(col-has-white_king,Exists(adjacent_col,col-has-white_queen))] [k=5]
+  (G) Bool[And(row-has-black_king,Exists(adjacent_row,row-has-white_king))] [k=5]
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. E=0 AND A>0 AND B=0 AND C=0 AND D=0 -> {A ·, B ↑, C ·, D ·, E ↑}, {A ·, B ·, C ·, D ↑, E ·}
-  2. E=0 AND A=0 AND B=0 AND C>0 AND D=0 -> {A ·, B ·, C ·, D ↑, E ↑}, {A ·, B ↑, C ·, D ·, E ·}
-  3. E=0 AND A>0 AND B>0 AND C=0 AND D=0 -> {A ·, B ↓, C ·, D ↑, E ·}
-  4. E=0 AND A=0 AND B=0 AND C=0 AND D=0 -> {A ·, B ·, C ·, D ·, E ↑}
-  5. E=0 AND A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ·, D ↓, E ·}
+  1. A>0 AND B=0 AND C=0 AND D=0 AND E=0 AND F=0 AND G=0 -> {A ·, B ·, C ·, D ↑, E ·, F ·, G ·},
+                                                            {A ·, B ↑, C ·, D ·, E ↑, F ·, G ·}
+  2. A=0 AND B=0 AND C>0 AND D=0 AND E=0 AND F>0 AND G=0 -> {A ·, B ↑, C ·, D ·, E ·, F ↓, G ·}
+  3. A=0 AND B=0 AND C>0 AND D=0 AND E=0 AND F=0 AND G=0 -> {A ·, B ·, C ·, D ↑, E ↑, F ↑, G ·},
+                                                            {A ·, B ↑, C ·, D ·, E ·, F ·, G ·}
+  4. A=0 AND B=0 AND C=0 AND D=0 AND E=0 AND F=0 AND G=0 -> {A ·, B ↑, C ·, D ·, E ↑, F ↑, G ·},
+                                                            {A ·, B ·, C ·, D ·, E ↑, F ↑, G ·}
+  5. A>0 AND B=0 AND C=0 AND D=0 AND E=0 AND F>0 AND G=0 -> {A ·, B ↑, C ·, D ·, E ↑, F ↓, G ·},
+                                                            {A ·, B ·, C ·, D ↑, E ·, F ↓, G ·}
+  6. A=0 AND B=0 AND C>0 AND D>0 AND E=0 AND F>0 AND G=0 -> {A ·, B ↑, C ·, D ↓, E ·, F ↓, G ·}
+  7. A=0 AND B=0 AND C=0 AND D=0 AND E=0 AND F>0 AND G=0 -> {A ·, B ↑, C ·, D ·, E ↑, F ·, G ·},
+                                                            {A ·, B ·, C ·, D ·, E ↑, F ·, G ·}
+  8. A=0 AND B=0 AND C>0 AND D>0 AND E=0 AND F=0 AND G=0 -> {A ·, B ↑, C ·, D ↓, E ·, F ·, G ·}
+  9. A=0 AND B=0 AND C=0 AND D=0 AND E=0 AND F=0 AND G>0 -> {A ·, B ·, C ·, D ↑, E ↑, F ↑, G ·}
+  10. A=0 AND B=0 AND C=0 AND D=0 AND E=0 AND F>0 AND G>0 -> {A ·, B ·, C ·, D ↑, E ↑, F ·, G ·}
+  11. A>0 AND B>0 AND C=0 AND D=0 AND E=0 AND F=0 AND G=0 -> {A ·, B ↓, C ·, D ↑, E ·, F ·, G ·}
+\end{Verbatim}
 
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  K  .  .  #  .  .  .  .  .  .  .  K  .  .  #
+  .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  Q  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
 \end{Verbatim}
@@
 Otherwise he loses.
-In the version v0 white pieces have the king and the tower, and black pieces have the king.
+In the version v0 white pieces have the king and the rook, and black pieces have the king.
+
+\subsubsection{Training instances:}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  k  .  .  . #
+  # .  .  .  .  . #
+  # .  K  .  .  . #
+  # .  .  .  .  . #
+  # .  .  .  .  R #
+\end{Verbatim}
 
@@
   (A) Bool[And(col-has-black_king,col-has-white_king)] [k=3]
-  (B) Bool[And(col-has-black_king,col-has-white_tower)] [k=3]
-  (C) Bool[And(row-has-black_king,row-has-white_tower)] [k=3]
+  (B) Bool[And(col-has-black_king,col-has-white_rook)] [k=3]
+  (C) Bool[And(row-has-black_king,row-has-white_rook)] [k=3]
 
@@
   2. A=0 AND B=0 AND C=0 -> {A ·, B ↑, C ·}
+\end{Verbatim}
 
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  K  .  k  #  .  .  .  .  .  .  .  K  .  k  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  .  .  R  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  R  #
+  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
 \end{Verbatim}

### 2021-05-27 experiments/checkmate_tactic.py

@@ -1,3 +1,4 @@
+import copy
 import math
 from sltp.util.misc import update_dict
 from gpl.domains.grid_games.domain import Domain
@@ -9,11 +10,13 @@ from gpl.domains.grid_games.envs.checkmate_tactic import CHECKMATE, STALEMATE, N
 ct_params = Bunch({
     'domain_name': 'checkmate_tactic',
     'use_player_as_feature': True,
+    'use_next_player_as_feature': False,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
-    'use_adjacency': {CELL_S},
+    'use_margin_as_feature': True,
+    'use_adjacency': {CELL_S, COL_S, ROW_S},
     'use_bidirectional': {},
-    'sorts_to_use': {COL_S, ROW_S, CELL_S},
+    'sorts_to_use': {CELL_S, COL_S, ROW_S},
     'n_moves': 1,
     'unary_predicates': {},
     # 'unary_predicates': {"{}_{}".format(N_MOVE, i) for i in range(CHECKMATE_IN_N + 1)},
@@ -55,8 +58,8 @@ def experiments():
         distinguish_goals=True,
         sampling_strategy="full",
 
-        # skip_train_steps=[0, 1, 2],  # do not generate features twice!
-        skip_train_steps=[],
+        skip_train_steps=[0, 1, 2, 3],  # do not generate features twice!
+        # skip_train_steps=[],
 
         # rollouts
         # num_episodes=1,
@@ -74,18 +77,24 @@ def experiments():
     exps = dict()
     exps["1"] = update_dict(
         base,
-        instances=list(range(50)) + [74, 76, 77, 79, 86, 50, 52, 118, 142, 147, 159, 169, 187, 200, 201, 202, 206, 208,
-                                     221, 223, 233, 235, 242, 244, 78, 80, 81, 83, 90, 92, 96, 98, 327, 56, 222, 224,
-                                     228, 230, 243, 245, 255, 257, 264, 266, 267, 269, 294, 296, 309, 311, 315],
-        test_instances=list(range(2000)),
+        # instances=[1, 9, 11, 43, 45, 47, 48, 49, 50, 56, 57, 62, 63, 65, 68, 69, 71, 77, 78, 80, 81, 83, 89, 90, 93, 98,
+        #            99, 15, 18, 19, 23, 24, 25, 26, 28, 30, 32, 82, 84, 101, 110, 111, 112, 113, 124, 125, 126, 128, 13, 35,
[…]

### 2021-05-27 experiments/nim.py

@@ -13,6 +13,7 @@ from gpl.domains.grid_games.envs.nim import ONLY_ONE_LEFT
 nim_params = Bunch({
     'domain_name': 'nim',
     'use_player_as_feature': True,
+    'use_next_player_as_feature': False,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
     'use_adjacency': {CELL_S},

### 2021-05-27 experiments/shoot.py

@@ -13,6 +13,7 @@ from gpl.domains.grid_games.grammar.objects import PLAYER1, PLAYER2
 shoot_params = Bunch({
     'domain_name': 'shoot',
     'use_player_as_feature': True,
+    'use_next_player_as_feature': False,
     'map_cells': False,
     'use_diagonals_for_map_cells': True,
     'use_adjacency': {COL_S, ROW_S},

### 2021-05-27 src/gpl/domains/grid_games/domain.py

@@ -49,7 +49,7 @@ def load_general_lang(lang, statics, env):
     params = env.params
     for sort in params.sorts_to_use:
         lang.sort(sort)
-        for o in OBJECTS.general:
+        for o in OBJECTS.general | {OBJECTS.none}:
             lang.predicate(f'{sort}-has-{o}', sort)
         if sort in params.use_adjacency:
             lang.predicate(f'{ADJACENT}_{sort}', sort, sort)
@@ -89,17 +89,17 @@ def load_general_problem(problem, lang, rep, env):
         for c in range(-1, ncols + 1):
             for sort in params.sorts_to_use:
                 o = brd[r, c] if (nrows > r >= 0 and ncols > c >= 0) else OBJECTS.none
-                if o == OBJECTS.none:
+                if o == OBJECTS.none and not params.use_margin_as_feature:
                     continue
                 try:
                     map_sorts[(r, c, sort)] = lang.constant(CONST[sort](r, c, nrows, ncols), lang.get(sort))
                 except:
                     map_sorts[(r, c, sort)] = lang.get(CONST[sort](r, c, nrows, ncols))
-                if o not in {OBJECTS.empty, OBJECTS.none}:
+                if o not in {OBJECTS.empty}:
                     problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
 
     def __add_direction_predicate(problem, lang, direction, sort, const, new_r, new_c):
-        if new_r<0 or new_c<0 or ncols==new_c or nrows==new_r:
+        if (new_r<0 or new_c<0 or ncols==new_c or nrows==new_r) and not params.use_margin_as_feature:
             return
         if sort in params.use_adjacency:
             problem.init.add(lang.get(f'{ADJACENT}_{sort}'), const, lang.get(CONST[sort](new_r, new_c, nrows, ncols)))
@@ -111,31 +111,31 @@ def load_general_problem(problem, lang, rep, env):
             continue
         if sort in {CELL_S, COL_S, D1_S, D2_S}:
             # Right
-            if col < ncols - 1:
+            if col < ncols:
                 __add_direction_predicate(problem, lang, RIGHT, sort, const, row, col + 1)
             # Left
             if col > 0:
                 __add_direction_predicate(problem, lang, LEFT, sort, const, row, col - 1)
         if sort in {CELL_S, ROW_S}:
             # Down
-            if row < nrows - 1:
+            if row < nrows:
[…]

### 2021-05-27 src/gpl/domains/grid_games/envs/delivery.py

@@ -10,11 +10,11 @@ from ..utils import identify_next_player
 
 
 SIMPLIFIED_OBJECT = {
-    EMPTY:' . ',
-    AGENT:' A ',
-    PACKAGE:' p ',
-    DESTINY:' D ',
-    PIT:' * ',
+    EMPTY:'.',
+    AGENT:'A',
+    PACKAGE:'p',
+    DESTINY:'D',
+    PIT:'*',
 }
 
 opposite_player = lambda c: PLAYER2 if c == PLAYER1 else PLAYER1
@@ -72,7 +72,7 @@ ACTION_DROP_DIRECTION = {
 }
 
 # unary predicates
-HOLDING_PACKAGE = 'holding_package'
+HOLDING_PACKAGE = 'holding_pet'
 
 # Begin Wumpus =================================
 

### 2021-05-27 src/gpl/domains/grid_games/grammar/objects.py

@@ -4,15 +4,15 @@ NONE = 'none'
 PLAYER1 = 1
 PLAYER2 = 2
 
-WHITE_KING = 'AGENT'
-# WHITE_KING = 'white_king'
-BLACK_KING = 'TARGET'
-# BLACK_KING = 'black_king'
+# WHITE_KING = 'AGENT'
+WHITE_KING = 'white_king'
+# BLACK_KING = 'TARGET'
+BLACK_KING = 'black_king'
 WHITE_QUEEN = 'white_queen'
-WHITE_TOWER = 'white_tower'
+WHITE_TOWER = 'white_rook'
 MARTIAN = 'martian'
 TARGET_MARTIAN = 'target_martian'
-PACKAGE = 'package'
+PACKAGE = 'pet'
 DESTINY = 'destiny'
 PIT = 'pit'
 AGENT = 'agent'

### 2021-05-27 src/gpl/domains/grid_games/grammar/state_to_atoms.py

@@ -16,9 +16,9 @@ def state_to_atoms(domain_name, state, p):
         for c in range(-1, ncols + 1):
             for sort in p.sorts_to_use:
                 o = brd[r, c] if (nrows > r >= 0 and ncols > c >= 0) else OBJECTS.none
-                if o == OBJECTS.none:
+                if o == OBJECTS.none and not p.use_margin_as_feature:
                     continue
-                if o not in {OBJECTS.empty, OBJECTS.none}:
+                if o not in {OBJECTS.empty}:
                     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
 
     for u in p.unary_predicates:

### 2021-05-27 doc/paper/paper.tex
some changes

@@
 In this domain the agent can shoot, move to the right or to the left.
-The agent has two actions per turn and the adversary one.
-To win the agent has to kill all the opponents, for this he must shoot each of them.
+The agent $A$ has two actions per turn and the mastians $m$ one.
+To win the agent has to kill all the martians, for this he must shoot each of them.
 The agent kills an opponent if he shoots while being in the same column, and he can only kill one for each shoot.
-The adversary has three possible actions, left, right and down, all the adversaries move in the same direction.
+The martians has three possible actions, left, right and down, all the adversaries move in the same direction.
 The agent cannot be destroyed by the opponents.
+The agent can select a Martian as a target $M$.
 
@@
 \subsubsection{Description}
-In this domain the agent can move to the right or to the left.
-TThe agent has two actions per turn and the adversary one.
-To win the agent has to kill all the opponents, for this he must shoot each of them.
+In this domain the agent $A$ can move to the right or to the left.
+The agent has two actions per turn and the martians $m$ one.
+To win the agent has to kill all the martians, for this he must shoot each of them.
 The agent kills an opponent if he moves into the column of the adversary, and he can only kill one for each shoot.
@@
 The agent cannot be destroyed by the opponents.
+The agent can select a Martian as a target $M$.
 
@@
 \subsubsection{Description}
-In this domain an agent has to chase an adversary.
-The goal is defined by the agent being in a target adjacent cell.
+In this domain an agent $A$ has to chase an adversary $T$.
+The goal is defined by the agent being in a adversary's adjacent cell.
 The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
@@
 The agent can move only diagonally and the adversary can move in perpendicular directions.
-The agent and the target can move only once per turn.
+The agent and the adversary can move only once per turn.
 
@@
 The goal is defined by the agent being in a target adjacent cell.
-The set of possile actions for the agent and the target is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The set of possile actions for the agent and the adversary is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
 The agent can move twice per turn and the adversary can move once per turn.
@@
 \subsubsection{Description}
-In this game the action space is equal to the number of cells in the grid.
+In this game the action space is equal to the number of tokens $t$ in the grid.
 In order to win the agent has to remove the last token in his turn.
@@
 
-In this domain the agent has to pick up a pet and take it to a certain location.
+In this domain the agent has to pick up a missed pet $p$ and take it to a certain location, the destiny $D$.
 The pet has the option on its turn to escape from its captor to any of the cells adjacent to it.
@@
 Otherwise he loses.
-In the version v0 white pieces have the king and the queen, and black pieces have the king.
+In the version $checkmate-v0$ white pieces have the king $K$ and the queen $Q$, and black pieces have the king $k$.
 
@@
 Otherwise he loses.
-In the version v0 white pieces have the king and the rook, and black pieces have the king.
+In the version $checkmate-v1$ white pieces have the king and the rook $R$, and black pieces have the king.
 

### 2021-05-27 doc/paper/paper.tex
doc changes

@@
 \begin{Verbatim}[fontsize=\footnotesize]
-(A) Num[cell-has-martian] [k=1]
-(B) Bool[cell-has-target_martian] [k=1]
-(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
+(A) Num[cell-has-martian] [k=1]: number of martians
+(B) Bool[cell-has-target_martian] [k=1]: there is one target martian
+(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]: absolute horizontal distance between agent and target martian
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Num[cell-has-martian] [k=1]
-  (B) Bool[cell-has-target_martian] [k=1]
-  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
+  (A) Num[cell-has-martian] [k=1]: number of martians
+  (B) Bool[cell-has-target_martian] [k=1]: there is one target martian
+  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]: absolute horizontal distance between agent and target martian
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
-  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
-  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
-  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
+  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]: the column of the agent is adjacent to the column of the adversary
+  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]: the row of the agent is adjacent to the row of the adversary
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]: absolute vertical distance between agent and adversary
+  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]: absolute horizontal distance between agent and adversary
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]
-  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]
-  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]
+  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]: number of tokens with a token immediately to the left of it
+  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]: number of tokens with a token immediately to the leftdown of it
+  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]: number of tokens with a token immediately to the rightdown of it
 
@@
 
-In this domain the agent has to pick up a missed pet $p$ and take it to a certain location, the destiny $D$.
+In this domain the agent has to pick up a missed pet $p$ and take it to a certain location, the destination $D$.
 The pet has the option on its turn to escape from its captor to any of the cells adjacent to it.
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Atom[holding_pet] [k=1]
-  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destiny))] [k=5]
-  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destiny] [k=4]
-  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
+  (A) Atom[holding_pet] [k=1]: the agent is holding the pet
+  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destination))] [k=5]: the destination is adjacent to the agent
+  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]: manhattan distance between agent and destination
+  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]: manhattan distance between agent and pet
 \end{Verbatim}

### 2021-05-27 doc/paper/paper.tex
doc changes

--- 2021-05-27 doc/paper/paper.tex
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-(A) Num[cell-has-martian] [k=1]
-(B) Bool[cell-has-target_martian] [k=1]
-(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
+(A) Num[cell-has-martian] [k=1]:
+number of martians
+
+(B) Bool[cell-has-target_martian] [k=1]:
+there is some target martian
+
+(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
+absolute horizontal distance between agent and target martian
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Num[cell-has-martian] [k=1]
-  (B) Bool[cell-has-target_martian] [k=1]
-  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
+  (A) Num[cell-has-martian] [k=1]:
+  number of martians
+
+  (B) Bool[cell-has-target_martian] [k=1]:
+  there is one target martian
+
+  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
+  absolute horizontal distance between agent and target martian
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
-  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
-  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
-  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
+  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]:
+  the column of the agent is adjacent to the column of the adversary
+
+  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]:
+  the row of the agent is adjacent to the row of the adversary
+
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]:
+  absolute vertical distance between agent and adversary
+
+  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]:
+  absolute horizontal distance between agent and adversary
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]
-  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]
-  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]
+  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]:
+  number of tokens with a token immediately to the left of it
+
+  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]:
+  number of tokens with a token immediately to the leftdown of it
+
+  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]:
+  number of tokens with a token immediately to the rightdown of it
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Atom[holding_pet] [k=1]
-  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destiny))] [k=5]
-  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destiny] [k=4]
-  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
+  (A) Atom[holding_pet] [k=1]:
+  the agent is holding the pet
+
+  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destination))] [k=5]:
+  the destination is adjacent to the agent
+
+  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]:
+  manhattan distance between agent and destination
+
+  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]:
+  manhattan distance between agent and pet
 \end{Verbatim}

### 2021-05-27 doc/paper/paper.tex
added policy descriptions for space invaders

@@
 \begin{Verbatim}[fontsize=\footnotesize]
-(A) Num[cell-has-martian] [k=1]:
-number of martians
+(A) Num[cell-has-martian] [k=1]
+(B) Bool[cell-has-target_martian] [k=1]
+(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
+\end{Verbatim}
 
-(B) Bool[cell-has-target_martian] [k=1]:
-there is some target martian
-
-(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
-absolute horizontal distance between agent and target martian
-\end{Verbatim}
+\subsubsection{Feature Descrition}
+$A$. Number of martians\\
+$B$. There is some target martian\\
+$C$. Absolute horizontal distance between agent and target martian
 
@@
     2. A=0 AND B>0 AND C=0 -> {A ·, B ↓, C ↑}
-    3. A>0 AND B>0 AND C=0 -> {A ↓, B ·, C ↑}, {A ↓, B ·, C ·}
+    3. A>0 AND B>0 AND C=0 -> {A ↓, B ·}
 \end{Verbatim}
+
+\subsubsection{Policy Description}
+According to the first rule if the distance between the agent and the target martian is greater than zero, it is good to decrease this distance, i.e.
+move towards the target martian.
+The third rule is applicable when there are several Martians and the agent is in the same column as the targeted Martian, and indicates that in this abstraction of the state it is good to decrease the number of Martians.
+The second rule indicates that if there is only one Martian left, and we are below him, it is good to eliminate him.
 
@@
 In this domain the agent $A$ can move to the right or to the left.
-The agent has two actions per turn and the martians $m$ one.
+The agent has two actions per turn and the martians $m$ have one.
 To win the agent has to kill all the martians, for this he must shoot each of them.
 The agent kills an opponent if he moves into the column of the adversary, and he can only kill one for each shoot.
-The adversary has three possible actions, left, right and down, all the adversaries move in the same direction.
+The adversary has three possible actions, left, right and down, and all the adversaries move in the same direction.
 The agent cannot be destroyed by the opponents.
@@
   (A) Num[cell-has-martian] [k=1]:
-  number of martians
-
   (B) Bool[cell-has-target_martian] [k=1]:
-  there is one target martian
-
   (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
@@
 \end{Verbatim}
+
+\subsubsection{Feature Descrition}
+$A$. Number of martians\\
+$B$. There is some target martian\\
+$C$. Absolute horizontal distance between agent and target martian
 
@@
   2. B>0 AND C>0 -> {A ·, B ·, C ↓}
-  3. A=0 AND B>0 AND C>0 -> {A ·, B ↓, C ↑}
-  4. A>0 AND B>0 AND C>0 -> {A ↓, B ·, C ↓},
-                            {A ↓, B ·, C ↑},
-                            {A ↓, B ·, C ·}
+  3. A=0 AND B>0 AND C>0 -> {A ·, B ↓}
+  4. A>0 AND B>0 AND C>0 -> {A ↓, B ·}
 \end{Verbatim}
+
+\subsubsection{Policy Description}
+In the $Space Invaders - v1$ the agent cannot shoot, but he can kill the Martians by positioning himself in their column.
+According to the second rule, if the agent is not in the column of the target Martian, it is good to move closer to this column.
+According to the first rule of the policy, if we are below the target Martian, it is good to increase the horizontal distance between him and the agent.
+Intuitively, if the agent is under the target Martian, it is good to for the agent to moves away from the target martinan and then get in his column and finish him off.
+Finally, rules three and four say that transitions to states where the number of Martians has decreased are good.
 
@@
 Otherwise he loses.
-In the version $checkmate-v0$ white pieces have the king $K$ and the queen $Q$, and black pieces have the king $k$.
+In $Checkmate-v0$ white pieces have the king $K$ and the queen $Q$, and black pieces have the king $k$.
 
@@
 Otherwise he loses.
-In the version $checkmate-v1$ white pieces have the king and the rook $R$, and black pieces have the king.
+In $Checkmate-v1$ white pieces have the king and the rook $R$, and black pieces have the king.
 

### 2021-05-28 doc/paper/paper.tex
changes in doc

@@
 (B) Bool[cell-has-target_martian] [k=1]
-(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
+(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Num[cell-has-martian] [k=1]:
-  (B) Bool[cell-has-target_martian] [k=1]:
-  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]:
+  (A) Num[cell-has-martian] [k=1]
+  (B) Bool[cell-has-target_martian] [k=1]
+  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
   absolute horizontal distance between agent and target martian
@@
   ..A. # ...A # ..A. # ..A. # ...A # ..A. # ..A. # .A.. # ..A. # ..A. # .A.. # A... #
-  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)
 \end{Verbatim}
@@
 
-\subsubsection{Training instances:}
+\subsubsection{Training instances}
 \begin{Verbatim}[fontsize=\footnotesize]
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]:
-  the column of the agent is adjacent to the column of the adversary
-
-  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]:
-  the row of the agent is adjacent to the row of the adversary
-
-  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]:
-  absolute vertical distance between agent and adversary
-
-  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]:
-  absolute horizontal distance between agent and adversary
+  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
+  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
 \end{Verbatim}
 
-\subsubsection{Policy (with no fixed action space)}
+\subsubsection{Feature Descrition}
+$A$. The column of the agent is adjacent to the column of the adversary\\
+$B$. The row of the agent is adjacent to the row of the adversary\\
+$C$. Absolute vertical distance between agent and adversary\\
+$D$. Absolute horizontal distance between agent and adversary
+\subsubsection{Policy}
 
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND D>0 AND C=0 -> {A ↑, B ↑, C ↑, D ↓}, {A ·, B ↑, C ↑, D ↓}
-  2. A=0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ↓}, {A ↑, B ↑, C ↓, D ↓},
-                                    {A ·, B ·, C ↓, D ↓}, {A ↑, B ·, C ↓, D ↓}
-  3. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ↓, C ↓, D ↓}, {A ↑, B ↓, C ↓, D ↓}
-  4. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, B ·, C ↓, D ↓}, {A ↓, B ↑, C ↓, D ↓}
-  5. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, B ·, C ↓, D ↑}, {A ↑, B ↑, C ↓, D ↑}
+  1. A=0 AND B=0 AND D>0 AND C=0 -> {B ↑, C ↑, D ↓}
+  2. A=0 AND B=0 AND D>0 AND C>0 -> {C ↓, D ↓}
+  3. A=0 AND B>0 AND D>0 AND C>0 -> {B ↓, C ↓, D ↓}
+  4. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, C ↓, D ↓}
+  5. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, C ↓, D ↑}
+\end{Verbatim}
 
-\end{Verbatim}
+\subsubsection{Policy Description}
+According to rule three, if the agent is in the row adjacent to the adversary, it is good to stand in the same row as him.
+Following the rule four if the agent is in the column adjacent to the opponent it is good to be in the same column.
+According to rule three, if the agent is in the row adjacent to the adversary, it is good to stand in the same row as him.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]:
-  the column of the agent is adjacent to the column of the adversary
-
-  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]:
-  the row of the agent is adjacent to the row of the adversary
-
-  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]:
-  absolute vertical distance between agent and adversary
-
-  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]:
-  absolute horizontal distance between agent and adversary
+  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
+  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
+  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
+  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
 \end{Verbatim}
 
-\subsubsection{Policy (with no fixed action space)}
+\subsubsection{Feature Descrition}
+$A$. The column of the agent is adjacent to the column of the adversary\\
+$B$. The row of the agent is adjacent to the row of the adversary\\
+$C$. Absolute vertical distance between agent and adversary\\
+$D$. Absolute horizontal distance between agent and adversary
+
+\subsubsection{Policy}
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
+  1. A=0 AND B=0 AND C>0 -> {A ·, C ↓, D ·}
   2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
-  3. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ·, C ·, D ↓}, {A ↑, B ·, C ·, D ↓}
-  4. B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
+  3. A=0 AND B=0 AND D>0 AND C=0 -> {B ·, C ·, D ↓}
+  4. B=0 AND D>0 AND C>0 -> {A ·, C ↓, D ·}
   5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
-  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
-  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, B ·, C ↓, D ·}, {A ·, B ↑, C ↓, D ·}
+  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, C ↓, D ·}
+  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, C ↓, D ·}
+\end{Verbatim}
 
-\end{Verbatim}
+\subsubsection{Policy Description}
+According to rule two, if the agent is in the opponent's adjacent row, it is good to reduce the distance between them without moving from the adjacent row.
+Rule six is the same as 2 but with the column.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]:
-  number of tokens with a token immediately to the left of it
+  (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]
+  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]
+  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]
+\end{Verbatim}
 
-  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]:
-  number of tokens with a token immediately to the leftdown of it
-
-  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]:
-  number of tokens with a token immediately to the rightdown of it
-
-\end{Verbatim}
+\subsubsection{Feature Descrition}
+$A$. Number of tokens with a token immediately to the left of it\\
+$B$. Number of tokens with a token immediately to the leftdown of it\\
+$C$. Number of tokens with a token immediately to the rightdown of it\\
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A>0 AND B>0 AND C>0 -> {A ·, B ↓, C ↓}
-  2. B>0 AND C>0 -> {A ·, B ↓, C ↓}
+  1. B>0 AND C>0 -> {A ·, B ↓, C ↓}
+\end{Verbatim}
 
-\end{Verbatim}
+\subsubsection{Policy Description}
+The policy can be interpreted as leaving the two token stacks with the same number of tokens.
+This is done by decreasing the number of tokens that have a token to their leftdown or rightdown without decreasing the number of tokens with a token next to them.
 
@@
 The agent has two actions per turn and the adversary one.
-The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The set of possile actions for the agent is ~\{$pick$, $rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The agent to pick up the pet has to execute the $pick$ action or move to the same cell where the pet is located.
 The set of possile actions for the pet consist in escape to one of the adjacent cells to the agent, i.e.
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Atom[holding_pet] [k=1]:
-  the agent is holding the pet
+  (A) Atom[holding_pet] [k=1]
+  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destination))] [k=5]
+  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]
+  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
+\end{Verbatim}
 
-  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destination))] [k=5]:
-  the destination is adjacent to the agent
-
-  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]:
-  manhattan distance between agent and destination
-
-  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]:
-  manhattan distance between agent and pet
-\end{Verbatim}
+\subsubsection{Feature Descrition}
+$A$. The agent is holding the pet\\
+$B$. The destination is adjacent to the agent\\
+$C$. Manhattan distance between agent and destination\\
+$D$. Manhattan distance between agent and pet
 
@@
   1. B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ·}
-  2. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ↓}, {A ·, B ·, C ↑, D ↓},
-                                    {A ↑, B ·, C ·, D ↑}, {A ·, B ·, C ·, D ↓}
+  2. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ↓},
+                                    {A ·, B ·, C ↑, D ↓},
+                                    {A ↑, B ·, C ·, D ↑},
+                                    {A ·, B ·, C ·, D ↓}
   3. A>0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↓, D ·}
   4. A=0 AND B>0 AND C>0 AND D>0 -> {A ·, B ↓, C ↑, D ↓}
+\end{Verbatim}
 
-\end{Verbatim}
+\subsubsection{Policy Description}
+According to the third rule, if the agent has the pet, it is good to move towards the destination.
+According to the fourth rule of the policy, if the agent does not have the pet, it is good to increase the distance to the destination and decrease the distance to the pet.
+Finally, according to the second rule, it is good to take the pet if you have the possibility, and if not, it is good to decrease the distance between the agent and the pet.
 
@@
   (C) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
-
 \end{Verbatim}

### 2021-05-28 doc/paper/paper.tex
improve in doc

@@
 \subsubsection{Description}
-In this domain the agent can shoot, move to the right or to the left.
-The agent $A$ has two actions per turn and the mastians $m$ one.
+In this domain the agent can $shoot$, move to the $right$ or to the $left$.
+The agent during his turn can do two actions, while the Martians can do one.
+Note that if the Martians and the agent have only one action per turn the agent cannot win, this is because of the situation where the agent stands in the Martian's column to shoot him on his next turn, but the next turn (the Martian's turn) the Martian can move away, this leads to an infinite loop if both are playing perfectly.
+That is, the agent must be able to move to the agent's column and then shoot.
 To win the agent has to kill all the martians, for this he must shoot each of them.
 The agent kills an opponent if he shoots while being in the same column, and he can only kill one for each shoot.
-The martians has three possible actions, left, right and down, all the adversaries move in the same direction.
-The agent cannot be destroyed by the opponents.
-The agent can select a Martian as a target $M$.
+The martians has three possible actions $left$, $right$, $up$ and $down$.
+All the adversaries move in the same direction.
+The agent cannot be destroyed in any way by the Martians, they can go down to the row above the agent.
+The agent cannot collide with the Martians as they cannot descend to the row above it.
+Note that the policy found is optimal and will solve all possible instances of the game.
+The policy is also optimal for a version of the game where the Martians destroy the agent when they reach the row above him.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  #m...m#
-  #m...M#
-  #.....#
-  #...A.#
+  # m  .  .  m #
+  # m  .  .  m #
+  # .  .  .  . #
+  # .  .  .  . #
+  # .  .  .  . #
+  # .  .  A  . #
 \end{Verbatim}
@@
 (A) Num[cell-has-martian] [k=1]
-(B) Bool[cell-has-target_martian] [k=1]
-(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
+(B) Dist[col-has-agent;adjacent_col;col-has-martian] [k=4]
 \end{Verbatim}
@@
 $A$. Number of martians\\
-$B$. There is some target martian\\
-$C$. Absolute horizontal distance between agent and target martian
+$B$. Minimum absolute horizontal distance between a column with an agent and a column with martian
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-    1. B>0 AND C>0 -> {A ·, B ·, C ↓}
-    2. A=0 AND B>0 AND C=0 -> {A ·, B ↓, C ↑}
-    3. A>0 AND B>0 AND C=0 -> {A ↓, B ·}
+  1. A>0 AND B>0 -> {A ·, B ↓}
+  2. A>0 AND B=0 -> {A ↓}
 \end{Verbatim}
@@
 \subsubsection{Policy Description}
-According to the first rule if the distance between the agent and the target martian is greater than zero, it is good to decrease this distance, i.e.
-move towards the target martian.
-The third rule is applicable when there are several Martians and the agent is in the same column as the targeted Martian, and indicates that in this abstraction of the state it is good to decrease the number of Martians.
-The second rule indicates that if there is only one Martian left, and we are below him, it is good to eliminate him.
+According to the first rule if the agent is not in the column of a Martian, $B$ is greater than zero, it is good to decrement $B$, i.e.
+move towards the closest martian.
+The second rule is applicable when the agent is under a Martian, in the same column, and according to this rule it is good to decrease the number of Martians, i.e.
+execute the action $shoot$.
 
@@
   ..A. # .A.. # A... # A... # A... # A... # A... # .A.. # ..A. # ..A. # ...A # ...A # ...A # ..A. # ..A. #
-\end{Verbatim}
-
-\subsection{Space Invaders - v1}
-\subsubsection{Description}
-In this domain the agent $A$ can move to the right or to the left.
-The agent has two actions per turn and the martians $m$ have one.
-To win the agent has to kill all the martians, for this he must shoot each of them.
-The agent kills an opponent if he moves into the column of the adversary, and he can only kill one for each shoot.
-The adversary has three possible actions, left, right and down, and all the adversaries move in the same direction.
-The agent cannot be destroyed by the opponents.
-The agent can select a Martian as a target $M$.
-
-\subsubsection{Training instances:}
-\begin{Verbatim}[fontsize=\footnotesize]
-  #m...m#
-  #m...M#
-  #.....#
-  #...A.#
-\end{Verbatim}
-
-\subsubsection{Features}
-\begin{Verbatim}[fontsize=\footnotesize]
-  (A) Num[cell-has-martian] [k=1]
-  (B) Bool[cell-has-target_martian] [k=1]
-  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
-  absolute horizontal distance between agent and target martian
-\end{Verbatim}
-
-\subsubsection{Feature Descrition}
-$A$. Number of martians\\
-$B$. There is some target martian\\
-$C$. Absolute horizontal distance between agent and target martian
-
-\subsubsection{Policy}
-\begin{Verbatim}[fontsize=\footnotesize]
-  1. B>0 AND C=0 -> {A ·, B ·, C ↑}
-  2. B>0 AND C>0 -> {A ·, B ·, C ↓}
-  3. A=0 AND B>0 AND C>0 -> {A ·, B ↓}
-  4. A>0 AND B>0 AND C>0 -> {A ↓, B ·}
-\end{Verbatim}
-
-\subsubsection{Policy Description}
-In the $Space Invaders - v1$ the agent cannot shoot, but he can kill the Martians by positioning himself in their column.
-According to the second rule, if the agent is not in the column of the target Martian, it is good to move closer to this column.
-According to the first rule of the policy, if we are below the target Martian, it is good to increase the horizontal distance between him and the agent.
-Intuitively, if the agent is under the target Martian, it is good to for the agent to moves away from the target martinan and then get in his column and finish him off.
-Finally, rules three and four say that transitions to states where the number of Martians has decreased are good.
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  m..m # m..M # m..M # .... # .... # .... # .... # .... # .... # .... # .... # .... #
-  m..M # m... # m... # m..M # m... # m... # .m.. # .M.. # .M.. # M... # M... # .... #
-  .... # .... # .... # m... # M... # M... # .M.. # .... # .... # .... # .... # .... #
-  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
-  ..A. # ...A # ..A. # ..A. # ...A # ..A. # ..A. # .A.. # ..A. # ..A. # .A.. # A... #
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
-  (B) Bool[And(col-has-AGENT,Exists(adjacent_col,col-has-TARGET))] [k=5]
-  (C) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
+  (A) Bool[And(col-has-agent,col-has-adversary)] [k=3]
+  (B) Bool[And(col-has-agent,Exists(adjacent_col,col-has-adversary))] [k=5]
+  (C) Dist[row-has-agent;adjacent_row;row-has-adversary] [k=4]
 \end{Verbatim}
+
+\subsubsection{Feature Description}
+$A$. The agent and the adversary are in the same column\\
+$B$. The agent column is adjacent to the adversary column\\
+$C$. Absolute vertical distance between the agent and the adversary
 
@@
 \end{Verbatim}
+
+\subsubsection{Policy Description}
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ·, C ↓, D ↑},
-                                    {A ↑, B ·, C ↓, D ↓}, {A ·, B ·, C ↓, D ↓},
+  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓},
+                                    {A ↑, B ·, C ↓, D ↑},
+                                    {A ↑, B ·, C ↓, D ↓},
+                                    {A ·, B ·, C ↓, D ↓},
                                     {A ·, B ↑, C ↓, D ↓}
-
 \end{Verbatim}

### 2021-05-30 doc/paper/paper.tex
delivery broken, backup

@@
 
-\subsection{Space Invaders - v0}
+\subsection{Space Invaders}
 \subsubsection{Description}
@@
 $A$. Number of martians\\
-$B$. Minimum absolute horizontal distance between a column with an agent and a column with martian
+$B$. Minimum absolute horizontal distance between a column with an agent and a column with a martian
 
@@
 The goal is defined by the agent being in a adversary's adjacent cell.
-The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
-The set of possile action for the target is ~\{$up$, $right$, $down$, $left$, $leftup\}$.
+The set of possile actions for the agent and the adversary is ~\{$up$, $right$, $down$, $left\}$.
 The agent can move only diagonally and the adversary can move in perpendicular directions.
@@
 According to rule three, if the agent is in the row adjacent to the adversary, it is good to stand in the same row as him.
-Following the rule four if the agent is in the column adjacent to the opponent it is good to be in the same column.
-According to rule three, if the agent is in the row adjacent to the adversary, it is good to stand in the same row as him.
+Following the rule four if the agent is in the column adjacent to the opponent it is good to go into the same column.
 
@@
 The goal is defined by the agent being in a target adjacent cell.
-The set of possile actions for the agent and the adversary is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
+The set of possile actions for the agent and the adversary is ~\{$up$, $down$, $left$, $right\}$.
 The agent can move twice per turn and the adversary can move once per turn.
@@
 
-\subsection{Shoot - v0}
+\subsection{Shoot}
 \subsubsection{Description}
-In this domain an agent has to chase an adversary.
-The goal is defined by the agent being in the column or row of the adversary.
-The set of possile actions for the agent and the target is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
-The agent and the target can move once per turn.
+In this domain an agent has to shoot an adversary.
+The goal is defined by the agent being alone on the grid, having finished with the opponent.
+The agent can execute the action $shoot$, but the opponent does not, so the opponent is able to win the game from any state of any instance if he knows the right strategy.
+The agent and the adversary share the set of actions ~{$up$, $right$, $down$, $left\}$.
+To reach the goal state, the agent has to be in the same row or column as the adverary and execute the action $shoot$.
+When the agent executes the $shoot$ action on the adversary's line, the adversary disappears.
+We can define the goal state, as the adversary not being on the board.
+The agent and the opponent have two actions per turn, so that the agent can stand in the opponent's row or column and shoot before the opponent escapes.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-#A.....#
-#......#
-#......#
-#.....T#
+  # A . . . #
+  # . . . . #
+  # . . . . #
+  # . . . T #
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-has-agent,col-has-adversary)] [k=3]
-  (B) Bool[And(col-has-agent,Exists(adjacent_col,col-has-adversary))] [k=5]
-  (C) Dist[row-has-agent;adjacent_row;row-has-adversary] [k=4]
+  (A) Bool[cell-has-adversary] [k=1]
+  (B) Bool[And(row-has-adversary,row-has-agent)] [k=3]
+  (C) Bool[And(row-has-adversary,Exists(adjacent_row,row-has-agent))] [k=5]
+  (D) Dist[col-has-agent;adjacent_col;col-has-adversary] [k=4]
 \end{Verbatim}
@@
 \subsubsection{Feature Description}
-$A$. The agent and the adversary are in the same column\\
-$B$. The agent column is adjacent to the adversary column\\
-$C$. Absolute vertical distance between the agent and the adversary
+$A$. The adversary is in the board\\
+$B$. The agent and the adversary are in the same row\\
+$C$. The agent row is adjacent to the adversary row\\
+$D$. Absolute horizontal distance between the agent and the adversary
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND C>0 -> {A ·, B ·, C ↓}
-  2. A=0 AND B>0 AND C>0 -> {A ↑, B ↓, C ·}
+  1. A>0 AND B=0 AND C=0 AND D>0 -> {B ·, C ·, D ↓}
+  2. A>0 AND B=0 AND C>0 AND D>0 -> {B ↑, C ↓, D ·}
+  3. A>0 AND D=0 -> {A ↓}
+  4. A>0 AND B>0 -> {A ↓}
 \end{Verbatim}
@@
 \subsubsection{Policy Description}
+According to the fourth rule of the policy, if the agent is in the same column as the agent it is good to decrease $A$, i.e.
+shoot the adversary.
+In the same way, according to the third rule, if the agent is in the same row as the adversary it is good to execute the action $shoot$.
+According to the second rule, if the agent is in the row adjacent to the adversary it is good to get in the same row.
+Finally, according to the first rule, if the agent is not in the row adjacent to the adversary, and is not in the same row or column, it is good to decrease the horizontal distance between the agent and the adversary.
+The first rule can also be read as, it is good for the agent to approach the adversary horizontally if you do not have the possibility to stand, or you are already in a position where it is good to shoot.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  A...... # ....... # ....... # ....... # ....... # ....... #
-  ....... # A...... # ....... # ....... # ....... # ....... #
-  ....... # ....... # A...... # ....... # ....... # ....... #
-  ....... # ....... # ....... # A...... # ....... # ....... #
-  ....... # .....T. # ....... # ....... # A...... # ....... #
-  .....T. # ....... # .....T. # ....... # ....... # A.....T #
-  ....... # ....... # ....... # .....T. # ......T # ....... #
-\end{Verbatim}
+  A....... # .A...... # ..A..... # ..A..... # ...A.... # ....A... # ....A... # .....A.. # ......A. # ......A. # .....A.. # .....A.. #
+  ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
+  ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
+  ........ # ........ # ........ # .....T.. # .....T.. # .....T.. # ......T. # ......T. # ......T. # .....T.. # .....T.. # ........ #
+  .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
 
-\subsection{Shoot - v1}
-\subsubsection{Description}
-In this domain an agent has to chase an adversary.
-The goal is defined by the agent being in the column or row of the adversary.
-The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftdown$, $leftup\}$.
-The set of possile action for the target is ~\{$up$, $right$, $down$, $left$, $leftup\}$.  The agent and the target can move once per turn.
-
-\subsubsection{Features}
-\begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-has-AGENT,col-has-TARGET)] [k=3]
-  (B) Bool[And(row-has-AGENT,row-has-TARGET)] [k=3]
-  (C) Dist[col-has-TARGET;adjacent_col;col-has-AGENT] [k=4]
-  (D) Dist[row-has-TARGET;adjacent_row;row-has-AGENT] [k=4]
-
-\end{Verbatim}
-
-\subsubsection{Policy}
-\begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↑, D ↓},
-                                    {A ↑, B ·, C ↓, D ↑},
-                                    {A ↑, B ·, C ↓, D ↓},
-                                    {A ·, B ·, C ↓, D ↓},
-                                    {A ·, B ↑, C ↓, D ↓}
-\end{Verbatim}
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  A...... # ....... # ....... # ....... # ....... # ....... #
-  ....... # A...... # ....... # ....... # ....... # ....... #
-  ....... # ....... # A...... # ....... # ....... # ....... #
-  ....... # ....... # ....... # A...... # ....... # ....... #
-  ....... # .....T. # ....... # ....... # A...... # ....... #
-  .....T. # ....... # .....T. # ....... # ....... # A.....T #
-  ....... # ....... # ....... # .....T. # ......T # ....... #
 \end{Verbatim}

### 2021-05-30 experiments/space_invaders.py

@@ -14,11 +14,13 @@ space_invaders_params = Bunch({
     'domain_name': 'space_invaders',
     'use_player_as_feature': False,
     'use_next_player_as_feature': False,
+    'use_margin_as_feature': False,
+    'use_target_margin': False,
     'map_cells': True,
     'use_diagonals_for_map_cells': False,
-    'use_adjacency': {COL_S},
+    'use_adjacency': {COL_S, ROW_S},
     'use_bidirectional': {},
-    'sorts_to_use': {CELL_S, COL_S},
+    'sorts_to_use': {CELL_S, COL_S, ROW_S},
     'unary_predicates': {},
     'predicates_arity_1': {},
     'agent_has_to_shoot': True,
@@ -46,12 +48,12 @@ def experiments():
         distance_feature_max_complexity=4,
         concept_generation_timeout=15000,
         cond_feature_max_complexity=0,
-        comparison_features=False,
+        comparison_features=True,
         generate_goal_concepts=False,
         print_denotations=True,
         print_hstar_in_feature_matrix=False,
 
-        verbosity=2,
+        verbosity=3,
         initial_sample_size=100,
         refinement_batch_size=200,
         maxsat_iter=20,
@@ -84,7 +86,7 @@ def experiments():
     # martians can't Kill the Agent
     space_invaders_params_v1 = copy.deepcopy(space_invaders_params)
     space_invaders_params_v1.unary_predicates = {}
-    space_invaders_params_v1.use_player_as_feature = True
+    space_invaders_params_v1.use_player_as_feature = False
     space_invaders_params_v1.use_bidirectional = {}
     space_invaders_params_v1.max_actions={PLAYER1: 2, PLAYER2: 1}
     space_invaders_params_v1.target_columns=False
@@ -92,21 +94,23 @@ def experiments():
         base,
         domain=Domain(space_invaders_params_v1),
         instances=[0, 17, 18],
-        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 17, 18],
+        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 17, 18, 19],
+        allow_bad_states=False,
     )
 
     # version 2: the agent can not shoot, but can kill moving into the adv column, has 2 moves
     space_invaders_params_v2 = copy.deepcopy(space_invaders_params)
     space_invaders_params_v2.unary_predicates = {}
[…]

### 2021-05-30 src/gpl/domains/grid_games/envs/delivery.py

@@ -21,8 +21,8 @@ opposite_player = lambda c: PLAYER2 if c == PLAYER1 else PLAYER1
 
 
 PLAYER_VALID_ACTIONS = {
-    PLAYER1: lambda pos, layout, params: agent_valid_actions(pos, layout, params),
-    PLAYER2: lambda layout, params: wumpus_valid_actions(layout, params),
+    PLAYER1: lambda pos, rep, params: agent_valid_actions(pos, rep, params),
+    PLAYER2: lambda rep, params: wumpus_valid_actions(rep, params),
 }
 
 ALL_DIRECTIONS = [(-1, -1), (-1, 0), (-1, 1), (0, -1), (0, 1), (1, -1), (1, 0), (1, 1)]
@@ -48,6 +48,7 @@ DROP_RIGHTDOWN = 14
 DROP_LEFTDOWN = 15
 
 PICK = 16
+DROP = 17
 
 ACTION_MOVE_DIRECTION = {
     UP: (-1, 0),
@@ -87,11 +88,9 @@ class Env(object):
         assert action in valid_actions
         l = layout.copy()
         if rep.player == PLAYER1:
-            l = layout_after_agent_action(layout, action, self.params)
+            new_rep = rep_after_agent_action(rep, action, self.params)
         else:
-            l = layout_after_wumpus_action(layout, action, self.params)
-        new_rep = copy.deepcopy(rep)
-        new_rep.grid = l
+            new_rep = rep_after_wumpus_action(rep, action, self.params)
         if rep.nact < self.params.max_actions[rep.player]:
             new_rep.nact += 1
         else:
@@ -99,12 +98,11 @@ class Env(object):
             new_rep.player = opposite_player(rep.player)
         if self.params.use_next_player_as_feature:
             new_rep.next_player = identify_next_player(new_rep, self.params)
-        setattr(new_rep, HOLDING_PACKAGE, check_if_holding_package(new_rep.grid))
         return self.__update_rep(new_rep)
 
     def __update_rep(self, rep):
         updated_rep = rep.to_dict()
-        gstatus = Env.check_game_status(rep)
+        gstatus = self.check_game_status(rep)
         if gstatus == 1:
             updated_rep['goal'] = True
         updated_rep['nmoves'] += 1
@@ -114,9 +112,8 @@ class Env(object):
     def get_simplified_objects():
         return SIMPLIFIED_OBJECT
 
-    @staticmethod
-    def check_game_status(rep):
-        if terminated(rep):
[…]

### 2021-05-30 src/gpl/domains/grid_games/envs/shoot.py

@@ -7,6 +7,8 @@ from ..grammar.language import D1_S, D2_S, COL_S, ROW_S
 import numpy as np
 from gpl.utils import Bunch
 import copy
+from ..utils import identify_next_player
+
 
 WHITE = 1 # player 1
 BLACK = 2 # player 2
@@ -78,7 +80,10 @@ class Env(object):
         layout = rep.grid
         l = layout.copy()
         valid_actions = self.available_actions(rep)
-        assert action in valid_actions
+        try:
+            assert action in valid_actions
+        except:
+            raise
         if action == SHOOT and rep.player in self.params.player_can_shoot:
             l = layout_after_shoot(l, rep.player, self.params)
         else:
@@ -101,6 +106,7 @@ class Env(object):
         else:
             new_rep.nact = 0
             new_rep.player = opposite_color(rep.player)
+        new_rep.next_player = identify_next_player(new_rep, self.params)
         return self.__update_rep(new_rep, rep.player)
 
     def __update_rep(self, rep, prev_in_act):
@@ -147,56 +153,28 @@ class Env(object):
         valid_actions = self.available_actions(rep)
         r_wk, c_wk = runnable_position(rep.grid, WHITE)
         r_bk, c_bk = runnable_position(rep.grid, BLACK)
-        if 2 in self.params.player_can_shoot:
-            if r_wk - r_bk == -1:
-                if UP in valid_actions:
-                    return UP
-            if r_wk - r_bk == 1:
-                if DOWN in valid_actions:
-                    return DOWN
-            if c_wk - c_bk == 1:
-                if RIGHT in valid_actions:
-                    return RIGHT
-            if c_wk - c_bk == -1:
-                if LEFT in valid_actions:
-                    return LEFT
-            if r_wk - r_bk == -2:
-                if DOWN in valid_actions:
-                    return DOWN
-            if r_wk - r_bk == 2:
-                if UP in valid_actions:
-                    return UP
-            if c_wk - c_bk == 2:
-                if LEFT in valid_actions:
-                    return LEFT
-            if c_wk - c_bk == -2:
-                if RIGHT in valid_actions:
-                    return RIGHT
-        else:
-            if r_wk - r_bk == 1:
-                if UP in valid_actions:
-                    return UP
-            if r_wk - r_bk == -1:
-                if DOWN in valid_actions:
-                    return DOWN
[…]

### 2021-05-30 src/gpl/domains/grid_games/envs/space_invaders.py

@@ -26,6 +26,7 @@ COLOR_TO_PIECES = {
 
 opposite_color = lambda c: BLACK if c == WHITE else WHITE
 
+
 # Actions IDs
 
 SHOOT = 0
@@ -75,7 +76,7 @@ class Env(object):
         if rep.player == WHITE:
             l = layout_after_agent_action(layout, action_id, self.params)
         elif rep.player == BLACK:
-            l = layout_after_env_action(layout, action_id) if action_id else layout
+            l = layout_after_env_action(layout, action_id, self.params) if action_id else layout
         new_rep = copy.deepcopy(rep)
         new_rep.grid = l
         if rep.nact < self.params.max_actions[rep.player]:
@@ -141,7 +142,7 @@ class Env(object):
 
     def init_instance(self, key):
         rep = {u: False for u in self.params.unary_predicates}
-        rep['grid'] = generate_gird(key)
+        rep['grid'] = generate_gird(key, self.params)
         rep['nact'] = 1
         rep['player'] = WHITE
         rep['goal'] = False
@@ -182,27 +183,29 @@ def martians_valid_actions(layout, params):
     return valid_actions
 
 
-def layout_after_env_action(layout, action_id):
-    assert TARGET_MARTIAN in layout
+def layout_after_env_action(layout, action_id, params):
+    if params.use_target_margin:
+        assert TARGET_MARTIAN in layout
+        target_martian_pos = np.argwhere(layout == TARGET_MARTIAN)[0]
     assert action_id in MARTIANS_ACTION_SPACE
     martians_pos = np.argwhere(layout == MARTIAN)
-    target_martian_pos = np.argwhere(layout == TARGET_MARTIAN)[0]
     martians_new_pos = []
     for pos in martians_pos:
         running_pos = np.add(pos, ACTION_MOVE_DIRECTION[action_id])
         martians_new_pos.append((running_pos[0], running_pos[1]))
-    new_target_martian_pos = np.add(target_martian_pos, ACTION_MOVE_DIRECTION[action_id])
     nrows, ncols = layout.shape
     l = copy.deepcopy(layout)
     l = np.where(l == MARTIAN, EMPTY, l)
-    l = np.where(l == TARGET_MARTIAN, EMPTY, l)
     for pos in martians_new_pos:
         l[pos] = MARTIAN
         if pos[0] == nrows-2:
             l = np.where(l == AGENT, EMPTY, l)
-    l[new_target_martian_pos[0], new_target_martian_pos[1]] = TARGET_MARTIAN
[…]

### 2021-05-30 src/gpl/domains/grid_games/grammar/grammar.py

@@ -34,9 +34,9 @@ class Grammar:
         """
         try:
             b = list(self.object_bytes[obj] for obj in r.grid.flatten())
-            if self.params.use_player_as_feature:
+            if self.params.use_player_to_encode:
                 b = b + [self.object_bytes[r.player]]
-            if self.params.use_next_player_as_feature:
+            if self.params.use_next_player_to_encode:
                 b = b + [self.object_bytes[r.next_player]]
             for u in self.params.unary_predicates:
                 b = b + [self.object_bytes['true']] if getattr(r, u) else b + [self.object_bytes['false']]
@@ -46,9 +46,10 @@ class Grammar:
             # b = b + [self.object_bytes['true']] if info['deadend'] else b + [self.object_bytes['false']]
             return bytes(b)
         except:
-            for o in r.grid.flatten():
-                if o not in self.object_bytes:
-                    print('EXCEPTION: Unknown object: {}'.format(o))
+            raise
+            # for o in r.grid.flatten():
+            #     if o not in self.object_bytes:
+            #         print('EXCEPTION: Unknown object: {}'.format(o))
 
     def objects_to_bytes(self):
         OBJECTS = get_domain_objects(self.domain_name)

### 2021-05-30 src/gpl/domains/grid_games/grammar/objects.py

@@ -11,6 +11,7 @@ BLACK_KING = 'black_king'
 WHITE_QUEEN = 'white_queen'
 WHITE_TOWER = 'white_rook'
 MARTIAN = 'martian'
+# TARGET_MARTIAN = 'martian'
 TARGET_MARTIAN = 'target_martian'
 PACKAGE = 'pet'
 DESTINY = 'destiny'

### 2021-05-30 src/gpl/domains/grid_games/task.py

@@ -42,7 +42,11 @@ class Task(ITask):
             return self.colapse_state(r1)
         op = self.env.player2_policy(r1)
         r2 = self.env.act(r1, op)  # adversary move
-        return self.colapse_state(r2)
+        s2 = self.colapse_state(r2)
+        if r2.player != self.objects.player1:
+            return self.transition_env(s2)
+        else:
+            return s2
 
     def colapse_state(self, rep):
         s_encoded = self.encode_state(rep)
@@ -70,20 +74,19 @@ class Task(ITask):
                 succs.append((op0, s1, s1))
             else:
                 assert s1[0].player == self.objects.player2
-                ava_actions_1 = self.env.available_actions(s1[0])
-                for op1 in ava_actions_1:
-                    # global i
-                    # i += 1
-                    # if i == 76:
-                    #     print('H')
-                    s2 = __transition_player(s1, op1)
-                    # print("{}. deadend: {}, turn: {}".format(i, s2[0].deadend, s2[0].player))
-                    # print(self.get_printable_rep(s2[0]))
-                    # if s2[1] == s1[1]:
-                    #     continue
-                    assert s2[0].player == self.objects.player1
-                    succs.append((op0, s1, s2))
-
+                s2 = copy.deepcopy(s1)
+                queue = [s2]
+                vistited_s2={s2[1]}
+                while queue:
+                    s2_ = queue.pop()
+                    ava_actions_1 = self.env.available_actions(s2_[0])
+                    for op1 in ava_actions_1:
+                        s2 = __transition_player(s2_, op1)
+                        if s2[0].player == self.objects.player1:
+                            succs.append((op0, s1, s2))
+                        else:
+                            if s2[1] not in vistited_s2:
+                                queue.append(s2)
         # succs_reps.append(r0)
         # for _, sp, spp in succs:
         #     succs_reps.append(sp[0])
@@ -139,12 +142,13 @@ class Task(ITask):
             single_rep_row += simplified_objects[o]
         size_single_row = len("{} # ".format(single_rep_row))
 
-        info_to_print = ["player", "nmoves", "last_turn", "next_player"]
+        info_to_print = ["player", "nmoves", "last_turn", "next_player", "holding_pet", "goal"]
         for info in info_to_print:
             try:
                 tmp_full_row = ""
                 for rep in reps:
-                    tmp_full_row += "{} ({})".format(getattr(rep, info), info[:2]).ljust(size_single_row)
[…]

### 2021-05-31 doc/paper/paper.tex
solved new and clean delivery domain

@@
 \begin{Verbatim}[fontsize=\footnotesize]
+
 (A) Num[cell-has-martian] [k=1]
@@
 
-\subsection{Chase - v0}
+\subsection{Chase}
 \subsubsection{Description}
@@
 
-\subsection{Chase - v1}
-\subsubsection{Description}
-In this domain an agent has to chase an adversary.
-The goal is defined by the agent being in a target adjacent cell.
-The set of possile actions for the agent and the adversary is ~\{$up$, $down$, $left$, $right\}$.
-The agent can move twice per turn and the adversary can move once per turn.
-
-\subsubsection{Training instances}
-\begin{Verbatim}[fontsize=\footnotesize]
-#A.....#
-#......#
-#......#
-#.....T#
-\end{Verbatim}
-
-\subsubsection{Features}
-\begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
-  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
-  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
-  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
-\end{Verbatim}
-
-\subsubsection{Feature Descrition}
-$A$. The column of the agent is adjacent to the column of the adversary\\
-$B$. The row of the agent is adjacent to the row of the adversary\\
-$C$. Absolute vertical distance between agent and adversary\\
-$D$. Absolute horizontal distance between agent and adversary
-
-\subsubsection{Policy}
-\begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND C>0 -> {A ·, C ↓, D ·}
-  2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
-  3. A=0 AND B=0 AND D>0 AND C=0 -> {B ·, C ·, D ↓}
-  4. B=0 AND D>0 AND C>0 -> {A ·, C ↓, D ·}
-  5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
-  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, C ↓, D ·}
-  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, C ↓, D ·}
-\end{Verbatim}
-
-\subsubsection{Policy Description}
-According to rule two, if the agent is in the opponent's adjacent row, it is good to reduce the distance between them without moving from the adjacent row.
-Rule six is the same as 2 but with the column.
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  ...... # ...... # ...... # .T.... # .T.... # .T.... # T..... # T..... # T..... #
-  .T.... # .T.... # .T.... # ...... # ....A. # ...A.. # ...A.. # ..A... # .A.... #
-  ...... # .....A # ....A. # ....A. # ...... # ...... # ...... # ...... # ...... #
-  .....A # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-\end{Verbatim}
-
-\subsection{Nim - v0}
+\subsection{Nim}
 \subsubsection{Description}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Atom[holding_pet] [k=1]
-  (B) Bool[And(cell-has-agent,Exists(adjacent_cell,cell-has-destination))] [k=5]
-  (C) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]
-  (D) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
+    (A) Bool[holding-pet] [k=1]
+    (B) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]
+    (C) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
 \end{Verbatim}
@@
 $A$. The agent is holding the pet\\
-$B$. The destination is adjacent to the agent\\
-$C$. Manhattan distance between agent and destination\\
-$D$. Manhattan distance between agent and pet
+$B$. Manhattan distance between agent and destination\\
+$C$. Manhattan distance between agent and pet
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ·}
-  2. A=0 AND B=0 AND C>0 AND D>0 -> {A ·, B ·, C ↓, D ↓},
-                                    {A ·, B ·, C ↑, D ↓},
-                                    {A ↑, B ·, C ·, D ↑},
-                                    {A ·, B ·, C ·, D ↓}
-  3. A>0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↓, D ·}
-  4. A=0 AND B>0 AND C>0 AND D>0 -> {A ·, B ↓, C ↑, D ↓}
+  1. A=0 AND C>0 -> {A ·, C ↓}, {A ↑}
+  1. A>0 AND B>0 -> {A ·, B ↓}
 \end{Verbatim}

### 2021-05-31 experiments/delivery.py

@@ -13,23 +13,23 @@ chase_params = Bunch({
     'domain_name': 'delivery',
     'use_player_as_feature': False,
     'use_player_to_encode': False,
-    'use_next_player_as_feature': False,
-    'use_next_player_to_encode': False,
+    'use_next_player_as_feature': True,
+    'use_next_player_to_encode': True,
     'use_margin_as_feature': False,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
     'use_adjacency': {CELL_S},
     'use_bidirectional': {},
     'sorts_to_use': {CELL_S},
-    'unary_predicates': {HOLDING_PACKAGE},
+    'unary_predicates': {},
     'can_build_walls': False,
     'wumpus_active': False,
     'ava_actions': {
-        PLAYER1: {PICK, UP, DOWN, RIGHT, LEFT},
-        # PLAYER1: {PICK, RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, DROP},
+        # PLAYER1: {PICK, UP, DOWN, RIGHT, LEFT},
+        PLAYER1: {PICK, RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, UP, DOWN, RIGHT, LEFT},
         PLAYER2: {DROP_LEFT, DROP_RIGHT}},
         # PLAYER2: {DROP_UP, DROP_DOWN, DROP_LEFT, DROP_RIGHT, DROP_LEFTDOWN, DROP_RIGHTDOWN, DROP_RIGHTUP, DROP_LEFTUP}},
-    'max_actions': {PLAYER1: 2,
+    'max_actions': {PLAYER1: 1000,
                     PLAYER2: 1},
 })
 
@@ -87,14 +87,12 @@ def experiments():
     exps = dict()
     exps["1"] = update_dict(
         base,
-        instances=[1],
-        # test_instances=[],
+        instances=[0, 1],
         test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9],
         max_concept_size=5,
-        allow_bad_states=True,
+        allow_bad_states=False,
     )
 
     return exps
-
 
 

### 2021-05-31 src/gpl/domains/grid_games/domain.py

@@ -98,6 +98,13 @@ def load_general_problem(problem, lang, rep, env):
                 if o not in {OBJECTS.empty}:
                     problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
 
+    DESTINY="destiny"
+    if DESTINY not in brd:
+        r, c = np.argwhere(brd==AGENT)[0]
+        sort = CELL_S
+        o=DESTINY
+        problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
+
     def __add_direction_predicate(problem, lang, direction, sort, const, new_r, new_c):
         if (new_r<0 or new_c<0 or ncols==new_c or nrows==new_r) and not params.use_margin_as_feature:
             return

### 2021-05-31 src/gpl/domains/grid_games/grammar/language.py

@@ -1,3 +1,5 @@
+
+
 CELL_S = 'cell'
 ROW_S = 'row'
 COL_S = 'col'

### 2021-05-31 src/gpl/domains/grid_games/grammar/state_to_atoms.py

@@ -1,7 +1,9 @@
 import copy
 
+import numpy as np
+
 from .language import *
-from .objects import OBJECTS
+from .objects import OBJECTS, DESTINY, AGENT
 
 # General State to atoms
 def state_to_atoms(domain_name, state, p):
@@ -20,6 +22,12 @@ def state_to_atoms(domain_name, state, p):
                     continue
                 if o not in {OBJECTS.empty}:
                     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
+
+    if DESTINY not in brd:
+        r, c = np.argwhere(brd==AGENT)[0]
+        sort = CELL_S
+        o=DESTINY
+        atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
 
     for u in p.unary_predicates:
         if getattr(rep, u):

### 2021-05-31 src/gpl/domains/grid_games/task.py

@@ -87,6 +87,7 @@ class Task(ITask):
                         else:
                             if s2[1] not in vistited_s2:
                                 queue.append(s2)
+
         # succs_reps.append(r0)
         # for _, sp, spp in succs:
         #     succs_reps.append(sp[0])

### 2021-05-31 doc/paper/paper.tex
updated doc

@@
 
+In all domains we managed to solve with the shown policies any instance of the problem class, of any size.
+The policies have been found by learning unsupervised form from the tranining instances shown in the domains.
+
+Layouts have been created to show the problems and examples of game traces. The objects that can be found in the layouts are equivalent to:
+\begin{Verbatim}[fontsize=\footnotesize]
+  A: Agent
+  D: destination
+  T: adversary
+  K: white-king
+  Q: white-queen
+  R: white-rook
+  k: black-king
+  m: martian
+  p: pet
+  t: token
+\end{Verbatim}
+
 \subsection{Space Invaders}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  # m  .  .  m #
-  # m  .  .  m #
+  # m  m  .  m #
+  # m  m  .  m #
+  # .  .  .  . #
   # .  .  .  . #
@@
 \subsubsection{Description}
-In this domain an agent $A$ has to chase an adversary $T$.
+In this domain an agent has to chase an adversary.
 The goal is defined by the agent being in a adversary's adjacent cell.
-The set of possile actions for the agent and the adversary is ~\{$up$, $right$, $down$, $left\}$.
-The agent can move only diagonally and the adversary can move in perpendicular directions.
+The set of possile actions for the adversary is ~\{$up$, $right$, $down$, $left\}$.
+The set of possile actions for the agent is ~\{$rightup$, $rightdown$, $leftup$, $leftdown\}$.
 The agent and the adversary can move only once per turn.
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-#A.....#
-#......#
-#......#
-#.....T#
+#. . . . . .#
+#. A . . . .#
+#. . . . . .#
+#. . . . T .#
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
-  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
-  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
-  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
+  (A) Dist[col-has-agent;adjacent_col;col-has-adversary] [k=4]
+  (B) Dist[row-has-agent;adjacent_row;row-has-adversary] [k=4]
 \end{Verbatim}
@@
 \subsubsection{Feature Descrition}
-$A$. The column of the agent is adjacent to the column of the adversary\\
-$B$. The row of the agent is adjacent to the row of the adversary\\
-$C$. Absolute vertical distance between agent and adversary\\
-$D$. Absolute horizontal distance between agent and adversary
+$A$. Absolute vertical distance between the agent and the adversary\\
+$B$. Absolute horizontal distance between the agent and the adversary
 \subsubsection{Policy}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND B=0 AND D>0 AND C=0 -> {B ↑, C ↑, D ↓}
-  2. A=0 AND B=0 AND D>0 AND C>0 -> {C ↓, D ↓}
-  3. A=0 AND B>0 AND D>0 AND C>0 -> {B ↓, C ↓, D ↓}
-  4. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, C ↓, D ↓}
-  5. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, C ↓, D ↑}
+  1. A>0 AND B>0 -> {A ↓, B ↓}
+  2. A=0 AND B>0 -> {A ↑, B ↓}
+  3. A>0 AND B=0 -> {A ↓, B ↑}
 \end{Verbatim}
@@
 \subsubsection{Policy Description}
-According to rule three, if the agent is in the row adjacent to the adversary, it is good to stand in the same row as him.
-Following the rule four if the agent is in the column adjacent to the opponent it is good to go into the same column.
+According to rule one, is good to decrease the horizontal and vertical distance from the angent to the adversary if possible, i.e.
+move in diagonal towards him.
+Following the rule two if the agent is in the column of the adversary it is good to decrease the vertical distance.
+Finally, following the rule three if the agent is in the row of the adversary it is good to decrease the horizonal distance.
 
@@
 When one token is removed, the tokens above in the same column are removed too.
+It is interesting to note that in this game not all states are solvable if the opponent plays optimally.
+Knowing that the expert policy is to leave the opponent with both stacks with the same number of tokens, this state with both stacks leveled will not be solvable.
+Therefore, in order to solve it, we have made use of the $Bad(state)$ feature, which allows us not to have to define a good transition for each state, and as an alternative to label it as a bad state.
+The advantage is that if the initial state is solvable, bad states can always be avoided.
+However the policy is not complete for all states, in particular there will be no good transition for states with the two token stacks leveled, as we will see below, which we can say is the optimal representation of the game strategy.
 
-\subsubsection{Training instances:}
+\subsubsection{Training instances}
 \begin{Verbatim}[fontsize=\footnotesize]
+  # .  . #
   # t  . #
   # t  . #
-  # t  t #
   # t  t #
@@
 $B$. Number of tokens with a token immediately to the leftdown of it\\
-$C$. Number of tokens with a token immediately to the rightdown of it\\
+$C$. Number of tokens with a token immediately to the rightdown of it
 
@@
 This is done by decreasing the number of tokens that have a token to their leftdown or rightdown without decreasing the number of tokens with a token next to them.
+As the policy clearly shows, there is no good transition, that includes a change in the number of tokens that a token has on its left.
+In other words, states where the same number of tokens in the two stacks cannot be preserved with some legal move are bad, and therefore they have no good transition.
+In fact according to the policy it is good to leave the opponent in these states bad, because there will be no legal move for the opponent to leave us with the same number of tokens in the two stacks.
 
@@
 
-\subsection{Delivery - v0}
+\subsection{Delivery}
 \subsubsection{Description}
 
-In this domain the agent has to pick up a missed pet $p$ and take it to a certain location, the destination $D$.
-The pet has the option on its turn to escape from its captor to any of the cells adjacent to it.
-The goal is defined by the agent in a cell adjacent to the destination while carrying the pet.
-The agent has two actions per turn and the adversary one.
-The set of possile actions for the agent is ~\{$pick$, $rightup$, $rightdown$, $leftdown$, $leftup\}$.
-The agent to pick up the pet has to execute the $pick$ action or move to the same cell where the pet is located.
-The set of possile actions for the pet consist in escape to one of the adjacent cells to the agent, i.e.
-at most eight possible actions depending on the position of the agent in the grid.
-The pet can not escape to the delivey point.
+In this domain the agent has to pick up a missed pet and take it to a certain location, the destination.
+The pet has the option on its turn to escape from its captor to any of the cells adjacent to the pet, even if is holded by the agent it can escape.
+The goal is defined by the pet being droped at the destination cell, not holded by the agent.
+The agent has two actions per turn and the adversary one, otherwise the game would not be solvable for all the states.
+The set of possile actions for the agent is ~\{$pick$, $drop$, $right$, $up$, $down$, $left\}$.
+The agent, in order to pick up or drop the pet has to execute the actions $pick$ or $drop$ respectively being at the pet's cell.
+The set of possile actions for the pet consist in escape to one of the adjacent cells to it, i.e.
+at most eight possible actions depending on the position of the pet in the grid.
+The pet can not move into the delivery point.
 
-\subsubsection{Training instances:}
+\subsubsection{Training instances}
 \begin{Verbatim}[fontsize=\footnotesize]
-  # D  .  .  .  .  A #
+  # .  .  .  .  .  A #
+  # .  D  .  .  .  . #
   # .  .  .  .  .  . #
   # .  .  .  .  .  . #
+  # .  .  p  .  .  . #
   # .  .  .  .  .  . #
-  # .  .  .  .  .  . #
-  # .  .  .  .  .  p #
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-    (A) Bool[holding-pet] [k=1]
-    (B) Dist[cell-has-agent;adjacent_cell;cell-has-destination] [k=4]
-    (C) Dist[cell-has-agent;adjacent_cell;cell-has-pet] [k=4]
+  (A) Atom[holding_pet] [k=1]
+  (B) Dist[cell-has-pet;adjacent_cell;cell-has-agent] [k=4]
+  (C) Dist[cell-has-destiny;adjacent_cell;cell-has-agent] [k=4
 \end{Verbatim}
@@
 \subsubsection{Feature Descrition}
-$A$. The agent is holding the pet\\
-$B$. Manhattan distance between agent and destination\\
-$C$. Manhattan distance between agent and pet
+$A$. The agent is holding a pet
+$B$. Manhattan distance between the agent and the pet\\
+$C$. Manhattan distance between the agent and the destination
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A=0 AND C>0 -> {A ·, C ↓}, {A ↑}
-  1. A>0 AND B>0 -> {A ·, B ↓}
+  1. A=0 AND B>0 -> {B ↓}
+  2. A>0 AND C>0 -> {C ↓}
+  3. A>0 AND C=0 -> {A ↓}
+  4. A=0 AND B>0 -> {A ↑, B ↓}
 \end{Verbatim}
@@
 \subsubsection{Policy Description}
-According to the third rule, if the agent has the pet, it is good to move towards the destination.
-According to the fourth rule of the policy, if the agent does not have the pet, it is good to increase the distance to the destination and decrease the distance to the pet.
-Finally, according to the second rule, it is good to take the pet if you have the possibility, and if not, it is good to decrease the distance between the agent and the pet.
+According to the first rule, it is good to move towards the pet if the agent is not holding it and the distance to it is greater than zero.
+According to the second rule, if the agent has the pet, and is at the destination, it is good to move towards the destination.
+According to the third rule of the policy, if the agent is holding the pet, and is at destination it is good to drop the pet.
+Finally, according to the fourth rule of the policy, if the agent does not have the pet, and is at the same cell it is good to pick it.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-p.... # p.... # p.... # p.... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
-..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... #
-..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... #
-..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. #
-A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D #
+p.... # p.... # p.... # p.... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
+..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #
+..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... #
+..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..... # ..... #
+A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....A # ....A #
 \end{Verbatim}
@@
 The agent can execute the action $shoot$, but the opponent does not, so the opponent is able to win the game from any state of any instance if he knows the right strategy.
-The agent and the adversary share the set of actions ~{$up$, $right$, $down$, $left\}$.
+The agent and the adversary share the set of actions ~\{$up$, $right$, $down$, $left\}$.
 To reach the goal state, the agent has to be in the same row or column as the adverary and execute the action $shoot$.
@@
 We can define the goal state, as the adversary not being on the board.
-The agent and the opponent have two actions per turn, so that the agent can stand in the opponent's row or column and shoot before the opponent escapes.
+The agent have one actions per turn and the adversary two, so that the agent can stand in the opponent's row or column and shoot before the opponent escapes.
 
-\subsubsection{Training instances:}
+\subsubsection{Training instances}
 \begin{Verbatim}[fontsize=\footnotesize]
+  # . . . . #
   # A . . . #
+  # . . T . #
   # . . . . #
-  # . . . . #
-  # . . . T #
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  A....... # .A...... # ..A..... # ..A..... # ...A.... # ....A... # ....A... # .....A.. # ......A. # ......A. # .....A.. # .....A.. #
-  ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
-  ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
-  ........ # ........ # ........ # .....T.. # .....T.. # .....T.. # ......T. # ......T. # ......T. # .....T.. # .....T.. # ........ #
-  .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
+  A....... # .A...... # ..A..... # ..A..... # ...A.... # ....A... # ....A... # .....A.. # ......A. #
+  ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
+  ........ # ........ # ........ # ........ # ........ # ........ # .....T.. # ......T. # ......T. #
+  ........ # ........ # ........ # .....T.. # .....T.. # .....T.. # ........ # ........ # ........ #
+  .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ........ # ........ # ........ # ...
+
+     # ......A. # .....A.. # .....A.. #
+     # ........ # ........ # ........ #
+     # .....T.. # .....T.. # ........ #
+     # ........ # ........ # ........ #
+  ...# ........ # ........ # ........ #
 
@@
 
-\subsection{Checkmate - v0}
+\subsection{Checkmate whith Queen}
 \subsubsection{Description}
 In this game the action space is equal to the number of cells in the grid.
-In order to win the agent has to do a checkmate in one movement.
-Otherwise he loses.
-In $Checkmate-v0$ white pieces have the king $K$ and the queen $Q$, and black pieces have the king $k$.
+In order to win the white pieces has to do a checkmate in one movement.
+The white pieces have the white-king and the white-queen, and black pieces have the black-king.
 
-\subsubsection{Training instances:}
+\subsubsection{Training instances}
 \begin{Verbatim}[fontsize=\footnotesize]
@@
 
+\subsubsection{Feature Description}
+$A$. The black-king and the white-king are in the same column\\
+$B$. The black-king and the white-queen are in the same column\\
+$C$. The black-king and the white-king are in the same row\\
+$D$. The black-king and the white-king are in the same row\\
+$E$. The black-king's cell and the white-queen's cell are adjacent\\
+$F$. The white-king's column and the white-queen's column are adjacent\\
+$G$. The black-king's column and the white-king's column are adjacent
+
 \subsubsection{Policy}
@@
                                                             {A ·, B ↑, C ·, D ·, E ·, F ·, G ·}
-  4. A=0 AND B=0 AND C=0 AND D=0 AND E=0 AND F=0 AND G=0 -> {A ·, B ↑, C ·, D ·, E ↑, F ↑, G ·},
-                                                            {A ·, B ·, C ·, D ·, E ↑, F ↑, G ·}
+  4. A=0 AND B=0 AND C=0 AND D=0 AND E=0 AND F=0 AND G=0 -> {A ·, C ·, D ·, E ↑, F ↑, G ·}
   5. A>0 AND B=0 AND C=0 AND D=0 AND E=0 AND F>0 AND G=0 -> {A ·, B ↑, C ·, D ·, E ↑, F ↓, G ·},
@@
   6. A=0 AND B=0 AND C>0 AND D>0 AND E=0 AND F>0 AND G=0 -> {A ·, B ↑, C ·, D ↓, E ·, F ↓, G ·}
-  7. A=0 AND B=0 AND C=0 AND D=0 AND E=0 AND F>0 AND G=0 -> {A ·, B ↑, C ·, D ·, E ↑, F ·, G ·},
-                                                            {A ·, B ·, C ·, D ·, E ↑, F ·, G ·}
+  7. A=0 AND B=0 AND C=0 AND D=0 AND E=0 AND F>0 AND G=0 -> {A ·, C ·, D ·, E ↑, F ·, G ·}
   8. A=0 AND B=0 AND C>0 AND D>0 AND E=0 AND F=0 AND G=0 -> {A ·, B ↑, C ·, D ↓, E ·, F ·, G ·}
@@
 \end{Verbatim}
+
+\subsubsection{Policy description}
+The policy is an abstraction of all the possible one-move checkmates that exist on a chessboard of any size with two kings and a queen.
+For example rule one tells us that if the white king is on the same column as the black king, it is good to put the white queen on the same row as the black king, avoiding squares where the white queen would be in a cell adjacent to the black king.
+Following on from the first rule, transitions where the white queen is placed on the same column as the black king, and in a cell adjacent to the black king, would also be good, i.e.
+it is good for the white queen to be placed between the white and black kings.
+This policy will generalise to any chessboard size board.
 
@@
 In this game the action space is equal to the number of cells in the grid.
-In order to win the agent has to do a checkmate in one movement.
-Otherwise he loses.
-In $Checkmate-v1$ white pieces have the king and the rook $R$, and black pieces have the king.
+In order to win the white pieces has to do a checkmate in one movement.
+In white pieces have the white-king and the white-rook, and black pieces have the black-king.
 
-\subsubsection{Training instances:}
+\subsubsection{Training instances}
 \begin{Verbatim}[fontsize=\footnotesize]
@@
   (C) Bool[And(row-has-black_king,row-has-white_rook)] [k=3]
+\end{Verbatim}
 
-\end{Verbatim}
+\subsubsection{Feature Description}
+$A$. The black-king and the white-king are in the same column\\
+$B$. The black-king and the white-rook are in the same column\\
+$C$. The black-king and the white-rook are in the same row
 
@@
 \end{Verbatim}
+
+\subsubsection{Policy description}
+The policy is an abstraction of all the possible one-move checkmates that exist on a chessboard of any size with two kings and a tower.
+According to rule one, if the black king is in the same column as the white king, it is good to put the white rook in the same row as the white king.
+According to the second rule if the black king is not on the same column as the white king, it is good to put the white rook on the same column as the white king.
+This policy will generalise to any chessboard size board where checkmate is possible in one with rook and king.
 

### 2021-05-31 experiments/chase.py

@@ -10,11 +10,15 @@ from gpl.domains.grid_games.grammar.objects import PLAYER1, PLAYER2
 chase_params = Bunch({
     'domain_name': 'chase',
     'use_player_as_feature': False,
+    'use_player_to_encode': False,
+    'use_next_player_as_feature': False,
+    'use_next_player_to_encode': False,
+    'use_margin_as_feature': False,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
-    'use_adjacency': {COL_S, ROW_S},
+    'use_adjacency': {COL_S, ROW_S, CELL_S},
     'use_bidirectional': {},
-    'sorts_to_use': {COL_S, ROW_S},
+    'sorts_to_use': {COL_S, ROW_S, CELL_S},
     'unary_predicates': {},
     'can_build_walls': False,
     'ava_actions': {
@@ -56,7 +60,7 @@ def experiments():
         allow_cycles=False,
         use_action_ids=False,
         use_weighted_tx=True,
-        distinguish_goals=True,
+        distinguish_goals=False,
 
         sampling_strategy="full",
 

### 2021-05-31 experiments/delivery.py

@@ -5,31 +5,31 @@ from gpl.domains.grid_games.domain import Domain
 from gpl.utils import Bunch
 from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
 from gpl.domains.grid_games.envs.delivery import \
-    RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, UP, DOWN, RIGHT, LEFT, HOLDING_PACKAGE, PICK, DROP, \
+    RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, UP, DOWN, RIGHT, LEFT, HOLDING_PACKAGE, AT_DESTINATION, PICK, DROP, \
     DROP_RIGHT, DROP_LEFT, DROP_DOWN, DROP_UP, DROP_LEFTDOWN, DROP_RIGHTDOWN, DROP_RIGHTUP, DROP_LEFTUP
 from gpl.domains.grid_games.grammar.objects import PLAYER1, PLAYER2
 
 chase_params = Bunch({
     'domain_name': 'delivery',
     'use_player_as_feature': False,
-    'use_player_to_encode': False,
-    'use_next_player_as_feature': True,
-    'use_next_player_to_encode': True,
+    'use_player_to_encode': True,
+    'use_next_player_as_feature': False,
+    'use_next_player_to_encode': False,
     'use_margin_as_feature': False,
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
     'use_adjacency': {CELL_S},
     'use_bidirectional': {},
     'sorts_to_use': {CELL_S},
-    'unary_predicates': {},
+    'unary_predicates': {HOLDING_PACKAGE, AT_DESTINATION},
     'can_build_walls': False,
     'wumpus_active': False,
     'ava_actions': {
         # PLAYER1: {PICK, UP, DOWN, RIGHT, LEFT},
-        PLAYER1: {PICK, RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, UP, DOWN, RIGHT, LEFT},
+        PLAYER1: {PICK, DROP, UP, DOWN, RIGHT, LEFT, RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP},
         PLAYER2: {DROP_LEFT, DROP_RIGHT}},
[…]

### 2021-05-31 src/gpl/domains/grid_games/domain.py

@@ -98,12 +98,17 @@ def load_general_problem(problem, lang, rep, env):
                 if o not in {OBJECTS.empty}:
                     problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
 
-    DESTINY="destiny"
-    if DESTINY not in brd:
-        r, c = np.argwhere(brd==AGENT)[0]
-        sort = CELL_S
-        o=DESTINY
-        problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
+    # from .envs.delivery import AT_DESTINATION, HOLDING_PACKAGE, DESTINY, PACKAGE
+    # if getattr(rep, AT_DESTINATION):
+    #     r, c = np.argwhere(brd==AGENT)[0]
+    #     sort = CELL_S
+    #     o=DESTINY
+    #     problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
+    # if not PACKAGE in rep.grid:
+    #     r, c = np.argwhere(brd==AGENT)[0]
+    #     sort = CELL_S
+    #     o=PACKAGE
+    #     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
 
     def __add_direction_predicate(problem, lang, direction, sort, const, new_r, new_c):
         if (new_r<0 or new_c<0 or ncols==new_c or nrows==new_r) and not params.use_margin_as_feature:

### 2021-05-31 src/gpl/domains/grid_games/envs/delivery.py

@@ -72,8 +72,12 @@ ACTION_DROP_DIRECTION = {
     DROP_LEFTDOWN: ACTION_MOVE_DIRECTION[LEFTDOWN],
 }
 
+PACKAGES_QUEUE = 'packages_queue'
 # unary predicates
 HOLDING_PACKAGE = 'holding_pet'
+AT_DESTINATION = 'at_destination'
+ALL_PETS_DELIVERED = 'all_pets_delivered'
+
 
 # Begin Wumpus =================================
 
@@ -85,12 +89,12 @@ class Env(object):
         layout = rep.grid
         assert rep.nact < self.params.max_actions[rep.player] + 1
         valid_actions = self.available_actions(rep)
-        assert action in valid_actions
+        # assert action in valid_actions
         l = layout.copy()
         if rep.player == PLAYER1:
-            l = layout_after_agent_action(layout, action, self.params)
+            l, holding, at_dest = layout_after_agent_action(rep, action, self.params)
         else:
-            l = layout_after_wumpus_action(layout, action, self.params)
+            l, holding, at_dest = layout_after_wumpus_action(rep, action, self.params)
         new_rep = copy.deepcopy(rep)
         new_rep.grid = l
         if rep.nact < self.params.max_actions[rep.player]:
@@ -100,7 +104,8 @@ class Env(object):
             new_rep.player = opposite_player(rep.player)
         if self.params.use_next_player_as_feature:
             new_rep.next_player = identify_next_player(new_rep, self.params)
-        setattr(new_rep, HOLDING_PACKAGE, holding_package(new_rep.grid))
+        setattr(new_rep, HOLDING_PACKAGE, holding)
+        setattr(new_rep, AT_DESTINATION, at_dest)
         return self.__update_rep(new_rep)
 
     def __update_rep(self, rep):
@@ -119,10 +124,7 @@ class Env(object):
 
     def check_game_status(self, rep):
         if terminated(rep, self.params):
-            if holding_package(rep.grid):
-                return 1
-            else:
-                return -1
+            return 1
         else:
             return 0
 
@@ -131,13 +133,15 @@ class Env(object):
         actions = []
         if rep.player == PLAYER1:
             c0 = np.argwhere(layout == AGENT)[0]
-            actions += PLAYER_VALID_ACTIONS[PLAYER1](c0, layout, self.params)
[…]

### 2021-05-31 src/gpl/domains/grid_games/task.py

@@ -124,37 +124,39 @@ class Task(ITask):
             print(tmp_str)
         print("#" * ncols)
 
-    def print_path(self, reps):
+    def print_path(self, reps_, divide=15):
         simplified_objects = self.env.get_simplified_objects()
-        nrows, ncols = reps[0].grid.shape
-        total_path_rep = ""
-        for row in range(nrows):
-            tmp_full_row = ""
-            for rep in reps:
-                layout = rep.grid
-                tmp_row = ""
-                for o in layout[row, :]:
-                    tmp_row += simplified_objects[o]
-                tmp_full_row += "{} # ".format(tmp_row)
-            total_path_rep += "{}\n".format(tmp_full_row)
-
-        single_rep_row = ""
-        for o in layout[0, :]:
-            single_rep_row += simplified_objects[o]
-        size_single_row = len("{} # ".format(single_rep_row))
-
-        info_to_print = ["player", "nmoves", "last_turn", "next_player", "holding_pet", "goal"]
-        for info in info_to_print:
-            try:
+        nrows, ncols = reps_[0].grid.shape
+        while reps_:
+            reps, reps_ = reps_[:divide], reps_[divide:]
+            total_path_rep = ""
+            for row in range(nrows):
                 tmp_full_row = ""
                 for rep in reps:
-                    att = getattr(rep, info)
-                    tmp_full_row += "{} ({})".format(int(att), info[:2]).ljust(size_single_row)
+                    layout = rep.grid
+                    tmp_row = ""
+                    for o in layout[row, :]:
+                        tmp_row += simplified_objects[o]
+                    tmp_full_row += "{} # ".format(tmp_row)
                 total_path_rep += "{}\n".format(tmp_full_row)
-            except:
-                pass
 
-        print(total_path_rep)
+            single_rep_row = ""
+            for o in layout[0, :]:
+                single_rep_row += simplified_objects[o]
+            size_single_row = len("{} # ".format(single_rep_row))
+
+            info_to_print = ["player", "nmoves", "last_turn", "next_player", "holding_pet", "at_destination", "goal"]
+            for info in info_to_print:
+                try:
+                    tmp_full_row = ""
+                    for rep in reps:
+                        att = getattr(rep, info)
+                        tmp_full_row += "{}({})".format(int(att), info[:2]).ljust(size_single_row)
+                    total_path_rep += "{}\n".format(tmp_full_row)
+                except:
+                    pass
+
[…]

### 2021-05-31 doc/paper/paper.tex
doc update

@@
 
+The sections broken down into each domain are: Description of the domain, the training instances used to discover the policy, the learned features, description of the features, learned policy, description of the policy, and finally an example of a possible game, from initial state to goal, using the discovered policy in a test instance against an expert adversary.
+The initial state of the example test instance is taken from the infinite set of possible instances in the domain.
+
 Layouts have been created to show the problems and examples of game traces. The objects that can be found in the layouts are equivalent to:
@@
 .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
@@
 t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
+t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
 t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-p.... # p.... # p.... # p.... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
+p.... # p.... # .p... # .p... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
 ..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #

### 2021-05-31 doc/paper/paper.tex
grammar added to doc

@@
 
+\section{Grammar}
+
+The sorts used are: $cell$, $row$, $column$ and .
+The constants for the sort $cell$ have the form $cell.r\_c$, this constant refers to the cell that is at the same time in the row $r$ and in the column $c$.
+The constants for sort $row$ are $row.r$, and this constant refers to the row $r$.
+The constants for sort $column$ are $column.c$, and this constant refers to column $c$.
+Each sort can be linked to an object, using a one-arity predicate, depending on the objects of the domain, given by a predicate of arity one with any variable belonging to the sorts $cell$, $row$ or $column$.
+An example for the sort $cell$ would be $cell\_has\_v(cell)$, where the variable of type $cell$ can take the value of $cell.r\_c$, and this predicate would indicate that the cell $cell.r\_c$ has an object with value $v$, which is the name of the object currently in $cell.r\_c$.
+To map the relative position between constants of the same sort, we use two-arity predicates, which have as variables these constants belonging to the same sort.
+For example, $adjacent\_cell(cell, cell)$ takes two constants of the sort $cell$, and means that the two cells are adjacent.
+The same philosophy would apply to the predicates $adjacent\_col(column, column)$ or $adjacent\_row(row, row)$.
+
+\newpage
+
 \section{Empirical Results}
@@
 The agent has two actions per turn and the adversary one, otherwise the game would not be solvable for all the states.
-The set of possile actions for the agent is ~\{$pick$, $drop$, $right$, $up$, $down$, $left\}$.
+The set of possile actions for the agent is ~\{$pick$, $drop$, $rightup$, $reightdown$, $leftup$, $leftdown\}$.
 The agent, in order to pick up or drop the pet has to execute the actions $pick$ or $drop$ respectively being at the pet's cell.
@@
 
-\subsection{Checkmate - v1}
+\subsection{Checkmate with Rook}
 \subsubsection{Description}
@@
 \item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
-\item Empirical results with five domains: Chase, Shoot, Space Invaders, Delivery, Wumpus world.
+\item Empirical results with six different domains: Chase, Shoot, Space Invaders, Delivery, Checkmate with Queen, Checkmate with Rook.
 \item Incremental policy learning, to address the scalability problem.

### 2021-05-31 doc/paper/paper.tex
minor changes

@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  m..m # m..m # m..m # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
-  M..m # M..m # M..m # m..m # M..m # ...m # ..m. # ..m. # ..m. # ...m # ...m # ...M # ..M. # ..M. # .... #
-  .... # .... # .... # M..m # ...m # ...M # ..M. # ..M. # ..M. # ...M # ...M # .... # .... # .... # .... #
-  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
-  ..A. # .A.. # A... # A... # A... # A... # A... # .A.. # ..A. # ..A. # ...A # ...A # ...A # ..A. # ..A. #
+    # m.mm.m # m.mm.m # m.mm.m # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # m.mm.m # m.mm.m # m.mm.. # m.mm.m # m.mm.. # m.mm.. # .m.mm. # .m.mm. # .m.mm. # ..m.mm #
+    # m.mm.m # m.mm.. # m.mm.. # m.mm.. # m.mm.. # m.mm.. # .m.mm. # .m.mm. # .m.m.. # ..m.m. #
+    # ...... # ...... # ...... # m.mm.. # m.mm.. # m.mm.. # .m.mm. # .m.m.. # .m.m.. # ..m.m. #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # .....A # .....A # .....A # .....A # .....A # ....A. # ....A. # ....A. # ....A. # ....A. # ...
+
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ..m.mm # ..m.mm # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ..m.m. # ..m... # ..m.mm # ..m..m # ..m..m # ...... # ...... # ...... # ...... # ...... #
+    # ..m... # ..m... # ..m... # ..m... # ..m... # ..m..m # ..m... # ..m... # ...m.. # ...m.. #
+    # ...... # ...... # ..m... # ..m... # ..m... # ..m... # ..m... # ..m... # ...m.. # ...m.. #
+    # ...... # ...... # ...... # ...... # ...... # ..m... # ..m... # ..m... # ...m.. # ...m.. #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+... # ....A. # ....A. # ....A. # ....A. # .....A # .....A # .....A # ....A. # ....A. # ...A.. # ...
+
+    # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+    # ...m.. # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+    # ...m.. # ...m.. # ...m.. # ...... #
+    # ...... # ...m.. # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+... # ...A.. # ...A.. # ...A.. # ...A.. #
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  A..... # ...... # ...... # ...... # ...... # ...... # .....T # ....AT #
-  ...... # .A.... # .A.... # ...... # .....T # ...A.T # ...A.. # ...... #
-  ...... # ...... # .....T # ..A..T # ..A... # ...... # ...... # ...... #
-  .....T # .....T # ...... # ...... # ...... # ...... # ...... # ...... #
+ # A..... # ...... # ...... # ...... # ...... # ...... # .....T # ....AT #
+ # ...... # .A.... # .A.... # ...... # .....T # ...A.T # ...A.. # ...... #
+ # .....T # .....T # ...... # ...... # ...... # ...... # ...... # ...... #
+ # ...... # ...... # .....T # ..A..T # ..A... # ...... # ...... # ...... #
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
-.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
-.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
-t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
-t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
-t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
-t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
-t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
-t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
-t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
-t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
-t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
-t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+ # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
 \end{Verbatim}
@@
   (B) Dist[cell-has-pet;adjacent_cell;cell-has-agent] [k=4]
-  (C) Dist[cell-has-destiny;adjacent_cell;cell-has-agent] [k=4
+  (C) Dist[cell-has-destiny;adjacent_cell;cell-has-agent] [k=4]
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-p.... # p.... # .p... # .p... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
-..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #
-..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... #
-..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..... # ..... #
-A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....A # ....A #
+ # p.... # p.... # .p... # .p... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
+ # ..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... #
+ # ..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #
+ # ..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..... # ..... #
+ # A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....A # ....A #
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  K  .  .  #  .  .  .  .  .  .  .  K  .  .  #
-  .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  Q  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  K  .  .  #  .  .  .  .  .  .  .  K  .  .  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  Q  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  K  .  k  #  .  .  .  .  .  .  .  K  .  k  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  .  .  R  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  R  #
-  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  K  .  k  #  .  .  .  .  .  .  .  K  .  k  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  R  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  R  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
 \end{Verbatim}

### 2021-05-31 experiments/space_invaders.py

@@ -13,7 +13,9 @@ from gpl.domains.grid_games.domain import Domain
 space_invaders_params = Bunch({
     'domain_name': 'space_invaders',
     'use_player_as_feature': False,
+    'use_player_to_encode': False,
     'use_next_player_as_feature': False,
+    'use_next_player_to_encode': False,
     'use_margin_as_feature': False,
     'use_target_margin': False,
     'map_cells': True,
@@ -94,7 +96,7 @@ def experiments():
         base,
         domain=Domain(space_invaders_params_v1),
         instances=[0, 17, 18],
-        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 17, 18, 19],
+        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 17, 18, 19, 20],
         allow_bad_states=False,
     )
 

### 2021-05-31 src/gpl/domains/grid_games/envs/space_invaders.py

@@ -339,4 +339,5 @@ LAYOUTS = {
     17: (5, 4, 2, [0, 1], 0, [0, 3]),
     18: (4, 5, 3, [0, 1], 0, [0, 4]),
     19: (8, 4, 2, [0,], 0, [0, 3]),
+    20: (10, 6, 5, list(range(3)), 0, [0, 2, 3, 5]),
 }

### 2021-05-31 src/gpl/domains/grid_games/task.py

@@ -124,7 +124,7 @@ class Task(ITask):
             print(tmp_str)
         print("#" * ncols)
 
-    def print_path(self, reps_, divide=15):
+    def print_path(self, reps_, divide=10):
         simplified_objects = self.env.get_simplified_objects()
         nrows, ncols = reps_[0].grid.shape
         while reps_:

### 2021-06-01 doc/paper/paper.tex
minor change in format
minor change
doc update

@@
 \subsubsection{Description}
+This domain is a simplified version of the original Space Invaders in which the Martians cannot shoot and cannot move below the penultimate row.
 In this domain the agent can $shoot$, move to the $right$ or to the $left$.
 The agent during his turn can do two actions, while the Martians can do one.
-Note that if the Martians and the agent have only one action per turn the agent cannot win, this is because of the situation where the agent stands in the Martian's column to shoot him on his next turn, but the next turn (the Martian's turn) the Martian can move away, this leads to an infinite loop if both are playing perfectly.
+Note that if the Martians and the agent have only one action per turn the agent cannot win from all possible states in the game, this is because of the situation where the agent stands in the Martian's column to shoot him on his next turn, but the next turn (the Martian's turn) the Martian can move away, this leads to an infinite loop if both are playing perfectly.
 That is, the agent must be able to move to the agent's column and then shoot.
@@
 The agent kills an opponent if he shoots while being in the same column, and he can only kill one for each shoot.
-The martians has three possible actions $left$, $right$, $up$ and $down$.
+The martians has three possible actions $left$, $right$, and $down$.
 All the adversaries move in the same direction.
@@
 According to the first rule if the agent is not in the column of a Martian, $B$ is greater than zero, it is good to decrement $B$, i.e.
-move towards the closest martian.
+move agent towards the closest column with martians.
 The second rule is applicable when the agent is under a Martian, in the same column, and according to this rule it is good to decrease the number of Martians, i.e.
@@
 \subsubsection{Description}
-In this game the action space is equal to the number of tokens $t$ in the grid.
-In order to win the agent has to remove the last token in his turn.
-If the opponet removes the last token in his turn, the agent loses.
+In this domain there are two stacks (columns) of tokens.
+The number of actions available in each state depends on the number of tokens, a valid action involves removing one of the tokens.
+When a token is removed, that token and all the tokens above it are removed as well.
+When a token is removed, the turn is changed and the other player must remove a token as an action if there is one.
+The objective of the game is to leave the opponent with no actions available on his turn, i.e., without any token.
 The agent and the adversary has on action per turn.
-When one token is removed, the tokens above in the same column are removed too.
 It is interesting to note that in this game not all states are solvable if the opponent plays optimally.
@@
 However the policy is not complete for all states, in particular there will be no good transition for states with the two token stacks leveled, as we will see below, which we can say is the optimal representation of the game strategy.
+The winning tactic in this game is to level the two stacks of tokens by removing the token next to an empty cell and diagonally above another token, como se puede ver en~\cite{silver2020few}.
+The intuition behind this tactic is that if we follow it we can always reach a final situation where the opponent is forced to remove all the tokens from one pile, then we can remove the remaining tokens from the other pile.
 
@@
   (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]
-  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]
-  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]
+  (B) Num[And(cell-has-token,Exists(leftdown_cell,cell-has-token))] [k=5]
+  (C) Num[And(cell-has-token,Exists(rightdown_cell,cell-has-token))] [k=5]
 \end{Verbatim}
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. B>0 AND C>0 -> {A ·, B ↓, C ↓}
+  1. B>0 AND C>0 -> {A ·, B ↓, C ·}, {A ·, B ·, C ↓}
 \end{Verbatim}
@@
 \subsubsection{Policy Description}
-The policy can be interpreted as leaving the two token stacks with the same number of tokens.
+The policy guarantees to leave both stacks with the same number of tokens.
 This is done by decreasing the number of tokens that have a token to their leftdown or rightdown without decreasing the number of tokens with a token next to them.
@@
 The goal is defined by the pet being droped at the destination cell, not holded by the agent.
+In this domain we use the additional predicate $holding_pet$ to indicate that the agent is holding the pet.
 The agent has two actions per turn and the adversary one, otherwise the game would not be solvable for all the states.
 The set of possile actions for the agent is ~\{$pick$, $drop$, $rightup$, $reightdown$, $leftup$, $leftdown\}$.
-The agent, in order to pick up or drop the pet has to execute the actions $pick$ or $drop$ respectively being at the pet's cell.
+The agent, in order to pick up the pet has to execute the action $pick$ adjacent to the the pet's cell.
+The agent, in order to drop the pet has to execute the action $drop$ while $holding_pet$, and the pet will be droped at de agent's cell.
 The set of possile actions for the pet consist in escape to one of the adjacent cells to it, i.e.
@@
 According to the third rule of the policy, if the agent is holding the pet, and is at destination it is good to drop the pet.
-Finally, according to the fourth rule of the policy, if the agent does not have the pet, and is at the same cell it is good to pick it.
+Finally, according to the fourth rule of the policy, if the agent does not have the pet, and is at the adjacent cell it is good pick it.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
- # p.... # p.... # .p... # .p... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
- # ..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... #
- # ..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #
- # ..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..... # ..... #
- # A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....A # ....A #
+  p.... # p.... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
+  ..... # .A... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
+  A.... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... # ..... # ..... # ..... #
+  ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..pA. # ...A. # ..... # ..... # ..... #
+  ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ...pA # ....A # ....A #
 \end{Verbatim}
@@
 In this domain an agent has to shoot an adversary.
-The goal is defined by the agent being alone on the grid, having finished with the opponent.
+The goal is defined by the agent being alone on the grid, having finished with the adversary.
 The agent can execute the action $shoot$, but the opponent does not, so the opponent is able to win the game from any state of any instance if he knows the right strategy.
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. A>0 AND B=0 AND C=0 AND D>0 -> {B ·, C ·, D ↓}
-  2. A>0 AND B=0 AND C>0 AND D>0 -> {B ↑, C ↓, D ·}
+  1. A>0 AND B=0 AND C=0 AND D>0 -> {A ·, B ·, C ·, D ↓}
+  2. A>0 AND B=0 AND C>0 AND D>0 -> {A ·, B ↑, C ↓, D ·}
   3. A>0 AND D=0 -> {A ↓}
@@
 Finally, according to the first rule, if the agent is not in the row adjacent to the adversary, and is not in the same row or column, it is good to decrease the horizontal distance between the agent and the adversary.
-The first rule can also be read as, it is good for the agent to approach the adversary horizontally if you do not have the possibility to stand, or you are already in a position where it is good to shoot.
+The first rule can also be read as, it is good for the agent to approach the adversary horizontally.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  A....... # .A...... # ..A..... # ..A..... # ...A.... # ....A... # ....A... # .....A.. # ......A. #
-  ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
-  ........ # ........ # ........ # ........ # ........ # ........ # .....T.. # ......T. # ......T. #
-  ........ # ........ # ........ # .....T.. # .....T.. # .....T.. # ........ # ........ # ........ #
-  .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ........ # ........ # ........ # ...
+  # A....... # .A...... # ..A..... # ..A..... # ...A.... # ....A... # ....A... # .....A.. # ......A. #
+  # ........ # ........ # ........ # ........ # ........ # ........ # .....T.. # ......T. # ......T. #
+  # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
+  # .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ........ # ........ # ........ #
+  # ........ # ........ # ........ # .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ...
 
@@
 
+\subsubsection{Task instance distribution}
+To generate all the possible states from which the queen can checkmate the black king in one, in a board of $NxM$, we follow the following procedure.
+We generate all the possible checkmates that can be given to the black king if it is in the first row, then we apply three rotations to each board, 90, 180 and 270 degrees.
+To generate the checkmate with the black king in the first row we must take into account that for each black king position in this row there are three possible positions of the white king that allow a checkmate in one.
+In all these possible positions of the two kings we place the king in all the squares where it can checkmate the black king, and eliminate those where it would be giving a check.
+For the training, one hundred random boards of five by fifty are selected.
+To check that the policy is complete, it is tested on all possible, for each board size $NxM$ where both $N$ and $M$ are numbers no greater than twenty randomly selected.
+
 \subsubsection{Example of Game}
@@
 # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
 # .  .  .  .  .  .  .  K  .  .  #  .  .  .  .  .  .  .  K  .  .  #
+# .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
 # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-   # .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
 # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
@@
 # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
 \end{Verbatim}
@@
 \subsubsection{Description}
-In this game the action space is equal to the number of cells in the grid.
+In this game the action space is equal to the number of cells in the board.
 In order to win the white pieces has to do a checkmate in one movement.
@@
 This policy will generalise to any chessboard size board where checkmate is possible in one with rook and king.
+
+\subsubsection{Task instance distribution}
+To generate all the possible states from which the rook can checkmate the black king in one, in a board of $NxM$, we follow the following procedure.
+We generate all the possible checkmates that can be given to the black king if it is in the first row, then we apply three rotations to each board, 90, 180 and 270 degrees.
+To generate the checkmate with the black king in the first row we must take into account that for each black king position in this row there are one possible position of the white king that allow a checkmate in one.
+In all these possible positions of the two kings we place the king in all the squares where it can checkmate the black king, and eliminate those where it would be giving a check.
+For the training, one hundred random boards of five by fifty are selected.
+To check that the policy is complete, it is tested on all possible, for each board size $NxM$ where both $N$ and $M$ are numbers no greater than twenty randomly selected.
 

### 2021-06-01 experiments/delivery.py

@@ -14,8 +14,9 @@ chase_params = Bunch({
     'use_player_as_feature': False,
     'use_player_to_encode': True,
     'use_next_player_as_feature': False,
-    'use_next_player_to_encode': False,
+    'use_next_player_to_encode': True,
     'use_margin_as_feature': False,
+    'objects_to_ignore': set(),
     'map_cells': True,
     'use_diagonals_for_map_cells': True,
     'use_adjacency': {CELL_S},

### 2021-06-01 src/gpl/domains/grid_games/domain.py

@@ -95,20 +95,34 @@ def load_general_problem(problem, lang, rep, env):
                     map_sorts[(r, c, sort)] = lang.constant(CONST[sort](r, c, nrows, ncols), lang.get(sort))
                 except:
                     map_sorts[(r, c, sort)] = lang.get(CONST[sort](r, c, nrows, ncols))
-                if o not in {OBJECTS.empty}:
+                if o not in {OBJECTS.empty} | params.objects_to_ignore:
                     problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
 
-    # from .envs.delivery import AT_DESTINATION, HOLDING_PACKAGE, DESTINY, PACKAGE
-    # if getattr(rep, AT_DESTINATION):
-    #     r, c = np.argwhere(brd==AGENT)[0]
+    # WUMPUS
+    # from .envs.wumpus import AT_WUMPUS, AT_PIT, AGENT, WUMPUS
+    # if AGENT not in brd and getattr(rep, AT_WUMPUS):
+    #     r, c = np.argwhere(brd == WUMPUS)[0]
     #     sort = CELL_S
-    #     o=DESTINY
+    #     o = AGENT
     #     problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
-    # if not PACKAGE in rep.grid:
-    #     r, c = np.argwhere(brd==AGENT)[0]
+    # if AGENT not in brd and getattr(rep, AT_PIT) is not None:
+    #     r, c = getattr(rep, AT_PIT)
     #     sort = CELL_S
-    #     o=PACKAGE
+    #     o = AGENT
     #     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
+
+    # DELIVERY
+    from .envs.delivery import AT_DESTINATION, HOLDING_PACKAGE, DESTINY, PACKAGE
+    if getattr(rep, AT_DESTINATION):
+        r, c = np.argwhere(brd==AGENT)[0]
+        sort = CELL_S
+        o=DESTINY
+        problem.init.add(lang.get(f'{sort}-has-{o}'), lang.get(CONST[sort](r, c, nrows, ncols)))
+    if not PACKAGE in rep.grid:
+        r, c = np.argwhere(brd==AGENT)[0]
+        sort = CELL_S
+        o=PACKAGE
[…]

### 2021-06-01 src/gpl/domains/grid_games/grammar/state_to_atoms.py

@@ -5,8 +5,6 @@ import numpy as np
 from .language import *
 from .objects import OBJECTS
 
-from ..envs.delivery import AT_DESTINATION, HOLDING_PACKAGE, DESTINY, PACKAGE, AGENT
-
 # General State to atoms
 def state_to_atoms(domain_name, state, p):
     rep, _ = state
@@ -22,19 +20,34 @@ def state_to_atoms(domain_name, state, p):
                 o = brd[r, c] if (nrows > r >= 0 and ncols > c >= 0) else OBJECTS.none
                 if o == OBJECTS.none and not p.use_margin_as_feature:
                     continue
-                if o not in {OBJECTS.empty}:
+                if o not in {OBJECTS.empty} | p.objects_to_ignore:
                     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
 
-    # if getattr(rep, AT_DESTINATION):
-    #     r, c = np.argwhere(brd==AGENT)[0]
+    # WUMPUS
+    # from ..envs.wumpus import AT_WUMPUS, AT_PIT, AGENT, WUMPUS
+    # if AGENT not in brd and getattr(rep, AT_WUMPUS):
+    #     r, c = np.argwhere(brd==WUMPUS)[0]
     #     sort = CELL_S
-    #     o=DESTINY
+    #     o=AGENT
     #     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
-    # if not PACKAGE in rep.grid:
-    #     r, c = np.argwhere(brd==AGENT)[0]
+    # if AGENT not in brd and getattr(rep, AT_PIT) is not None:
+    #     r, c = getattr(rep, AT_PIT)
     #     sort = CELL_S
-    #     o=PACKAGE
+    #     o=AGENT
     #     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
+
+    # DELIVERY
+    from ..envs.delivery import AT_DESTINATION, HOLDING_PACKAGE, DESTINY, PACKAGE, AGENT
+    if getattr(rep, AT_DESTINATION):
+        r, c = np.argwhere(brd==AGENT)[0]
+        sort = CELL_S
+        o=DESTINY
+        atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
+    if not PACKAGE in rep.grid:
[…]

### 2021-06-01 src/gpl/domains/grid_games/task.py

@@ -124,7 +124,7 @@ class Task(ITask):
             print(tmp_str)
         print("#" * ncols)
 
-    def print_path(self, reps_, divide=10):
+    def print_path(self, reps_, divide=13):
         simplified_objects = self.env.get_simplified_objects()
         nrows, ncols = reps_[0].grid.shape
         while reps_:
@@ -145,7 +145,7 @@ class Task(ITask):
                 single_rep_row += simplified_objects[o]
             size_single_row = len("{} # ".format(single_rep_row))
 
-            info_to_print = ["player", "nmoves", "last_turn", "next_player", "holding_pet", "at_destination", "goal"]
+            info_to_print = ["player", "nmoves", "last_turn", "next_player", "holding_pet", "at_destination", "deadend", "goal", "at_pet"]
             for info in info_to_print:
                 try:
                     tmp_full_row = ""

### 2021-06-01 src/gpl/tester.py

@@ -168,7 +168,7 @@ def run_test(config, search_policy, task, instance_name, rng):
         if spp[0].deadend:
             exitcode = ExitCode.DeadEndReached
             break
-        if visited_sp[sp[1]] > 10:
+        if visited_sp[sp[1]] > 3:
             exitcode = ExitCode.AbstractPolicyNonTerminatingOnTestInstances
             break
 
@@ -228,11 +228,13 @@ def run(config, data, rng):
         else:
             print("\nPOLICY:")
             data.d2l_policy.print_aaai20()
-        print('')
+        print("")
 
     def get_policy(model_factory, static_atoms, data):
-        policy = create_action_selection_function_from_transition_policy(config, model_factory, static_atoms,
-                                                                             data.d2l_policy)
+        policy = create_action_selection_function_from_transition_policy(config,
+                                                                         model_factory,
+                                                                         static_atoms,
+                                                                         data.d2l_policy)
         return policy
 
     # Test that the policy reaches a goal when applied on all test instances

### 2021-06-02 doc/paper/paper.tex
update doc

@@
 \subsubsection{Description}
-In this domain there are two stacks (columns) of tokens.
+This is the Nim version used in~\cite{silver2020few}.In this domain there are two stacks (columns) of tokens.
 The number of actions available in each state depends on the number of tokens, a valid action involves removing one of the tokens.
@@
 When a token is removed, the turn is changed and the other player must remove a token as an action if there is one.
-The objective of the game is to leave the opponent with no actions available on his turn, i.e., without any token.
+The objective of the game is to leave the opponent with no actions available on his turn, i.e.
+without any token.
 The agent and the adversary has on action per turn.
@@
   (A) Num[And(cell-has-token,Exists(left_cell,cell-has-token))] [k=5]
-  (B) Num[And(cell-has-token,Exists(leftdown_cell,cell-has-token))] [k=5]
-  (C) Num[And(cell-has-token,Exists(rightdown_cell,cell-has-token))] [k=5]
+  (B) Num[And(cell-has-token,Forall(leftdown_cell,cell-has-token))] [k=5]
+  (C) Num[And(cell-has-token,Forall(rightdown_cell,cell-has-token))] [k=5]
 \end{Verbatim}
@@
 $A$. Number of tokens with a token immediately to the left of it\\
-$B$. Number of tokens with a token immediately to the leftdown of it\\
-$C$. Number of tokens with a token immediately to the rightdown of it
+$B$. Number of tokens s.t. any cell to the leftdown also has a token.\\
+$C$. Number of tokens s.t. any cell to the rightdown also has a token.
 
@@
 \begin{Verbatim}[fontsize=\footnotesize]
-  1. B>0 AND C>0 -> {A ·, B ↓, C ·}, {A ·, B ·, C ↓}
+  1. B>0 AND C>0 -> {A ·, B ↓, C ↓}
 \end{Verbatim}
@@
 The policy guarantees to leave both stacks with the same number of tokens.
-This is done by decreasing the number of tokens that have a token to their leftdown or rightdown without decreasing the number of tokens with a token next to them.
+This is done by decreasing the number of tokens s.t.
+any cell to the leftdown and to the rightdown has a token, without changing the number of tokens with a token at left to them.
+The only way to fulfill this policy is to remove the token that has a token to its leftdown and an empty cell to its left, or to remove the token that has a token to its rightdown and an empty cell to its right.
+
 As the policy clearly shows, there is no good transition, that includes a change in the number of tokens that a token has on its left.

### 2021-06-08 experiments/shoot.py
problem with feature_generator

@@ -16,10 +16,11 @@ shoot_params = Bunch({
     'use_player_to_encode': True,
     'use_next_player_as_feature': False,
     'use_next_player_to_encode': True,
-    'use_margin_as_feature': False,
-    'map_cells': False,
-    'use_diagonals_for_map_cells': False,
-    'use_adjacency': {COL_S, ROW_S},
+    'use_margin_as_feature': True,
+    'objects_to_ignore': set(),
+    'map_cells': True,
+    'use_diagonals_for_map_cells': True,
+    'use_adjacency': {COL_S, ROW_S, CELL_S},
     'use_bidirectional': {},
     'sorts_to_use': {CELL_S, COL_S, ROW_S},
     'player_can_shoot': {},
@@ -84,16 +85,16 @@ def experiments():
     # version 1:
     # agent and adversary moves ortogonal
     p_v1 = copy.deepcopy(shoot_params)
-    p_v1.player_can_shoot={PLAYER1}
-    p_v1.player_can_check={}
+    p_v1.player_can_shoot={}
+    p_v1.player_can_check={PLAYER1}
     p_v1.max_actions = {PLAYER1: 2,
                         PLAYER2: 1}
     exps["1"] = update_dict(
         base,
         domain=Domain(p_v1),
         instances=[11],
-        allow_bad_states=False,
         test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10],
+        allow_bad_states=False,
     )
 
     # version 2:
@@ -108,7 +109,3 @@ def experiments():
     )
 
     return exps
-
-
-
-

### 2021-06-08 src/gpl/domains/grid_games/grammar/language.py

@@ -17,6 +17,8 @@ CONST = {
 ALL_GRID_DIRECTIONS = ['up', 'rightup', 'right', 'rightdown', 'down', 'leftdown', 'left', 'leftup']
 UP, RIGHTUP, RIGHT, RIGHTDOWN, DOWN, LEFTDOWN, LEFT, LEFTUP = [d for d in ALL_GRID_DIRECTIONS]
 ADJACENT = 'adjacent'
+DISTANCE_2 ='distance_2'
+DISTANCE_MORE_THAN_1 ='distance_more_than_1'
 
 GRID_DIRECTIONS = {
     CELL_S: ALL_GRID_DIRECTIONS,

### 2021-06-08 src/gpl/domains/grid_games/grammar/state_to_atoms.py

@@ -37,17 +37,17 @@ def state_to_atoms(domain_name, state, p):
     #     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
 
     # DELIVERY
-    from ..envs.delivery import AT_DESTINATION, HOLDING_PACKAGE, DESTINY, PACKAGE, AGENT
-    if getattr(rep, AT_DESTINATION):
-        r, c = np.argwhere(brd==AGENT)[0]
-        sort = CELL_S
-        o=DESTINY
-        atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
-    if not PACKAGE in rep.grid:
-        r, c = np.argwhere(brd==AGENT)[0]
-        sort = CELL_S
-        o=PACKAGE
-        atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
+    # from ..envs.delivery import AT_DESTINATION, HOLDING_PACKAGE, DESTINY, PACKAGE, AGENT
+    # if getattr(rep, AT_DESTINATION):
+    #     r, c = np.argwhere(brd==AGENT)[0]
+    #     sort = CELL_S
+    #     o=DESTINY
+    #     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
+    # if not PACKAGE in rep.grid:
+    #     r, c = np.argwhere(brd==AGENT)[0]
+    #     sort = CELL_S
+    #     o=PACKAGE
+    #     atoms.append((f'{sort}-has-{o}', CONST[sort](r, c, nrows, ncols)))
 
     for u in p.unary_predicates:
         if getattr(rep, u):

### 2021-06-08 src/gpl/domains/grid_games/utils.py

@@ -28,3 +28,11 @@ def identify_next_player(rep, params):
         return rep.player
     else:
         return opposite_player(rep.player)
+
+def in_grid(r, c, nrows, ncols, use_margins=False):
+    if (nrows > r >= 0 and ncols > c >= 0):
+        return True
+    elif use_margins and (nrows >= r >= -1 and ncols >= c >= -1):
+        return True
+    else:
+        return False

### 2021-06-08 src/gpl/tester.py

@@ -141,10 +141,11 @@ def run_test(config, search_policy, task, instance_name, rng):
 
         not_novelty_sp = dict()
         for op, sp in goods:
+            enc_op = encode_operator(s, op, task)
             if config.use_state_novelty:
                 times_seen = visited_sp[sp[1]]
                 if times_seen > 0:
-                    not_novelty_sp[(op, sp[1])] = times_seen
+                    not_novelty_sp[(enc_op, sp[1])] = times_seen
                     continue
                 else:
                     break

### 2021-06-30 doc/paper/paper.tex
problem with feature_generator
doc updated

@@
 without any token.
-The agent and the adversary has on action per turn.
+The agent and the adversary has one action per turn.
 It is interesting to note that in this game not all states are solvable if the opponent plays optimally.
@@
 
-\subsection{Checkmate whith Queen}
+\subsection{Checkmate in n with Queen}
+\subsubsection{Description}
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  k  .  .  K #
+  # .  .  .  .  . #
+  # .  .  .  .  . #
+  # Q  .  .  .  . #
+  # .  .  .  .  . #
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (CM) Atom[checkmate] [k=1]
+  (SM) Atom[stalemate] [k=1]
+  (QbK) Atom[white_queen_between_kings] [k=1]
+  (KE) Atom[black_king_closed_in_edge_by_white_queen] [k=1]
+  (KD) Dist[cell-has-white_king;adjacent_cell;cell-has-black_king] [k=4]
+  (BKhA) Bool[And(cell-attaked-by-black_king,Not(cell-attaked-by-white))] [k=4]
+  (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_queen))] [k=4]
+  () Bool[And(row-has-white_queen,Exists(adjacent_row,row-has-black_king)))] [k=6]
+  (WQadjBK_col) Bool[And(col-has-white_queen,Exists(adjacent_col,col-has-black_king)))] [k=6]
+  (WQadjBK) Bool[And(cell-has-white_queen,Exists(adjacent_cell,cell-has-black_king)))] [k=6]
+  (WQadjWK) Bool[And(cell-has-white_queen,Exists(adjacent_cell,cell-has-white_king)))] [k=6]
+\end{Verbatim}
+
+\subsubsection{All Transition Features}
+This features reason about how the value of the features can change in all possible successors.
+\begin{Verbatim}[fontsize=\footnotesize]
+  (CA) Bool[can(A, DEC)] [k=2]
+  (CCM) bool[can(CM, INC)] [k=2]
+\end{Verbatim}
+
+\subsubsection{Feature Description}
+$CM$. Checkmate\\
+$SM$. Stalemate\\
+$KE$. Black king is closed in an edge of the table by the white queen\\
+$QbK$. White queen is somewhere between kings, rows or columns\\
+$A$. The number of cells attaked by black king and not attacked by white queen\\
+$BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
+$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK AND WQadjWK$\\
+$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row OR WQadjWK_col$\\
+$CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\
+$CCM$. It is possible to do checkmate in the current state
+
+\subsubsection{Policy}
+  \begin{Verbatim}[fontsize=\footnotesize]
+   1. KE=0, CA>0 -> {A ↓}
+   2. KE=0, CA=0 -> {A ·, KD ·}
+   3. BKhA=0, WQadjBK_line>0 -> {KD ·, WQadjBK_line ·}
+   4. CCM=0, KE>0 -> {KD ↓}
+   5. CCM=1 -> {CM ↑}
+  \end{Verbatim}
+
+\subsubsection{Policy Implicits}
+The next features has to be in that certain value after the transition for classifing the transition as good, taking into account the policy rules.
+  \begin{Verbatim}[fontsize=\footnotesize]
+   Qaw=0, Qbk>0, SM=0
+  \end{Verbatim}
+
+\subsubsection{Policy description}
+Rules 1 and 2 cover the cases in which the king is not enclosed in an edge of the file.
+The first rule states that it is good to take transitions that decrease the number of squares available to the black king by using the queen.
+The second rule says that if the first rule is not applicable it is good to take transitions that do not alter the number of squares available to the black king, without moving the white king.
+The third rule refers to those cases where the black king had moved to its only free square, and classifies as good those transitions in which the queen is moved so that it is not stalemate and remains on the line adjacent to the black king.
+Rule four covers cases in which the black king is locked on an edge by the queen, and it is good to move the white king closer.
+finally, rule 5 says that if it is possible to checkmate it is good to do so.
+It should be noted that thanks to the implicit parts of the policy the king will never be left tied up and unprotected, stalemate will never occur and the white king will always be placed and remain in a line that is between the lines of the kings, whether rows or columns.
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  K.... # K.... # K.... # ..... # ..... # ..... # ..... # ..... # ..... #
+  ..Q.. # ..... # ..... # ..K.. # ..K.. # ..K.. # ..... # ..... # ..... #
+  ..... # ..... # ..... # ..... # ..... # ..... # ..K.. # ..K.. # ..K.. #
+  ..... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # ...Q. #
+  ....k # ....k # ...k. # ...k. # ..k.. # ...k. # ...k. # ....k # ....k #
+\end{Verbatim}
+
+\subsection{Checkmate in one with Queen}
 \subsubsection{Description}
@@
 To check that the policy is complete, it is tested on all possible, for each board size $NxM$ where both $N$ and $M$ are numbers no greater than twenty randomly selected.
-
+v
 \subsubsection{Example of Game}
@@
 
-\subsection{Checkmate with Rook}
+\subsection{Checkmate in one with Rook}
 \subsubsection{Description}

### 2021-06-30 experiments/checkmate_tactic.py

@@ -1,4 +1,5 @@
 import copy
+import itertools
 import math
 from sltp.util.misc import update_dict
 from gpl.domains.grid_games.domain import Domain
@@ -31,7 +32,7 @@ ct_params = Bunch({
     'use_adjacency': {CELL_S, ROW_S , COL_S},
     'use_distance_2': {},
     'use_distance_more_than_1': {},
-    'use_bidirectional': {},
+    'use_bidirectional': {CELL_S, ROW_S , COL_S},
     'sorts_to_use': {CELL_S, ROW_S , COL_S},
     'n_moves': 10000,
     'unary_predicates': {CHECKMATE, STALEMATE, CHECK,
@@ -64,7 +65,7 @@ def experiments():
         distance_feature_max_complexity=4,
         concept_generation_timeout=15000,
         cond_feature_max_complexity=0,
-        comparison_features=False,
+        comparison_features=True,
         generate_goal_concepts=False,
         print_denotations=True,
         print_hstar_in_feature_matrix=False,
@@ -117,8 +118,19 @@ def experiments():
 
     exps["2"] = update_dict(
         exps["1"],
-        instances=[300, ],
-        feature_generator=debug_features_checkmate_tactic_queen(),
+        validate_features=debug_validate_features_queen(),
+    )
+
+    exps["3"] = update_dict(
+        exps["1"],
+        instances=[1500],
+        validate_features=debug_validate_features_queen(),
+    )
+
+    exps["4"] = update_dict(
+        exps["1"],
+        instances=[1500],
+        validate_features=debug_validate_features_queen(),
     )
 
     return exps
@@ -137,9 +149,17 @@ row_h_bk = 'row-has-black_king'
 cell_h_wk = 'cell-has-white_king'
 cell_h_wq = 'cell-has-white_queen'
[…]

### 2021-06-30 src/d2l/src/sltp/separation.py

@@ -476,7 +476,7 @@ class TransitionActionClassificationPolicy:
     def __assign_keys_to_featuers(self):
         import string
         # ASCII = string.printable[36:62] # A..Z
-        ASCII = string.printable # A..Z
+        ASCII = string.printable[10:62] # A..Z
         for f in self.features:
             ASCII, b = ASCII[1:], ASCII[0]
             self.simplified_features[str(f)] = b

### 2021-06-30 src/gpl/domains/grid_games/envs/checkmate_tactic.py

@@ -653,7 +653,7 @@ TEST_LAYOUTS_QUEEN = {
     -10: (15, 15, (6, 6), (9, 9), (0, 0), None),
 }
 
-LAYOUTS_CHECK_IN_ONE_QUEEN = generate_check_in_one([(3, 3), (4, 3), (4, 4), (5, 5), (6, 6)], WHITE_QUEEN)
+LAYOUTS_CHECK_IN_ONE_QUEEN = generate_check_in_one([(3, 3), (4, 3), (4, 4), (4, 4), (4, 5), (5, 5), (6, 6)], WHITE_QUEEN)
 LAYOUTS_CHECK_IN_ONE_TOWER = generate_check_in_one([(3, 3), (4, 3), (3, 4), (4, 4), (4, 5), (5, 4), (5, 5), (6, 6)], WHITE_TOWER)
 
 for k in TEST_LAYOUTS_TOWER.keys():

### 2021-06-30 src/gpl/domains/grid_games/grammar/state_to_atoms.py

@@ -29,41 +29,42 @@ def state_to_atoms(domain_name, state, p):
                 if o not in {OBJECTS.empty} | p.objects_to_ignore:
                     atoms.append((CELL_HAS(sort, o), CONST[sort](r, c, nrows, ncols)))
 
-    # CHECKMATE TACTIC
-    from ..envs.checkmate_tactic import get_attacking_mask_from_piece, get_attacking_mask, \
-        WHITE, BLACK, WHITE_KING, WHITE_TOWER, BLACK_KING, CHECKMATE, WHITE_QUEEN
-    mask_white = get_attacking_mask(brd, WHITE)
-    mask_black = get_attacking_mask(brd, BLACK)
-    mask_bk = get_attacking_mask_from_piece(brd, BLACK_KING)
-    mask_wk = get_attacking_mask_from_piece(brd, WHITE_KING)
-    # mask_wr = get_attacking_mask_from_piece(brd, WHITE_TOWER)
-    mask_wq = get_attacking_mask_from_piece(brd, WHITE_QUEEN)
-    # mask_quadrant_bk = get_mask_quadrant_black_king(brd)
-    for r in range(nrows):
-        for c in range(ncols):
-            cell = CONST[CELL_S](r, c, nrows, ncols)
-            if mask_wk[r, c]:
-                atoms.append((CELL_HAS_PIECE_ATTAKED_BY(WHITE_KING), cell))
-            # if mask_wr[r, c]:
-            #     atoms.append((CELL_HAS_PIECE_ATTAKED_BY(WHITE_TOWER), cell))
-            if mask_bk[r, c]:
-                atoms.append((CELL_HAS_PIECE_ATTAKED_BY(BLACK_KING), cell))
-            if mask_wq[r, c]:
-                atoms.append((CELL_HAS_PIECE_ATTAKED_BY(WHITE_QUEEN), cell))
-            if mask_white[r, c]:
-                atoms.append((CELL_HAS_COLOR_ATTAKED_BY(WHITE), cell))
-            if mask_black[r, c]:
-                atoms.append((CELL_HAS_COLOR_ATTAKED_BY(BLACK), cell))
-            # if mask_quadrant_bk[r, c] and not mask_white[r, c] and not getattr(rep, CHECKMATE):
-            #     atoms.append((CELL_IS_IN(BLACK_KING_AVAILABLE_QUADRANT), cell))
-            if in_top(r, c, nrows, ncols):
-                atoms.append((CELL_IS_IN(TOP), cell))
[…]

### 2021-06-30 src/gpl/tester.py

@@ -133,15 +133,17 @@ def run_test(config, search_policy, task, instance_name, rng):
 
         exitcode, goods = run_policy_based_search(config, search_policy, task, s, successors)
         if exitcode == ExitCode.AbstractPolicyNotCompleteOnTestInstances:
-            if config.allow_bad_states:
-                # we know we are not complete
-                # TODO: take bad states into account
-                goods = successors
-                if (config.verbosity>2):
-                    logging.info("WARNING: Policy not complete in state:\n{}".format(task.get_printable_rep(s[0])))
-            else:
-                exitcode = ExitCode.AbstractPolicyNotCompleteOnTestInstances
-                break
+            if (config.verbosity > 2):
+                logging.info("WARNING: Policy not complete in state:\n{}".format(task.get_printable_rep(s[0])))
+            exitcode = ExitCode.AbstractPolicyNotCompleteOnTestInstances
+            break
+            # if config.allow_bad_states:
+            #     # we know we are not complete
+            #     # TODO: take bad states into account
+            #     goods = successors
+            # else:
+            #     exitcode = ExitCode.AbstractPolicyNotCompleteOnTestInstances
+            #     break
 
         not_novelty_sp = dict()
         for op, sp in goods:

### 2021-07-14 doc/paper/paper.tex
pygame init

@@
   (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_queen))] [k=4]
-  () Bool[And(row-has-white_queen,Exists(adjacent_row,row-has-black_king)))] [k=6]
+  (WQadjBK_row) Bool[And(row-has-white_queen,Exists(adjacent_row,row-has-black_king)))] [k=6]
   (WQadjBK_col) Bool[And(col-has-white_queen,Exists(adjacent_col,col-has-black_king)))] [k=6]
@@
 $BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
-$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK AND WQadjWK$\\
-$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row OR WQadjWK_col$\\
+$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK$ AND $WQadjWK$\\
+$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row$ OR $WQadjWK_col$\\
+$CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\
+$CCM$. It is possible to do checkmate in the current state
+
+\subsubsection{Policy}
+  \begin{Verbatim}[fontsize=\footnotesize]
+   1. KE=0, CA>0 -> {A ↓}
+   2. KE=0, CA=0 -> {A ·, KD ·}
+   3. BKhA=0, WQadjBK_line>0 -> {KD ·, WQadjBK_line ·}
+   4. CCM=0, KE>0 -> {KD ↓}
+   5. CCM=1 -> {CM ↑}
+  \end{Verbatim}
+
+\subsubsection{Policy Implicits}
+The next features has to be in that certain value after the transition for classifing the transition as good, taking into account the policy rules.
+  \begin{Verbatim}[fontsize=\footnotesize]
+   Qaw=0, Qbk>0, SM=0
+  \end{Verbatim}
+
+\subsubsection{Policy description}
+Rules 1 and 2 cover the cases in which the king is not enclosed in an edge of the file.
+The first rule states that it is good to take transitions that decrease the number of squares available to the black king by using the queen.
+The second rule says that if the first rule is not applicable it is good to take transitions that do not alter the number of squares available to the black king, without moving the white king.
+The third rule refers to those cases where the black king had moved to its only free square, and classifies as good those transitions in which the queen is moved so that it is not stalemate and remains on the line adjacent to the black king.
+Rule four covers cases in which the black king is locked on an edge by the queen, and it is good to move the white king closer.
+finally, rule 5 says that if it is possible to checkmate it is good to do so.
+It should be noted that thanks to the implicit parts of the policy the king will never be left tied up and unprotected, stalemate will never occur and the white king will always be placed and remain in a line that is between the lines of the kings, whether rows or columns.
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  K.... # K.... # K.... # ..... # ..... # ..... # ..... # ..... # ..... #
+  ..Q.. # ..... # ..... # ..K.. # ..K.. # ..K.. # ..... # ..... # ..... #
+  ..... # ..... # ..... # ..... # ..... # ..... # ..K.. # ..K.. # ..K.. #
+  ..... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # ...Q. #
+  ....k # ....k # ...k. # ...k. # ..k.. # ...k. # ...k. # ....k # ....k #
+\end{Verbatim}
+
+\subsection{Checkmate in n with Rook}
+\subsubsection{Description}
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  k  .  .  K #
+  # .  .  .  .  . #
+  # .  .  .  .  . #
+  # R  .  .  .  . #
+  # .  .  .  .  . #
+\end{Verbatim}
+
+\subsubsection{Features}
+\begin{Verbatim}[fontsize=\footnotesize]
+  (CM) Atom[checkmate] [k=1]
+  (SM) Atom[stalemate] [k=1]
+  (QbK) Atom[white_rook_between_kings] [k=1]
+  (KE) Atom[black_king_closed_in_edge_by_white_rook] [k=1]
+  (KD) Dist[cell-has-white_king;adjacent_cell;cell-has-black_king] [k=4]
+  (BKhA) Bool[And(cell-attaked-by-black_king,Not(cell-attaked-by-white))] [k=4]
+  (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_rook))] [k=4]
+  (WQadjBK_row) Bool[And(row-has-white_rook,Exists(adjacent_row,row-has-black_king)))] [k=6]
+  (WQadjBK_col) Bool[And(col-has-white_rook,Exists(adjacent_col,col-has-black_king)))] [k=6]
+  (WQadjBK) Bool[And(cell-has-white_rook,Exists(adjacent_cell,cell-has-black_king)))] [k=6]
+  (WQadjWK) Bool[And(cell-has-white_rook,Exists(adjacent_cell,cell-has-white_king)))] [k=6]
+\end{Verbatim}
+
+\subsubsection{All Transition Features}
+This features reason about how the value of the features can change in all possible successors.
+\begin{Verbatim}[fontsize=\footnotesize]
+  (CA) Bool[can(A, DEC)] [k=2]
+  (CCM) bool[can(CM, INC)] [k=2]
+\end{Verbatim}
+
+\subsubsection{Feature Description}
+$CM$. Checkmate\\
+$SM$. Stalemate\\
+$KE$. Black king is closed in an edge of the table by the white queen\\
+$QbK$. White queen is somewhere between kings, rows or columns\\
+$A$. The number of cells attaked by black king and not attacked by white queen\\
+$BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
+$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK$ AND $WQadjWK$\\
+$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row$ OR $WQadjWK_col$\\
 $CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\

### 2021-07-14 experiments/chase.py

@@ -22,6 +22,9 @@ chase_params = Bunch({
     'sorts_to_use': {COL_S, ROW_S, CELL_S},
     'unary_predicates': {},
     'can_build_walls': False,
+    'use_distance_2': {},
+    'use_distance_more_than_1': {},
+    'use_verbose_margin_as_feature': False,
     'ava_actions': {
         PLAYER1: {RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP},
         # PLAYER1: {UP, DOWN, RIGHT, LEFT},
@@ -86,7 +89,9 @@ def experiments():
         base,
         instances=[0],
         # instances=[0, 15],
-        test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16],
+        skip_train_steps=[0, 1, 2, 3],
+        test_instances=[12],
+        # test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16],
 
     )
 

### 2021-07-14 src/gpl/sampling.py

@@ -5,7 +5,7 @@ import math
 import sys
 from collections import defaultdict, OrderedDict, deque
 
-from ..utils import encode_operator
+from gpl.utils import encode_operator
 
 from sltp.returncodes import ExitCode
 from sltp.util.command import read_file

### 2021-07-14 src/gpl/utils.py

@@ -1,6 +1,3 @@
-import pickle
-import sys
-
 import dill
 
 def _create_exception_msg(step, e):
@@ -46,7 +43,7 @@ def encode_operator(s, op, task):
     return o
 
 def get_sampling_class(config):
-    from .sampling.adv import TransitionSampleADV
+    from gpl.sampling import TransitionSampleADV
     sampling_class = {
         'adv': TransitionSampleADV(),
     }[config.domain.type]

### 2021-07-22 doc/paper/paper.tex
update

@@
 
+\abstract
+
+Generalized planning is concerned with the computation of general policies that solve multiple instances of a planning domain all at once.
+It has been recently shown that these policies can be computed in two steps: first, a suitable abstraction in the form of a qualitative numerical planning problem (QNP) is learned from sample plans, then the general policies are obtained from the learned QNP using a planner.
+In this work, we introduce an alternative approach for computing more expressive general policies which does not require sample plans or a QNP planner.
+The new formulation is very simple and can be cast in terms that are more standard in machine learning: a large but finite pool of features is defined from the predicates in the planning examples using a general grammar, and a small subset of features is sought for separating “good” from “bad” state transitions, and goals from non-goals.
+The problems of finding such a “separating surface” while labeling the transitions as “good” or “bad” are
+jointly addressed as a single combinatorial optimization problem expressed as a Weighted Max-SAT problem.
+The advantage of looking for the simplest policy in the given feature space that solves the given examples, possibly non-optimally, is that many domains have no general, compact policies that are optimal.
+The approach yields general policies for a number of benchmark adversarial domains, even when non-determinism exists in the adverary turn.
+We use a uniform grammar for all the grid domains capable of capturing the domain representations.
+These policies can be interpreted qualitatively, explained, and it can be shown mathematically that they will solve all possible instances within a class of problems.
+This is an advantage when making manual policy changes.
+We also show an example of how the explainable policies produced by our algorithms can be applied to real robots.
+
+\section{Introduction}
+
+Generalized planning is concerned with the computation of general policies or plans that solve multiple instances of a given planning domain all at once (Srivastava, Immerman, and Zilberstein 2008; Bonet, Palacios, and Geffner 2009; Huand De Giacomo 2011; Belle and Levesque 2016; Segovia, Jim´enez, and Jonsson 2016).
+If the instances share the same strategy, it doesn't matter how different they are.
+For example, in an environment where an agent has to pick up a key and then approach a door and it will open, the strategy is to approach the key, pick it up, and then approach the door in order to open it.
+In this example it does not matter how large the environment is and how many actions the agent has to take, since the strategy does not change.
+
+The key question in generalized planning is how to represent and compute such general plans from the domain representation.
+This was solved by [], for non-adversarial and deterministic domains but not for adversarial domains, where you cannot control what the adversary will do during his turn.
+However, there are adversarial domains where the agent can take actions that no matter what happens in the environment the agent wins.
+For instance, if we are in a domain where an agent must chase an adversary, and the adversary can run slower than the agent, the strategy will be to decrease the distance between them until the agent can catch him.
+This we know is a winning strategy where it does not matter what the adversary does.
+
+This was solved by [], for non-adversarial and deterministic domains but not for adversarial domains, where you cannot control what the adversary will do during his turn.
+However, there are adversarial domains where you can take actions that no matter what happens in the environment you win.
+For example, if we are in a domain where an agent must chase an adversary, and the adversary can run slower than the agent, the strategy will be to decrease the distance between them until the agent can catch him.
+This we know is a winning strategy where it does not matter what the adversary does.
+Nor will the size of the environment, the distance or the position of the agent and the adversary matter.
+
+In one of the most general formulations, general policies are obtained from an abstract planning model expressed as a qualitative numerical planning problem or QNP (Srivastava et al.
+2011).
+A QNP is a standard STRIPS planning model extended with non-negative numerical variables that can be decreased or increased “qualitatively”; i.e., by uncertain positive amounts, short of making the variables negative.
+Unlike standard planning with numerical variables (Helmert 2002), QNP planning is decidable, and QNPs can be compiled in polynomial time into fully observable non-deterministic (FOND) problems (Bonet and Geffner 2020)
+
+The main advantage of the formulation of generalized planning based on QNPs is that it applies to standard relational domains where the pool of (ground) actions change from instance to instance.
+On the other hand, while the planning domain is assumed to be given, the QNP abstraction is not, and hence it has to be written by hand or learned.
+This is the approach of Bonet, Franc`es, and Geffner (2019) where generalized plans are obtained by learning the QNP abstraction from the domain representation and sample plans, and then solving the abstraction with a QNP planner.
+
+In this work, we build on this thread but introduce an alternative approach for computing general policies that is simpler, yet more powerful.
+The learning problem is cast as a self-supervised classification problem where (1) a pool of features is automatically generated from a uniform grammar applied to the domain predicates, and (2) a small subset of features is sought for separating “good” from “bad” state transitions, and goals from non-goals.
+The problems of finding the “separating surface” while labeling the transitions as “good” or “bad” are addressed jointly as a single combinatorial optimization task solved with a Weighted Max-SAT solver.
+The approach yields general policies for a number of benchmark domains.
+
+One of the advantages of having explainable policies is that it gives the engineer or researcher the possibility to modify them easily if necessary.
+For instance, if there are known exceptions within the domain.
+Although this has not been necessary in the domains discussed in this paper.
+
+The paper is organized as follows.
+We first review related work.
+Then we introduce a SAT encoding and the variables, where we see what the input of our algorithm consists of.
+We then present the learning task, the computational approach for solving it, and the experimental results.
+Then we describe the grammar used in all the domains.
+Then we describe each of the domains, and interpret the features and policies found with our approach.
+These explainable policies will be the output of the algorithm.
+Then we show how it is possible to use our framework to introduce policies or modify them after the training process.
+The use case is checkamate in chess in n-moves and any board size, with two kings and a queen.
+Finally, we show how it is possible to use the policies with robots, both in simulators and in the real world.
+
+\subsection{Related Work}
+
+% XRL
+% Planning, and explainable reinforcement learning (XRL)
+
+\subsection{Generalized Planning}
+
+A key question in generalized planning is how to represent general plans or policies when the different instances to be solved have different sets of objects and ground actions.
+One solution is to work with general features (functions) that have well defined values over any state of any possible domain instance, and think of general policies π as mappings from feature valuations into abstract actions that denote changes in the feature values (Bonet and Geffner 2018).
+In this work, we build on this intuition but avoid the introduction of abstract actions (Bonet and Geffner 2021).
+
 \subsection{SAT Encoding}
@@
  \item Pool $F$ of description logic features $f$, each with given feature complexity $\mathcal{K}(f)$.
- \item \newcontent{} A (training) set $T$ of transitions $(s, a, s') \in T$ from a number of instances of the same domain.
+ \item A (training) set $T$ of transitions $(s, a, s') \in T$ from a number of instances of the same domain.
        We assume $T$ is \emph{closed}: if $s$ appears in the first position of a transition, then all possible
        transitions starting in $s$ in that instance appear in $T$ too.
- \item \newcontent{} A set $adv(s)$ of all possible moves by the adversary on state $s$.
+ \item A set $adv(s)$ of all possible moves by the adversary on state $s$.
 
@@
 
- \item \newcontent{} A Boolean parameter \texttt{allow\_bad\_states} with intended meaning ``allow the policy
+ \item A Boolean parameter \texttt{allow\_bad\_states} with intended meaning ``allow the policy
         to remain undefined for some of the states in the training set''.
- \item \newcontent{} A parameter \texttt{action\_labels} with possible values:
+ \item A parameter \texttt{action\_labels} with possible values:
  \begin{itemize}
@@
 
-\paragraph{Bullet points}
-\begin{itemize}
-\item Learning generalized policies in unsupervised FOND domains from small examples.
-\item FOND encoding, introducing Good(s, a) features to deal with non-determinism.
+\subsection{Conclusions}
+
+\subsection{Discussoin of Results}
+
+\subsection{Discussoin of Results}
+
+%\paragraph{Bullet points}
+%\begin{itemize}
+%\item Learning generalized policies in unsupervised FOND domains from small examples.
+%\item FOND encoding, introducing Good(s, a) features to deal with non-determinism.
 Where $a \in A$, and $A$ is not required to be fixed.
 However, if $A$ is fixed we show a way to exploit it reducing the number of transitions to distinguish.
-\item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
-\item Empirical results with six different domains: Chase, Shoot, Space Invaders, Delivery, Checkmate with Queen, Checkmate with Rook.
-\item Incremental policy learning, to address the scalability problem.
+%\item Being complete in domains where not all states have a good transition, with the optional constraint Bad(s).
+%\item Empirical results with six different domains: Chase, Shoot, Space Invaders, Delivery, Checkmate with Queen, Checkmate with Rook.
+%\item Incremental policy learning, to address the scalability problem.
 First a random sample is taken from the whole graph and the policy is then refined incrementally by iteratively increasing the sample size.
 The strategy for increasing the size of the sample can be goal-directed or random.
-%\item Introducing the sort of novelty to choose between the different successors classified as good by our policy
-\item Use of a uniform grammar for the different grid domains.
-\end{itemize}
+%%\item Introducing the sort of novelty to choose between the different successors classified as good by our policy
+%\item Use of a uniform grammar for the different grid domains.
+%\end{itemize}
 

### 2021-07-22 experiments/chase.py

@@ -4,8 +4,8 @@ from sltp.util.misc import update_dict
 from gpl.domains.grid_games.domain import Domain
 from gpl.utils import Bunch
 from gpl.domains.grid_games.grammar.language import CELL_S, COL_S, ROW_S
-from gpl.domains.grid_games.envs.chase import RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, UP, DOWN, RIGHT, LEFT
 from gpl.domains.grid_games.grammar.objects import PLAYER1, PLAYER2
+from gpl.domains.grid_games.envs.chase import RIGHTUP, RIGHTDOWN, LEFTDOWN, LEFTUP, UP, DOWN, RIGHT, LEFT
 
 chase_params = Bunch({
     'domain_name': 'chase',
@@ -89,7 +89,8 @@ def experiments():
         base,
         instances=[0],
         # instances=[0, 15],
-        skip_train_steps=[0, 1, 2, 3],
+        skip_train_steps=[],
+        # skip_train_steps=[0, 1, 2, 3],
         test_instances=[12],
         # test_instances=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16],
 

### 2021-07-22 src/gpl/demo.py

@@ -67,7 +67,6 @@ def test_d2l_policy_on_gym_env(config, data, get_policy, rng):
 
             # init inteactive screen
             task.init_interacive_screen(task.initial_state)
-            task.end_inteactive_screen()
 
             # And now we inject our desired search and heuristic functions
             exitcode, solution, path, expanded = run_test(config, search_policy, task, instance_name, rng)
@@ -81,7 +80,7 @@ def test_d2l_policy_on_gym_env(config, data, get_policy, rng):
                 logging.info(f"Goal found after expanding {expanded} nodes")
                 logging.info(f"The solution was: {solution}")
             else:
-                logging.warning(f"Testing of policy failed with code: {exitcode}")
+                logging.warnieng(f"Testing of policy failed with code: {exitcode}")
                 unsolved_instances.append(instance_name)
                 continue
 

### 2021-07-22 src/gpl/domains/grid_games/envs/chase.py

@@ -1,3 +1,4 @@
+import os.path
 import sys
 
 import numpy as np
@@ -26,6 +27,14 @@ COLOR_TO_PIECES = {
 
 opposite_color = lambda c: BLACK if c == WHITE else WHITE
 
+def load_image(image_name, scale):
+    images_path = '/home/orbital/ws/research/gpl/code/gpl/src/gpl/domains/grid_games/envs/images'
+    return pygame.transform.scale(pygame.image.load(os.path.join(images_path, image_name)), scale)
+
+IMAGE_OBJECT = {
+    BLACK_KING: load_image('adv.jpeg', (100, 100)),
+    WHITE_KING: load_image('agent.jpg', (60, 60)),
+}
 
 PIECE_VALID_ACTIONS = {
     WHITE_KING: lambda pos, layout, params: king_valid_actions(pos, layout, WHITE, params),
@@ -177,20 +186,37 @@ class Env(object):
             actions += PIECE_VALID_ACTIONS[BLACK_KING](c0, layout, self.params)
         return actions
 
+    def init_interacive_screen(self, r):
+        nrows, ncols = r.grid.shape
+        self.screen = pygame.display.set_mode((nrows * 20, ncols * 20))
+        clock = pygame.time.Clock()
+        pygame.display.set_caption("chase")
+        self.screen.fill((255, 255, 255))
+        self.update(r)
+
+    def update(self, r):
+        self.screen.fill((255, 255, 255))
+        agent_r, agent_c = np.argwhere(r.grid == WHITE_KING)[0]
+        adv_r, adv_c = np.argwhere(r.grid == BLACK_KING)[0]
+        self.screen.blit(IMAGE_OBJECT[BLACK_KING], (adv_r * 20, adv_c * 20))
+        self.screen.blit(IMAGE_OBJECT[WHITE_KING], (agent_r * 20, agent_c * 20))
+        pygame.display.flip()
+
     def event_to_op(self, rep, event):
+        recognized_op = False; op = None
         valid_actions = self.available_actions(rep)
         if event.key == pygame.K_LEFT:
-            op = LEFT
-        elif event.key == pygame.K_RIGHT:
-            op = RIGHT
-        elif event.key == pygame.K_UP:
             op = UP
-        elif event.key == pygame.K_DOWN:
+        elif event.key == pygame.K_RIGHT:
             op = DOWN
+        elif event.key == pygame.K_UP:
[…]

### 2021-07-23 doc/paper/paper.tex
doc update

@@
 This is an advantage when making manual policy changes.
-We also show an example of how the explainable policies produced by our algorithms can be applied to real robots.
+We also show an example of how the explainable policies produced by our algorithm can be applied to real robots.
 
@@
 On the other hand, while the planning domain is assumed to be given, the QNP abstraction is not, and hence it has to be written by hand or learned.
-This is the approach of Bonet, Franc`es, and Geffner (2019) where generalized plans are obtained by learning the QNP abstraction from the domain representation and sample plans, and then solving the abstraction with a QNP planner.
+This is the approach of Bonet, Francés, and Geffner (2019) where generalized plans are obtained by learning the QNP abstraction from the domain representation and sample plans, and then solving the abstraction with a QNP planner.
 
@@
 The approach yields general policies for a number of benchmark domains.
-
-One of the advantages of having explainable policies is that it gives the engineer or researcher the possibility to modify them easily if necessary.
+One of the advantages of having explainable policies is that it gives the engineer the possibility to modify them easily if is necessary.
 For instance, if there are known exceptions within the domain.
-Although this has not been necessary in the domains discussed in this paper.
 
@@
 A key question in generalized planning is how to represent general plans or policies when the different instances to be solved have different sets of objects and ground actions.
-One solution is to work with general features (functions) that have well defined values over any state of any possible domain instance, and think of general policies π as mappings from feature valuations into abstract actions that denote changes in the feature values (Bonet and Geffner 2018).
+One solution is to work with general features (functions) that have well defined values over any state of any possible domain instance, and think of general policies $\pi$ as mappings from feature valuations into abstract actions that denote changes in the feature values (Bonet and Geffner 2018).
 In this work, we build on this intuition but avoid the introduction of abstract actions (Bonet and Geffner 2021).
@@
 
-\newpage
-
 \section{Grammar}
@@
 \subsection{Space Invaders}
+
 \subsubsection{Description}
@@
 
-\subsection{Checkmate in n with Queen}
-\subsubsection{Description}
-
-\subsubsection{Training instances}
-\begin{Verbatim}[fontsize=\footnotesize]
-  # .  k  .  .  K #
-  # .  .  .  .  . #
-  # .  .  .  .  . #
-  # Q  .  .  .  . #
-  # .  .  .  .  . #
-\end{Verbatim}
-
-\subsubsection{Features}
-\begin{Verbatim}[fontsize=\footnotesize]
-  (CM) Atom[checkmate] [k=1]
-  (SM) Atom[stalemate] [k=1]
-  (QbK) Atom[white_queen_between_kings] [k=1]
-  (KE) Atom[black_king_closed_in_edge_by_white_queen] [k=1]
-  (KD) Dist[cell-has-white_king;adjacent_cell;cell-has-black_king] [k=4]
-  (BKhA) Bool[And(cell-attaked-by-black_king,Not(cell-attaked-by-white))] [k=4]
-  (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_queen))] [k=4]
-  (WQadjBK_row) Bool[And(row-has-white_queen,Exists(adjacent_row,row-has-black_king)))] [k=6]
-  (WQadjBK_col) Bool[And(col-has-white_queen,Exists(adjacent_col,col-has-black_king)))] [k=6]
-  (WQadjBK) Bool[And(cell-has-white_queen,Exists(adjacent_cell,cell-has-black_king)))] [k=6]
-  (WQadjWK) Bool[And(cell-has-white_queen,Exists(adjacent_cell,cell-has-white_king)))] [k=6]
-\end{Verbatim}
-
-\subsubsection{All Transition Features}
-This features reason about how the value of the features can change in all possible successors.
-\begin{Verbatim}[fontsize=\footnotesize]
-  (CA) Bool[can(A, DEC)] [k=2]
-  (CCM) bool[can(CM, INC)] [k=2]
-\end{Verbatim}
-
-\subsubsection{Feature Description}
-$CM$. Checkmate\\
-$SM$. Stalemate\\
-$KE$. Black king is closed in an edge of the table by the white queen\\
-$QbK$. White queen is somewhere between kings, rows or columns\\
-$A$. The number of cells attaked by black king and not attacked by white queen\\
-$BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
-$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK$ AND $WQadjWK$\\
-$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row$ OR $WQadjWK_col$\\
-$CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\
-$CCM$. It is possible to do checkmate in the current state
-
-\subsubsection{Policy}
-  \begin{Verbatim}[fontsize=\footnotesize]
-   1. KE=0, CA>0 -> {A ↓}
-   2. KE=0, CA=0 -> {A ·, KD ·}
-   3. BKhA=0, WQadjBK_line>0 -> {KD ·, WQadjBK_line ·}
-   4. CCM=0, KE>0 -> {KD ↓}
-   5. CCM=1 -> {CM ↑}
-  \end{Verbatim}
-
-\subsubsection{Policy Implicits}
-The next features has to be in that certain value after the transition for classifing the transition as good, taking into account the policy rules.
-  \begin{Verbatim}[fontsize=\footnotesize]
-   Qaw=0, Qbk>0, SM=0
-  \end{Verbatim}
-
-\subsubsection{Policy description}
-Rules 1 and 2 cover the cases in which the king is not enclosed in an edge of the file.
-The first rule states that it is good to take transitions that decrease the number of squares available to the black king by using the queen.
-The second rule says that if the first rule is not applicable it is good to take transitions that do not alter the number of squares available to the black king, without moving the white king.
-The third rule refers to those cases where the black king had moved to its only free square, and classifies as good those transitions in which the queen is moved so that it is not stalemate and remains on the line adjacent to the black king.
-Rule four covers cases in which the black king is locked on an edge by the queen, and it is good to move the white king closer.
-finally, rule 5 says that if it is possible to checkmate it is good to do so.
-It should be noted that thanks to the implicit parts of the policy the king will never be left tied up and unprotected, stalemate will never occur and the white king will always be placed and remain in a line that is between the lines of the kings, whether rows or columns.
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  K.... # K.... # K.... # ..... # ..... # ..... # ..... # ..... # ..... #
-  ..Q.. # ..... # ..... # ..K.. # ..K.. # ..K.. # ..... # ..... # ..... #
-  ..... # ..... # ..... # ..... # ..... # ..... # ..K.. # ..K.. # ..K.. #
-  ..... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # ...Q. #
-  ....k # ....k # ...k. # ...k. # ..k.. # ...k. # ...k. # ....k # ....k #
-\end{Verbatim}
-
-\subsection{Checkmate in n with Rook}
-\subsubsection{Description}
-
-\subsubsection{Training instances}
-\begin{Verbatim}[fontsize=\footnotesize]
-  # .  k  .  .  K #
-  # .  .  .  .  . #
-  # .  .  .  .  . #
-  # R  .  .  .  . #
-  # .  .  .  .  . #
-\end{Verbatim}
-
-\subsubsection{Features}
-\begin{Verbatim}[fontsize=\footnotesize]
-  (CM) Atom[checkmate] [k=1]
-  (SM) Atom[stalemate] [k=1]
-  (QbK) Atom[white_rook_between_kings] [k=1]
-  (KE) Atom[black_king_closed_in_edge_by_white_rook] [k=1]
-  (KD) Dist[cell-has-white_king;adjacent_cell;cell-has-black_king] [k=4]
-  (BKhA) Bool[And(cell-attaked-by-black_king,Not(cell-attaked-by-white))] [k=4]
-  (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_rook))] [k=4]
-  (WQadjBK_row) Bool[And(row-has-white_rook,Exists(adjacent_row,row-has-black_king)))] [k=6]
-  (WQadjBK_col) Bool[And(col-has-white_rook,Exists(adjacent_col,col-has-black_king)))] [k=6]
-  (WQadjBK) Bool[And(cell-has-white_rook,Exists(adjacent_cell,cell-has-black_king)))] [k=6]
-  (WQadjWK) Bool[And(cell-has-white_rook,Exists(adjacent_cell,cell-has-white_king)))] [k=6]
-\end{Verbatim}
-
-\subsubsection{All Transition Features}
-This features reason about how the value of the features can change in all possible successors.
-\begin{Verbatim}[fontsize=\footnotesize]
-  (CA) Bool[can(A, DEC)] [k=2]
-  (CCM) bool[can(CM, INC)] [k=2]
-\end{Verbatim}
-
-\subsubsection{Feature Description}
-$CM$. Checkmate\\
-$SM$. Stalemate\\
-$KE$. Black king is closed in an edge of the table by the white queen\\
-$QbK$. White queen is somewhere between kings, rows or columns\\
-$A$. The number of cells attaked by black king and not attacked by white queen\\
-$BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
-$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK$ AND $WQadjWK$\\
-$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row$ OR $WQadjWK_col$\\
-$CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\
-$CCM$. It is possible to do checkmate in the current state
-
-\subsubsection{Policy}
-  \begin{Verbatim}[fontsize=\footnotesize]
-   1. KE=0, CA>0 -> {A ↓}
-   2. KE=0, CA=0 -> {A ·, KD ·}
-   3. BKhA=0, WQadjBK_line>0 -> {KD ·, WQadjBK_line ·}
-   4. CCM=0, KE>0 -> {KD ↓}
-   5. CCM=1 -> {CM ↑}
-  \end{Verbatim}
-
-\subsubsection{Policy Implicits}
-The next features has to be in that certain value after the transition for classifing the transition as good, taking into account the policy rules.
-  \begin{Verbatim}[fontsize=\footnotesize]
-   Qaw=0, Qbk>0, SM=0
-  \end{Verbatim}
-
-\subsubsection{Policy description}
-Rules 1 and 2 cover the cases in which the king is not enclosed in an edge of the file.
-The first rule states that it is good to take transitions that decrease the number of squares available to the black king by using the queen.
-The second rule says that if the first rule is not applicable it is good to take transitions that do not alter the number of squares available to the black king, without moving the white king.
-The third rule refers to those cases where the black king had moved to its only free square, and classifies as good those transitions in which the queen is moved so that it is not stalemate and remains on the line adjacent to the black king.
-Rule four covers cases in which the black king is locked on an edge by the queen, and it is good to move the white king closer.
-finally, rule 5 says that if it is possible to checkmate it is good to do so.
-It should be noted that thanks to the implicit parts of the policy the king will never be left tied up and unprotected, stalemate will never occur and the white king will always be placed and remain in a line that is between the lines of the kings, whether rows or columns.
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  K.... # K.... # K.... # ..... # ..... # ..... # ..... # ..... # ..... #
-  ..Q.. # ..... # ..... # ..K.. # ..K.. # ..K.. # ..... # ..... # ..... #
-  ..... # ..... # ..... # ..... # ..... # ..... # ..K.. # ..K.. # ..K.. #
-  ..... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # ...Q. #
-  ....k # ....k # ...k. # ...k. # ..k.. # ...k. # ...k. # ....k # ....k #
-\end{Verbatim}
-
 \subsection{Checkmate in one with Queen}
@@
 
+%\subsection{Checkmate in n with Rook}
+%\subsubsection{Description}
+
+%\subsubsection{Training instances}
+%\begin{Verbatim}[fontsize=\footnotesize]
+%  # .  k  .  .  K #
+%  # .  .  .  .  . #
+%  # .  .  .  .  . #
+%  # R  .  .  .  . #
+%  # .  .  .  .  . #
+%\end{Verbatim}
+
+%\subsubsection{Features}
+%\begin{Verbatim}[fontsize=\footnotesize]
+%  (CM) Atom[checkmate] [k=1]
+%  (SM) Atom[stalemate] [k=1]
+%  (QbK) Atom[white_rook_between_kings] [k=1]
+%  (KE) Atom[black_king_closed_in_edge_by_white_rook] [k=1]
+%  (KD) Dist[cell-has-white_king;adjacent_cell;cell-has-black_king] [k=4]
+%  (BKhA) Bool[And(cell-attaked-by-black_king,Not(cell-attaked-by-white))] [k=4]
+%  (A) Num[And(cell-attaked-by-black_king,Not(cell-attaked-by-white_rook))] [k=4]
+%  (WQadjBK_row) Bool[And(row-has-white_rook,Exists(adjacent_row,row-has-black_king)))] [k=6]
+%  (WQadjBK_col) Bool[And(col-has-white_rook,Exists(adjacent_col,col-has-black_king)))] [k=6]
+%  (WQadjBK) Bool[And(cell-has-white_rook,Exists(adjacent_cell,cell-has-black_king)))] [k=6]
+%  (WQadjWK) Bool[And(cell-has-white_rook,Exists(adjacent_cell,cell-has-white_king)))] [k=6]
+%\end{Verbatim}
+
+%\subsubsection{All Transition Features}
+%This features reason about how the value of the features can change in all possible successors.
+%\begin{Verbatim}[fontsize=\footnotesize]
+%  (CA) Bool[can(A, DEC)] [k=2]
+%  (CCM) bool[can(CM, INC)] [k=2]
+%\end{Verbatim}
+
+%\subsubsection{Feature Description}
+%$CM$. Checkmate\\
+%$SM$. Stalemate\\
+%$KE$. Black king is closed in an edge of the table by the white queen\\
+%$QbK$. White queen is somewhere between kings, rows or columns\\
+%$A$. The number of cells attaked by black king and not attacked by white queen\\
+%$BKhA$. Exist a cell attaked by Black king and no attacked by white pieces\\
+%$Qaw$. White queen is attaked and without protection, i.e. $WQadjBK$ AND $WQadjWK$\\
+%$WQadjBK_line$. White queen is in an adjacent line to the black king, i.e. $WQadjBK_row$ OR $WQadjWK_col$\\
+%$CA$. It is possible to decrease the number of cells attaked by black king and not attacked by white queen\\
+%$CCM$. It is possible to do checkmate in the current state
+
+%\subsubsection{Policy}
+%  \begin{Verbatim}[fontsize=\footnotesize]
+%   1. KE=0, CA>0 -> {A ↓}
+%   2. KE=0, CA=0 -> {A ·, KD ·}
+%   3. BKhA=0, WQadjBK_line>0 -> {KD ·, WQadjBK_line ·}
+%   4. CCM=0, KE>0 -> {KD ↓}
+%   5. CCM=1 -> {CM ↑}
+%  \end{Verbatim}
+
+%\subsubsection{Policy Implicits}
+%The next features has to be in that certain value after the transition for classifing the transition as good, taking into account the policy rules.
+%  \begin{Verbatim}[fontsize=\footnotesize]
+%   Qaw=0, Qbk>0, SM=0
+%  \end{Verbatim}
+
+%\subsubsection{Policy description}
+%Rules 1 and 2 cover the cases in which the king is not enclosed in an edge of the file.
+The first rule states that it is good to take transitions that decrease the number of squares available to the black king by using the queen.
+The second rule says that if the first rule is not applicable it is good to take transitions that do not alter the number of squares available to the black king, without moving the white king.
+The third rule refers to those cases where the black king had moved to its only free square, and classifies as good those transitions in which the queen is moved so that it is not stalemate and remains on the line adjacent to the black king.
+Rule four covers cases in which the black king is locked on an edge by the queen, and it is good to move the white king closer.
+finally, rule 5 says that if it is possible to checkmate it is good to do so.
+It should be noted that thanks to the implicit parts of the policy the king will never be left tied up and unprotected, stalemate will never occur and the white king will always be placed and remain in a line that is between the lines of the kings, whether rows or columns.
+
+%\subsubsection{Example of Game}
+%\begin{Verbatim}[fontsize=\footnotesize]
+%  K.... # K.... # K.... # ..... # ..... # ..... # ..... # ..... # ..... #
+%  ..Q.. # ..... # ..... # ..K.. # ..K.. # ..K.. # ..... # ..... # ..... #
+%  ..... # ..... # ..... # ..... # ..... # ..... # ..K.. # ..K.. # ..K.. #
+%  ..... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # Q.... # ...Q. #
+%  ....k # ....k # ...k. # ...k. # ..k.. # ...k. # ...k. # ....k # ....k #
+%\end{Verbatim}
+
 \newpage
 
+\section{Dealing with real robots}
+
+First it is necessary to have a simulator of the robot's environment discretised.
+The policy would be learned with the algorithm described in the paper without involving the robot.
+This policy is learned from a single instance in the simulator, and can then be run on different and larger instances of the domain.
+Once the policy is learned with the simulator and the algorithm, it is only necessary to translate the state where the robot is into a state that can be executed by the simulator.
+Then a transition is selected as good using the already learned policy, and the policy returns the action executed in the simulator to take that transition.
+The robot controller must be able to handle executing these actions in the real world.
+This process is repeated until the goal is reached.
+
+So, to be able to execute the policies on real robots, it is only necessary to have a simulator and an algorithm to translate the state of the robot into a state executable by the simulator.
+
+For example, with a turtle robot that has to pick up a certain number of packages and take them to a certain place.
+We only need a grid simulator, where the objects "package", "agent" and "destination" exist.
+The simulator must be able to execute the actions to move the robot, pick and drop.
+The strategy that we would learn with the simulator and our algorithm would be the same as the one learned in the "Delivery" domain, in the results section.
+The robot controller should be able to cope with executing the actions output by the algorithm, and ideally end up in the state that the simulator expects.
+
+Of course, you could give the initial state translated to the simulator and have the learned policy execute a sequence of actions up to the goal.
+But this method makes us more vulnerable to the noise that the real world produces.
+
 \subsection{Conclusions}
 
-\subsection{Discussoin of Results}
-
-\subsection{Discussoin of Results}
+\subsection{Discussion}
 

### 2021-08-04 doc/paper/paper.tex
doc updated

@@
 Generalized planning is concerned with the computation of general policies that solve multiple instances of a planning domain all at once.
-It has been recently shown that these policies can be computed in two steps: first, a suitable abstraction in the form of a qualitative numerical planning problem (QNP) is learned from sample plans, then the general policies are obtained from the learned QNP using a planner.
-In this work, we introduce an alternative approach for computing more expressive general policies which does not require sample plans or a QNP planner.
-The new formulation is very simple and can be cast in terms that are more standard in machine learning: a large but finite pool of features is defined from the predicates in the planning examples using a general grammar, and a small subset of features is sought for separating “good” from “bad” state transitions, and goals from non-goals.
-The problems of finding such a “separating surface” while labeling the transitions as “good” or “bad” are
-jointly addressed as a single combinatorial optimization problem expressed as a Weighted Max-SAT problem.
-The advantage of looking for the simplest policy in the given feature space that solves the given examples, possibly non-optimally, is that many domains have no general, compact policies that are optimal.
-The approach yields general policies for a number of benchmark adversarial domains, even when non-determinism exists in the adverary turn.
+It has been recently shown how these policies can be computed and we adress the problem of computing general policies for multi-agent settings.
+These policies can be computed in two steps: first, a suitable abstraction in the form of a qualitative numerical planning problem (QNP) is learned from sample plans, then the general policies are obtained from the learned QNP using a planner.
+We introduce an alternative approach for computing more expressive general policies in multi-agent settings which does not require sample plans or a QNP planner.
+The new formulation is very simple and can be cast in terms that are more standard in machine learning: a large but finite pool of features (functions) is defined from the predicates in the planning examples using a general grammar, and a small subset of features is sought for separating “good” from “bad” state transitions, and goals from non-goals.
+The problems of finding such a “separating surface” while labeling the transitions as “good” or “bad” are jointly addressed as a single combinatorial optimization problem expressed as a Weighted Max-SAT problem.
+The advantage of looking for the simplest policy in the given feature space that solves the given examples, possibly non-optimally, is that many domains have no general policies that are optimal.
+We assume that the state space is discrete and also that we know what actions the opponents can take in their turn.
+The approach yields general policies for a number of benchmark adversarial domains.
 We use a uniform grammar for all the grid domains capable of capturing the domain representations.
+We introduce the possibility to use actions to reduce the number of features used to distinguish one transition from another, in case the action space does not change from one instance of the domain to another.
+In case the action space changes from one instance to another we simply ignore the actions used.
 These policies can be interpreted qualitatively, explained, and it can be shown mathematically that they will solve all possible instances within a class of problems.
 This is an advantage when making manual policy changes.
-We also show an example of how the explainable policies produced by our algorithm can be applied to real robots.
 
@@
 
-Generalized planning is concerned with the computation of general policies or plans that solve multiple instances of a given planning domain all at once (Srivastava, Immerman, and Zilberstein 2008; Bonet, Palacios, and Geffner 2009; Huand De Giacomo 2011; Belle and Levesque 2016; Segovia, Jim´enez, and Jonsson 2016).
+Generalized planning is concerned with the computation of general policies or plans that solve multiple instances of a given planning domain all at once~\cite{srivastava2008network, ramirez2009plan, belle2016foundations, aguas2016generalized}.
 If the instances share the same strategy, it doesn't matter how different they are.
-For example, in an environment where an agent has to pick up a key and then approach a door and it will open, the strategy is to approach the key, pick it up, and then approach the door in order to open it.
+For instance, in an environment where an agent has to pick up a key and then approach a door and it will open, the strategy is to approach the key, pick it up, and then approach the door in order to open it.
 In this example it does not matter how large the environment is and how many actions the agent has to take, since the strategy does not change.
@@
 The key question in generalized planning is how to represent and compute such general plans from the domain representation.
-This was solved by [], for non-adversarial and deterministic domains but not for adversarial domains, where you cannot control what the adversary will do during his turn.
-However, there are adversarial domains where the agent can take actions that no matter what happens in the environment the agent wins.
+This was solved by \cite{frances2021learning}, for single agent settings and deterministic domains but not for multi-agent settings, where you cannot control what the other agents will do during their turn.
+However, we deal with adversarial domains where the agent can take actions that no matter what happens in the environment the agent can win.
 For instance, if we are in a domain where an agent must chase an adversary, and the adversary can run slower than the agent, the strategy will be to decrease the distance between them until the agent can catch him.
-This we know is a winning strategy where it does not matter what the adversary does.
-
-This was solved by [], for non-adversarial and deterministic domains but not for adversarial domains, where you cannot control what the adversary will do during his turn.
-However, there are adversarial domains where you can take actions that no matter what happens in the environment you win.
-For example, if we are in a domain where an agent must chase an adversary, and the adversary can run slower than the agent, the strategy will be to decrease the distance between them until the agent can catch him.
-This we know is a winning strategy where it does not matter what the adversary does.
-Nor will the size of the environment, the distance or the position of the agent and the adversary matter.
-
-In one of the most general formulations, general policies are obtained from an abstract planning model expressed as a qualitative numerical planning problem or QNP (Srivastava et al.
-2011).
+We know this is a winning strategy where it does not matter what the adversary does, the agent will win
+
+In one of the most general formulations, general policies are obtained from an abstract planning model expressed as a qualitative numerical planning problem or QNP~\cite{srivastava2008network}.
 A QNP is a standard STRIPS planning model extended with non-negative numerical variables that can be decreased or increased “qualitatively”; i.e., by uncertain positive amounts, short of making the variables negative.
-Unlike standard planning with numerical variables (Helmert 2002), QNP planning is decidable, and QNPs can be compiled in polynomial time into fully observable non-deterministic (FOND) problems (Bonet and Geffner 2020)
+Unlike standard planning with numerical variables~\cite{helmert2002decidability}, QNP planning is decidable, and QNPs can be compiled in polynomial time into fully observable non-deterministic (FOND) problems~\cite{bonet2020high}.
 
 The main advantage of the formulation of generalized planning based on QNPs is that it applies to standard relational domains where the pool of (ground) actions change from instance to instance.
+However, in our apporach there is also the possibility to take advantage of actions if they do not change from one instance to another.
 On the other hand, while the planning domain is assumed to be given, the QNP abstraction is not, and hence it has to be written by hand or learned.
-This is the approach of Bonet, Francés, and Geffner (2019) where generalized plans are obtained by learning the QNP abstraction from the domain representation and sample plans, and then solving the abstraction with a QNP planner.
-
-In this work, we build on this thread but introduce an alternative approach for computing general policies that is simpler, yet more powerful.
+This is the approach of~\cite{DBLP:conf/aaai/BonetFG19} where generalized plans are obtained by learning the QNP abstraction from the domain representation and sample plans, and then solving the abstraction with a QNP planner.
+
+We take inspiration from the work mentioned above, but introduce an alternative approach for computing general policies in multi-agent setting that is simpler.
 The learning problem is cast as a self-supervised classification problem where (1) a pool of features is automatically generated from a uniform grammar applied to the domain predicates, and (2) a small subset of features is sought for separating “good” from “bad” state transitions, and goals from non-goals.
@@
 
-\subsection{Generalized Planning}
+The computation of general plans from domain encodings and sample plans has been addressed in a number of works~\cite{cui2019stochastic, fern2003approximate, silver2020pddlgym}.
+Generalized planning has also been formulated as a problem in first-order logic~\cite{srivastava2011environment, on2019symbolic}, and general plans over finite horizons have been derived using first-order regression~\cite{boutilier2001symbolic, wang2008first, sanner2009practical}.
+More recently, general policies for planning have been learned from PDDL domains and sample plans using deep learning~\cite{toyer2018action, gargmausam}.
+Deep reinforcement learning methods~\cite{mnih2015human} have also been used to generate general policies from images without assuming prior symbolic knowledge~\cite{groshev2018learning,hui2020babyai}, in certain cases accounting for objects and relations through the use of suitable architectures~\cite{garnelo2019reconciling}.
+Our work  is closest to the works of~\cite{frances2021learning}.
+The first provides a model-based approach to generalized planning where an abstract QNP model is learned from the domain representation and sample instances and plans, which is then solved by a QNP planner~\cite{bonet2020general}.
+The second learns a generalized value function in an unsupervised manner, under the assumption that this function is linear.
+Model-based approaches have an advantage over inductive approaches that learn generalized plans; like logical approaches, they guarantee that the resulting policies (conclusions) are correct provided that the model (set of premises) is correct.
+The approach developed in this work does not make use of QNPs or planners but inherits these formal properties.
+The problem of generalisation in adversarial domains has been studied recently in~\cite{zhang2021understanding, subramani2020learning} from the perspective of reinforcement learning, trying to address the problem of transferability.
+
+\section{Contriution: Generalized Planning in multi-agent settings}
 
 A key question in generalized planning is how to represent general plans or policies when the different instances to be solved have different sets of objects and ground actions.
-One solution is to work with general features (functions) that have well defined values over any state of any possible domain instance, and think of general policies $\pi$ as mappings from feature valuations into abstract actions that denote changes in the feature values (Bonet and Geffner 2018).
-In this work, we build on this intuition but avoid the introduction of abstract actions (Bonet and Geffner 2021).
+We take inspiration of the work of~\cite{frances2021learning} and we extend it to multi-agent domains.
+One solution is to work with general features (functions) that have well defined values over any state of any possible domain instance, and think of general policies $\pi$ as mappings from feature valuations into abstract actions that denote changes in the feature values~\cite{bandres2018planning}.
+When a transition is taken by the agent the environment or other agent changes state, so when we record the AND/OR graph of states we capture how the environment or the other agent can change each state.
+In this work, we use abstract actions as~\cite{frances2021learning}, in addition to the possibility of taking advantage of using an action space fixed for all instances in the domain.
+The approach is SAT-based, so first we will define the variables and encoding, and then how we learn general policies.
+
+\section{Action Space}
+
+In the work of~\cite{frances2021learning} it was assumed that the set of actions was not fixed in all instances and abstruse actions were always used.
+In cases where the action set was fixed across all instances this information was simply ignored.
+There are some domains where it is useful to take advantage of fixed action sets, where in a certain abstract state it will always be good to do a certain action.
+We have implemented two ways to take advantage of a fixed set of actions.
+(1) Have policies where we reason about the value of features in a state, and whether at that value it is good to take an action $a$.
+(2) Have policies where we take into account the fixed set of actions and reason about the change of feature values in a transition, to put the two concepts together we only differentiate transitions where the actions are the same.
+
+\subsection{Features}
+
+Let us have a pool of features $f$.
+Where $f$ is a function that has as input a state and as output a numerical value.
+The initial feature pool is produced using the logical description language.
+In addition, a parameter is used to determine the maximum complexity of the features.
+Once the initial pool of features is produced, a pruning is performed based on the denotation of each feature with the following philosophy: if two features, $f$ and $f'$ have the same denotation in all states, it is likely that they are capturing the same information of the domain, therefore we keep the simpler of the two features.
+With these features you can basically create abstract states, or representations, the challenge will be to find which ones are useful to represent the strategy that solves the problem.
+After feature pruning, the set of features $f$ that we are left with is $F$, and it is the one that will have the SAT solver as input.
+Based on the encoding the SAT solver will select the features of $F$ needed to represent the policy, trying to minimize the complexity.
 
@@
        transitions starting in $s$ in that instance appear in $T$ too.
- \item A set $adv(s)$ of all possible moves by the adversary on state $s$.
+ \item A set $adv(s)$ of all possible moves by the adversary~\footnote{Second agent that plays the game} on state $s$.
 
@@
 
+\subsubsection{Terminology}
+
+A state is called \emph{reachable} if there is a path to it from $s_0$, and it is called \emph{solvable} if there is a path from it to a goal state.
+A state is \emph{alive} if it is solvable, reachable and not a goal state~\cite{frances-et-al-ijcai2019}.
+We use $T$ to denote the set of all transitions $(s, s')$ in the training sample such that $s$ is alive.
+
 \subsubsection{Hard Constraints}
+
+The constraints recognize good state transitions, the distance from an state to the goal, and distinguish good and bad states.
 
@@
 \smallpar{C2} $V$ is always descending along Good actions, \textbf{taking into account all possible adversary responses}.
-For each $(s, a, s')$ in the set of non-deterministic transitions
-such that both $s$ and $s'$ are alive, post:
+For each $(s, a, s')$ in the set of non-deterministic transitions such that both $s$ and $s'$ are alive, where all possible $s''$ are alive, where $s''$ is the result of the adversary transforming $s'$ into $s''$ by executing $a'$, post:
 %Good(s, a) \land V(s, k) \rightarrow \bigvee_{1 \leq k' \leq k} V(s', k'),&\;\; \text{for } k \in [1, D].
@@
 \end{itemize}
-
 Additionally, if \texttt{action\_labels = use$_1$} or \texttt{action\_labels = use$_2$}, then
@@
 
+\subsection{Constraints Description}
+
+How we arrive at these constrains has to do with the observation of adversarial domains and winning strategies.
+We observed that the dilemma of adversarial games meant that we were confronted with the fact that decisions were not made by a single agent, and we had to take into account that there were also other agents trying to "win".
+Moreover, this meant that in many domains we were faced with scalability problems.
+
+During policy learning, it does not matter which agents have been played against to learn the policy, as all their possible actions in each state will be taken into account when expanding the state space.
+
+We observed that in many domains the set of actions is fixed for all agents.
+In the paper~\cite{frances2021learning} there were $Good(s, s')$ variables.
+But these were not able to take advantage of fixed action sets, so we decided to include the information of the actions in these domains to alleviate scalability problems, for that reason we have variables such as $Good(s, a, s')$.
+ This allows us to reduce the number of C4 clauses.
+
+It was assumend by~\cite{frances2021learning} assumed that it was possible to get from any state of the problem to the objective, without entering dead ends (states where the agent has lost).
+However, in many multi-agent domains there are states where the agent has not lost, but no longer has the possibility of winning in that state no matter what the agent does.
+That is why we included the $Bad(s)$ variables, so that there could be states without any actions that lead to a path where the agent always wins.
+However, in our approach, if from a certain state there is a strategy that can be represented with the logic language and that always wins over the rest of the agents, we guarantee that we will find it.
+However, allowing the use of $Bad(s)$ variables is optional, through~$\texttt{allow\_bad\_states}$, since there are domains where we know that there is a winning strategy from any state.
+
+In C1 it can be understood that each state must have a possible transition that is good, if ~$\neg\texttt{allow\_bad\_states}$.
+This makes sense for many of the domains, as we want our overall strategy to be able to decide which transition to take in any given state.
+We then design counterin C2 to ensure that the strategy takes paths that do not fall into cycles by introducing the adversarial factor.
+To introduce the adversarial factor into the strategy we make sure that the number assigned to a state $s$ is greater than all the numbers assigned to the possible $s''$.
+The possible $s''$ are the result of the agents or the environment executing an action $a'$ on $s'$, where $s'$ is the state the agent reaches after executing $a$ on $s$.
+Note that adversaries will often have multiple $a'$ actions to execute on $s'$.
+We then design counterin C2 to ensure that the strategy takes paths that do not fall into cycles by introducing the adversarial factor.
+To introduce the adversarial factor into the strategy we make sure that the number assigned to a state $s$ is greater than all the numbers assigned to the possible $s''$.
+The possible $s''$ are the result of the agents or the environment executing an action $a'$ on $s'$, where $s'$ is the state the agent reaches after executing $a$ on $s$.
+Note that adversaries will often have multiple $a'$ actions to execute on $s'$, which will often result in a different set of $s"$..
+
 \pagebreak
-
-\section{Terminology}
-A state is called \emph{reachable} if there is a path to it from $s_0$, and
-it is called \emph{solvable} if there is a path from it to a goal
-state.
-A state is \emph{alive} if it is solvable, reachable and not a
-goal state~\cite{frances-et-al-ijcai2019}.
-We use $T$ to denote the set of all transitions $(s, s')$ in the training sample such that $s$ is alive.
 
@@
 To check that the policy is complete, it is tested on all possible, for each board size $NxM$ where both $N$ and $M$ are numbers no greater than twenty randomly selected.
-v
+
 \subsubsection{Example of Game}
@@
 
-\section{Dealing with real robots}
+\subsection{Dealing with real robots}
 
@@
 
+\subsection{Noisy adversaries}
+
+Note that for the algorithm to work it must be possible to win from the initial state of the problem no matter what the opponent does.
+So in domains where the agent has two actions per turn, which are "Space Invader" and "Delivery".
+If both players have one action per turn the agent's strategy does not change.
+Therefore in some domains the learned policy can deal with a noisy adversary even though it has not been learned by playing against him.
+
 \subsection{Conclusions}
 
-\subsection{Discussion}
+It is possible to learn policies unsupervised in small instances and transfer them to larger instances in the same domain.
+We can conclude from this that it is correctly learning the problem representation and a strategy capable of winning on a number of instances.
+Depending on the domains it is possible to create a common language for all, making the approach less domain dependent, although as we see in this work the language is focused on problems that are in two-dimensional grids.
+A requirement for the algorithm to work correctly is that the strategy can be described using the grammar, then in domains where the strategy is very complex it will be necessary to increase the complexity of the language.
+In this paper we propose a method for dealing with adversarial domains, which manages to find policies that beat the adversary from any initial state where this is possible.
+This approach is a step in the explainability of reinforcement-produced policies, and it is also a step towards having transferable policies that capture the representation of the problem.
+
+%\subsection{Discussion}
 

### 2021-08-30 doc/AAMAS-2022 Formatting Instructions/sample.tex
doc update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% LaTeX Template for AAMAS-2022 (based on sample-sigconf.tex)
%%% Prepared by Ana L. C. Bazzan and Lucas N. Alegre, with the contribution of the AAMAS-2022 Program Chairs. Thanks to Natasha Alechina. (version 2022-07-08)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Start your document with the \documentclass command.
%%% Use the first variant below for the final paper.
%%% Use the second variant below for submission.

\documentclass[sigconf]{aamas} 
%\documentclass[sigconf,anonymous]{aamas}

%%% Load required packages here (note that many are included already).

\usepackage{balance} % for balancing columns on the final page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% AAMAS-2022 copyright block (do not change!)

\setcopyright{ifaamas}
\acmConference[AAMAS '22]{Proc.\@ of the 21st International Conference
on Autonomous Agents and Multiagent Systems (AAMAS 2022)}{May 9--13, 2022}
{Auckland, New Zealand}{P.~Faliszewski, V.~Mascardi, C.~Pelachaud,
M.E.~Taylor (eds.)}
\copyrightyear{2022}
\acmYear{2022}
\acmDOI{}
\acmPrice{}
\acmISBN{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Use this command to specify your EasyChair submission number.
%%% In anonymous mode, it will be printed on the first page.

\acmSubmissionID{???}

%%% Use this command to specify the title of your paper.

\title[AAMAS-2022 Formatting Instructions]{Formatting Instructions for the 21st International Conference on Autonomous Agents and Multiagent Systems}

%%% Provide names, affiliations, and email addresses for all authors.

\author{Samwise Gamgee}
\affiliation{
  \institution{Long Journey University}
  \city{Eriador}
  \country{New Zealand}}
\email{samwise.gamgee@lju.nz}

\author{Merry Brandybuck}
\affiliation{
  \institution{The Ring Company Inc.}
  \city{Lindon}
  \state{The Great Land}
  \country{New Zealand}}
\email{merry@ring.com}

\author{Frodo Baggins}
\affiliation{
  \institution{Two Towers University}
  \city{Rohan}
  \country{New Zealand}}
\email{frodo.baggins@2tu.nz}

%%% Use this environment to specify a short abstract for your paper.

\begin{abstract}
This document outlines the formatting instructions for submissions to
AAMAS-2022. You can use its source file as a template when writing 
your own paper. It is based on the file `\texttt{sample-sigconf.tex}'
distributed with the ACM article template for \LaTeX\@.
\end{abstract}

%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
%%% Please replace this example with code appropriate for your own paper.

%%% Use this command to specify a few keywords describing your work.
%%% Keywords should be separated by commas.

\keywords{Auction Theory, Reinforcement Learning, Social Simulation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Include any author-defined commands here.

\newcommand{\BibTeX}{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%% The following commands remove the headers in your paper. For final 
%%% papers, these will be inserted during the pagination process.

\pagestyle{fancy}
\fancyhead{}

%%% The next command prints the information defined in the preamble.

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

This document explains the main features of the `\texttt{aamas}' 
document class, which is essentially identical to the `\texttt{acmart}'
document class provided by the ACM. The only difference is a minor 
modification to allow for the correct copyright attribution to IFAAMAS.
For detailed documentation of the original document class, please refer
to the relevant website maintained by the~ACM:
%
\begin{center}
\url{https://www.acm.org/publications/proceedings-template}
\end{center}
%
The first command in your source file should be either one of these:
\begin{verbatim}
    \documentclass[sigconf]{aamas}
    \documentclass[sigconf,anonymous]{aamas}
\end{verbatim}
%
The first variant should be used for final papers. The second should be
used when you submit your paper for blind review; it will replace the 
names of the authors with the submission number.

Make sure your paper includes the correct copyright information and 
the correct specification of the \emph{ACM Reference Format}. Both of 
these will be generated automatically if you include the correct 
\emph{copyright block} as shown in the source file of this document.

Modifying the template---e.g., by changing margins, typeface sizes, 
line spacing, paragraph or list definitions---or making excessive use 
of the `\verb|\vspace|' command to manually adjust the vertical spacing 
between elements of your work is not allowed. You risk getting your 
submission rejected (or your final paper excluded from the proceedings) 
in case such modifications are discovered. The `\texttt{aamas}' document 
class requires the use of the \textit{Libertine} typeface family, which 
should be included with your \LaTeX\ installation. Please do not use 
other typefaces instead.

Please consult the \emph{Call for Papers} for information on matters 
such as the page limit or anonymity requirements. It is available from
the conference website:
%
\begin{center}
\url{https://aamas2022-conference.auckland.ac.nz/}   
\end{center}
%
To balance the columns on the final page of your paper, use the 
`\texttt{balance}' package and issue the `\verb|\balance|' command
 somewhere in the text of what would be the first column of the last 
 page without balanced columns. This will be required for final papers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Preamble}

You will be assigned a submission number when you register the abstract 
of your paper on \textit{EasyChair}. Include this number in your 
document using the `\verb|\acmSubmissionID|' command.

Then use the familiar commands to specify the title and authors of your
paper in the preamble of the document. The title should be appropriately 
capitalised (meaning that every `important' word in the title should 
start with a capital letter). For the final version of your paper, make 
sure to specify the affiliation and email address of each author using 
the appropriate commands. Specify an affiliation and email address 
separately for each author, even if two authors share the same 
affiliation. You can specify more than one affiliation for an author by 
using a separate `\verb|\affiliation|' command for each affiliation.

Provide a short abstract using the `\texttt{abstract}' environment.

Finally, specify a small number of keywords characterising your work, 
using the `\verb|\keywords|' command.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Body of the Paper}

For help with typesetting the body of your paper in \LaTeX\@, please 
make use of the familiar resources~\cite{Lam94}. In this section we 
merely highlight a few specific features.

\subsection{Mathematical Expressions}

You can typeset all sorts of in-line mathematical expressions 
with the usual \verb|$...$| construct, as in 
$\Diamond\Diamond\varphi \rightarrow \Diamond\varphi$ or 
$\boldsymbol{R} = (R_1,\ldots,R_n)$.
For more complex expressions, it may often be preferable to use one of
the various equation-type environments available in \LaTeX\@, as shown 
in the following example:
%
\begin{eqnarray}
Z_i & = & \frac{u_i(x_i) - u_i(x_{-i})}{u_i(x_i)}
\end{eqnarray}
%
Here is a second example for an equation: 
%
\begin{eqnarray}\label{eq:vcg}
p_i(\boldsymbol{\hat{v}}) & = &
\sum_{j \neq i} \hat{v}_j(f(\boldsymbol{\hat{v}}_{-i})) - 
\sum_{j \neq i} \hat{v}_j(f(\boldsymbol{\hat{v}})) 
\end{eqnarray}
%
Use the usual combination of `\verb|\label|' and `\verb|\ref|' to refer
to numbered equations, such as Equation~(\ref{eq:vcg}) above. Of course,
introducing numbers in the first place is only helpful if you in fact 
need to refer back to the equation in question elsewhere in the paper.

\subsection{Tables and Figures}

Use the `\texttt{table}' environment (or its variant `\texttt{table*}')
in combination with the `\texttt{tabular}' environment to typeset tables
as floating objects. The `\texttt{aamas}' document class includes the 
`\texttt{booktabs}' package for preparing high-quality tables. Tables 
are often placed at the top of a page near their initial cite, as done 
here for Table~\ref{tab:locations}.

\begin{table}[t]
  \caption{Locations of the first five editions of AAMAS}
  \label{tab:locations}
  \begin{tabular}{rll}\toprule
    \textit{Year} & \textit{City} & \textit{Country} \\ \midrule
    2002 & Bologna & Italy \\
    2003 & Melbourne & Australia \\
    2004 & New York City & USA \\
    2005 & Utrecht & The Netherlands \\
    2006 & Hakodate & Japan \\ \bottomrule
  \end{tabular}
\end{table}

The caption of a table should be placed \emph{above} the table. 
Always use the `\verb|\midrule|' command to separate header rows from 
data rows, and use it only for this purpose. This enables assistive 
technologies to recognise table headers and support their users in 
navigating tables more easily.

%%% The following command should be issued somewhere in the first column 
%%% of the final page of your paper.
\balance

Use the `\texttt{figure}' environment for figures. If your figure 
contains third-party material, make sure to clearly identify it as such.
Every figure should include a caption, and this caption should be placed 
\emph{below} the figure itself, as shown here for Figure~\ref{fig:logo}.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\linewidth]{aamas2022Logo}
  \caption{The logo of AAMAS 2022}
  \label{fig:logo}
  \Description{Logo of AAMAS 2022 -- The 21st International Conference on Autonomous Agents and Multiagent Systems.}
\end{figure}

In addition, every figure should also have a figure description, unless
it is purely decorative. Use the `\verb|\Description|' command for this 
purpose. These descriptions will not be printed but can be used to 
convey what's in an image to someone who cannot see it. They are also 
used by search engine crawlers for indexing images, and when images 
cannot be loaded. A figure description must consist of unformatted plain 
text of up to 2000~characters. For example, the definition of 
Figure~\ref{fig:logo} in the source file of this document includes the 
following description: ``Logo of the IFAAMAS -- The  International Foundation for Autonomous Agents and Multiagent Systems.'' For more information on how best to write figure descriptions 
and why doing so is important, consult the information available here: 
%
\begin{center}
\url{https://www.acm.org/publications/taps/describing-figures/}
\end{center}
%
The use of colour in figures and graphs is permitted, provided they 
remain readable when printed in greyscale and provided they are 
intelligible also for people with a colour vision deficiency.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Citations and References}

The use of the \BibTeX\ to prepare your list of references is highly 
recommended. To include the references at the end of your document, put 
the following two commands just before the `\verb|\end{document}|' 
command in your source file:
%
\begin{verbatim}
   \bibliographystyle{ACM-Reference-Format}
   \bibliography{mybibfile}
\end{verbatim}
%
Here we assume that `\texttt{mybibfile.bib}' is the name of your 
\BibTeX\ file. Use the `\verb|\cite|' command to produce citations 
to your references. Here are a few examples for citations of journal 
articles~\cite{GrKr96,WoJe95}, books~\cite{Knu97}, articles in 
conference proceedings~\cite{Hag1993}, technical reports~\cite{Har78},
Master's and PhD theses~\cite{Ani03,Cla85}, online videos~\cite{Oba08}, 
datasets~\cite{AnMC13}, and patents~\cite{Sci09}. Both citations and 
references are numbered by default.

Make sure you provide complete and correct bibliographic information 
for all your references, and list authors with their full names 
(``Donald E.\ Knuth'') rather than just initials (``D.\ E.\ Knuth'').

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% The acknowledgments section is defined using the "acks" environment
%%% (rather than an unnumbered section). The use of this environment 
%%% ensures the proper identification of the section in the article 
%%% metadata as well as the consistent spelling of the heading.

\begin{acks}
If you wish to include any acknowledgments in your paper (e.g., to 
people or funding agencies), please do so using the `\texttt{acks}' 
environment. Note that the text of your acknowledgments will be omitted
if you compile your document with the `\texttt{anonymous}' option.
\end{acks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% The next two lines define, first, the bibliography style to be 
%%% applied, and, second, the bibliography file to be used.

\bibliographystyle{ACM-Reference-Format} 
\bibliography{sample}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-08-30 doc/paper/paper.tex
doc update

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{csquotes}
 
@@
 \usepackage{color}
+\usepackage{hyperref}
 
@@
 
-\title{Self-Supervised Learning of Generalized Policies in adversarial domains}
+\title{Self-Supervised Learning of Generalized Policies in multi-agent domains}
 %Your title must be in mixed case, not sentence case.
@@
 Generalized planning is concerned with the computation of general policies that solve multiple instances of a planning domain all at once.
-It has been recently shown how these policies can be computed and we adress the problem of computing general policies for multi-agent settings.
+Recently, it has been recently shown how these policies can be computed for single-agent settings.
 These policies can be computed in two steps: first, a suitable abstraction in the form of a qualitative numerical planning problem (QNP) is learned from sample plans, then the general policies are obtained from the learned QNP using a planner.
-We introduce an alternative approach for computing more expressive general policies in multi-agent settings which does not require sample plans or a QNP planner.
-The new formulation is very simple and can be cast in terms that are more standard in machine learning: a large but finite pool of features (functions) is defined from the predicates in the planning examples using a general grammar, and a small subset of features is sought for separating “good” from “bad” state transitions, and goals from non-goals.
-The problems of finding such a “separating surface” while labeling the transitions as “good” or “bad” are jointly addressed as a single combinatorial optimization problem expressed as a Weighted Max-SAT problem.
-The advantage of looking for the simplest policy in the given feature space that solves the given examples, possibly non-optimally, is that many domains have no general policies that are optimal.
-We assume that the state space is discrete and also that we know what actions the opponents can take in their turn.
-The approach yields general policies for a number of benchmark adversarial domains.
+We introduce an alternative approach for computing more expressive general policies in multi-agent settings which does not require sample plans nor a QNP planner.
+The new formulation is very simple and can be cast in terms that are more standard in machine learning: a large but finite pool of features (functions) is defined from the predicates in the planning examples using a general grammar, and a small subset of features is sought for separating “good” from “bad” state transitions, as well as goals from non-goals.
+The problem of finding such a ``separating surface'' while labeling the transitions as ``good'' or ``bad'' are jointly addressed as a single combinatorial optimization problem expressed as a Weighted Max-SAT problem.
+As many domains have no general policies that are optimal for all instance, we argue that looking for a simple policy, which might have some performance reduction  is beneficial .
+We assume that the state space is discrete and also that we know what actions the agents can take in their turn.
+The approach yields general policies for a number of benchmark multi-agent domains.
 We use a uniform grammar for all the grid domains capable of capturing the domain representations.
@@
 In case the action space changes from one instance to another we simply ignore the actions used.
+We make use of the minimax algorithm to extend the meaning of an unsolvable state, ensuring that the agent wins from all states where the policy is defined, regardless of what the other agents do.
 These policies can be interpreted qualitatively, explained, and it can be shown mathematically that they will solve all possible instances within a class of problems.
@@
 If the instances share the same strategy, it doesn't matter how different they are.
-For instance, in an environment where an agent has to pick up a key and then approach a door and it will open, the strategy is to approach the key, pick it up, and then approach the door in order to open it.
+For instance, in an environment where an agent has to pick up a key and then go to the door and it will open, the strategy is to approach the key, pick it up, and then approach the door in order to open it.
 In this example it does not matter how large the environment is and how many actions the agent has to take, since the strategy does not change.
@@
 The key question in generalized planning is how to represent and compute such general plans from the domain representation.
-This was solved by \cite{frances2021learning}, for single agent settings and deterministic domains but not for multi-agent settings, where you cannot control what the other agents will do during their turn.
-However, we deal with adversarial domains where the agent can take actions that no matter what happens in the environment the agent can win.
+This was solved by~\cite{frances2021learning}, for single agent settings and deterministic domains, where one agent cannot control what the other agents will do during their turn.
+We take inspiration of~\cite{frances2021learning} to create an approach that is capable of deal with multi-agent domains where the agent can take actions that no matter what happens in the environment the agent can win.
 For instance, if we are in a domain where an agent must chase an adversary, and the adversary can run slower than the agent, the strategy will be to decrease the distance between them until the agent can catch him.
@@
 In one of the most general formulations, general policies are obtained from an abstract planning model expressed as a qualitative numerical planning problem or QNP~\cite{srivastava2008network}.
-A QNP is a standard STRIPS planning model extended with non-negative numerical variables that can be decreased or increased “qualitatively”; i.e., by uncertain positive amounts, short of making the variables negative.
+A QNP is a standard STRIPS planning model~\cite{fikes1971strips, bylander1994computational} extended with non-negative numerical variables that can be decreased or increased “qualitatively”; i.e., by uncertain positive amounts, short of making the variables negative.
 Unlike standard planning with numerical variables~\cite{helmert2002decidability}, QNP planning is decidable, and QNPs can be compiled in polynomial time into fully observable non-deterministic (FOND) problems~\cite{bonet2020high}.
@@
 The main advantage of the formulation of generalized planning based on QNPs is that it applies to standard relational domains where the pool of (ground) actions change from instance to instance.
-However, in our apporach there is also the possibility to take advantage of actions if they do not change from one instance to another.
+For instance, given a domain that is a grid where the actions are clicking a cell given some coordinates, the number of actions would be equal to the number of cells in the grid, then in this case the number of possible actions is different depending on the size and shape of the grid.
 On the other hand, while the planning domain is assumed to be given, the QNP abstraction is not, and hence it has to be written by hand or learned.
@@
 
-We take inspiration from the work mentioned above, but introduce an alternative approach for computing general policies in multi-agent setting that is simpler.
-The learning problem is cast as a self-supervised classification problem where (1) a pool of features is automatically generated from a uniform grammar applied to the domain predicates, and (2) a small subset of features is sought for separating “good” from “bad” state transitions, and goals from non-goals.
-The problems of finding the “separating surface” while labeling the transitions as “good” or “bad” are addressed jointly as a single combinatorial optimization task solved with a Weighted Max-SAT solver.
+In our approach there is also the possibility to take advantage of actions if they do not change from one instance to another.
+For instance if the domain is a grid where the agent has to pick an object, the actions will be "move in some direction" and "pick", then the action space do not change with the size of the grid or the number of objects to be collected.
+The way we take advantage of domains with a fixed action space is by distinguishing with the features only the transitions that are the product of the same action, the mathematical expression of this effect is seen in the encoding section.
+To put it intuitively, let $tx=(s, a, s')$ be a transition from state $s$ to state $s'$ by executing the action $a$ and a transition $tx'=(t, b, t')$.
+If $a=b$ in a fixed action space, and $tx$ is a \emph{good} transition and $tx'$ is a \emph{bad} transition, we want to capture what change has occurred in the features.
+On the other hand, if $a$ is different from $b$ in a fixed action space we do not need to differentiate this transition.
+
+We take inspiration from~\cite{frances2021learning}, but introduce an alternative approach for computing general policies in multi-agent settings that is simpler.
+The learning problem is cast as a self-supervised classification problem where (1) a pool of features is automatically generated from a uniform grammar applied to the domain without any domain knowledge, and (2) a small subset of features is sought for separating “good” from “bad” state transitions, and goals from non-goals.
+The problems of finding the final features while labeling the transitions as “good” or “bad” are addressed jointly as a single combinatorial optimization task solved with a Weighted Max-SAT solver.
 The approach yields general policies for a number of benchmark domains.
@@
 For instance, if there are known exceptions within the domain.
+
+The domain knowledge entered will come from the grammar used, which depending on the domains can be uniform.
+For instance, in this work we use domains based on grid worlds, which allow us to have a uniform grammar for all of them, having predicates for the value of the cells, and the relative position of some cells to others.
+Once the initial feature pool is automatically generated from a grammar, we do a pre-pruning of these features based on their denotation, without introducing domain knowledge.
+Of course, this pre-pruning is not sound, however we have observed that features with the same denotation often contain the same domain information.
+After pre-pruning the feature pool, a small set of features is selected automatically based on the encoding for representing the policy.
+The encogin guarantee that the number of features selected for representing the policy will be as small and with as little complexity as possible.
+
+The approach is learning a model.
+The general policies obtained are made up of one or more rules, these rules have the form of "if a condition is met in certain features it is good to take actions that change the features in this way".
+This is completely different from the most common approaches, as it is not necessary to have any explicit action for the policy to be defined.
+However, if there is a fixed set of actions the approach is able to take advantage of this fact.
+Moreover, this way of using the features to represent the policy allows us to generalise to larger and more complex instances, since we are capturing the strategy that solves the problem.
+
+In~\cite{frances2021learning}, an \emph{unsolvabel} state is defined as a state in which the agent has lost.
+But in multi-agent games the agent may find himself in a state where he has not lost and yet cannot win in any way if the adversary or adversaries act correctly.
+Therefore, we also make use of the minimax algorithm to extend the meaning of an unsolvable state, ensuring that the agent wins from all states where the policy is defined, regardless of what the other agents do.
+The extension of unsolvable: An state is unsolvabel if some adversary is able to win regardless of what the agent does.
+
+Inspiration has been taken from the article by~\cite{silver2020few} to choose the domains.
+In~\cite{silver2020few} interpretable policies were learned by expanding with expert policies and then inferring the expert policy with the target language.
+In other words, imitation learning was used and the policies were learned in a supervised way.
+In this work we learn policies for the games of~\cite{silver2020few}, such as "two pile nim", "checkmate tactic" or "chase", but in an unsupervised way.
 
@@
 
-\section{Contriution: Generalized Planning in multi-agent settings}
+\section{Contribution: Generalized Planning in multi-agent settings}
 
@@
 One solution is to work with general features (functions) that have well defined values over any state of any possible domain instance, and think of general policies $\pi$ as mappings from feature valuations into abstract actions that denote changes in the feature values~\cite{bandres2018planning}.
-When a transition is taken by the agent the environment or other agent changes state, so when we record the AND/OR graph of states we capture how the environment or the other agent can change each state.
+When a transition is taken by the agent the environment or other agent changes state, so when we record the AND/OR graph of states, capturing how the environment or the other agent can change each state.
 In this work, we use abstract actions as~\cite{frances2021learning}, in addition to the possibility of taking advantage of using an action space fixed for all instances in the domain.
@@
 Where $f$ is a function that has as input a state and as output a numerical value.
-The initial feature pool is produced using the logical description language.
+The initial feature pool is produced using the logical description language, i.e., genereted from a grammar.
 In addition, a parameter is used to determine the maximum complexity of the features.
 Once the initial pool of features is produced, a pruning is performed based on the denotation of each feature with the following philosophy: if two features, $f$ and $f'$ have the same denotation in all states, it is likely that they are capturing the same information of the domain, therefore we keep the simpler of the two features.
-With these features you can basically create abstract states, or representations, the challenge will be to find which ones are useful to represent the strategy that solves the problem.
-After feature pruning, the set of features $f$ that we are left with is $F$, and it is the one that will have the SAT solver as input.
-Based on the encoding the SAT solver will select the features of $F$ needed to represent the policy, trying to minimize the complexity.
+With these features we can basically create abstract states, or representations, the challenge will be to find which ones are useful to represent the strategy that solves the problem.
+After the feature pruning, the set of features $f$ that are left represent $F$, and it is the one that will have the SAT solver as input.
+Based on the encoding the SAT solver will select the features of $F$ needed to represent the policy, trying to minimize the complexity and the number of features used.
 
@@
 A state is \emph{alive} if it is solvable, reachable and not a goal state~\cite{frances-et-al-ijcai2019}.
-We use $T$ to denote the set of all transitions $(s, s')$ in the training sample such that $s$ is alive.
+A state is \emph{unsolvable} if the agent has lost.
+We use $T$ to denote the set of all transitions $(s, a, s')$ in the training sample such that $s$ is alive.
+
+\subsubsection{Extension of unsolvaility}
+
+In some domains the agent can win from any state of the problem except for some specific states where the agent has lost.
+In other more complex domains, there are states where the agent has not lost, however, the success of the agent depends on whether the opponent plays well or not.
+In other words, if the opponent plays correctly the agent has no way to win.
+
+With our approach we want policies that are always able to win, no matter what state the agent is in.
+Therefore, we consider states where the agent can lose no matter what he does as \emph{unsolvable}.
+To classify unsolvable states we use the minimax algorithm.
 
@@
 \subsubsection{Soft Constraints}
+
 \smallpar{C6}
@@
 
-How we arrive at these constrains has to do with the observation of adversarial domains and winning strategies.
+How we arrive at these constrains has to do with the observation of multi-agent domains and winning strategies.
 We observed that the dilemma of adversarial games meant that we were confronted with the fact that decisions were not made by a single agent, and we had to take into account that there were also other agents trying to "win".
@@
 We observed that in many domains the set of actions is fixed for all agents.
-In the paper~\cite{frances2021learning} there were $Good(s, s')$ variables.
+In the paper~\cite{frances2021learning} there were $Good(s, a, s')$ variables.
 But these were not able to take advantage of fixed action sets, so we decided to include the information of the actions in these domains to alleviate scalability problems, for that reason we have variables such as $Good(s, a, s')$.
@@
 
-It was assumend by~\cite{frances2021learning} assumed that it was possible to get from any state of the problem to the objective, without entering dead ends (states where the agent has lost).
+It was assumend by~\cite{frances2021learning} assumed that it was possible to get from any state of the problem to the objective, without entering dead ends (states where the agent can lose, independently of what he does).
 However, in many multi-agent domains there are states where the agent has not lost, but no longer has the possibility of winning in that state no matter what the agent does.
@@
 We then design counterin C2 to ensure that the strategy takes paths that do not fall into cycles by introducing the adversarial factor.
-To introduce the adversarial factor into the strategy we make sure that the number assigned to a state $s$ is greater than all the numbers assigned to the possible $s''$.
+To introduce the adversarial factor into the strategy we make sure that the potential $V$ of the state $s$ is greater than all the potentials $V$ of all the possible $s''$.
 The possible $s''$ are the result of the agents or the environment executing an action $a'$ on $s'$, where $s'$ is the state the agent reaches after executing $a$ on $s$.
-Note that adversaries will often have multiple $a'$ actions to execute on $s'$.
-We then design counterin C2 to ensure that the strategy takes paths that do not fall into cycles by introducing the adversarial factor.
-To introduce the adversarial factor into the strategy we make sure that the number assigned to a state $s$ is greater than all the numbers assigned to the possible $s''$.
-The possible $s''$ are the result of the agents or the environment executing an action $a'$ on $s'$, where $s'$ is the state the agent reaches after executing $a$ on $s$.
-Note that adversaries will often have multiple $a'$ actions to execute on $s'$, which will often result in a different set of $s"$..
+Note that adversaries will often have multiple $a'$ actions to execute on $s'$, which will often result in a different set of $s''$.
 
@@
 
-\subsection{Optimizations}
-
-\paragraph{Non-distinguishability of transitions as an equivalence relation.}
-Any fixed, given pool of features $F$ implicitly defines an equivalence relation where to transitions are
-equivalent iff they cannot be distinguished \emph{by any feature in $F$}.
-If two transitions cannot be distinguished by any feature, then clearly either the policy computed by the SAT solver
-considers all of them as ``good'', or as ``bad''.
-We'll exploit this by using one single SAT variable to denote whether \emph{all transitions in a given equivalence
-class} are good or bad. When exploiting this notion of equivalence (which is implemented as an optional feature of
-the CNF generator), then every mention below to SAT variable $Good(s, s')$ needs to be read as $Good(s_{\star}, s_{\star}')$,
-where $(s_{\star}, s_{\star}')$ is the \emph{representative} transition of the equivalence class to which $(s, s')$ belongs.
-
-\paragraph{``Bad'' transitions.}
-We use \badtx{} to denote the set of transitions that have been determined at preprocessing as necessarily
-\emph{not} good.
-At the moment, this set contains all transitions that go from an alive to an unsolvable state and, if using
-equivalence relations, all those other transitions in whose equivalence class there is some other ``bad'' transition.
-
-\section{Grammar}
-
+%\subsection{Optimizations}
+
+%\paragraph{Non-distinguishability of transitions as an equivalence relation.}
+%Any fixed, given pool of features $F$ implicitly defines an equivalence relation where to transitions are
+%equivalent iff they cannot be distinguished \emph{by any feature in $F$}.
+%If two transitions cannot be distinguished by any feature, then clearly either the policy computed by the SAT solver
+%considers all of them as ``good'', or as ``bad''.
+%We'll exploit this by using one single SAT variable to denote whether \emph{all transitions in a given equivalence
+%class} are good or bad. When exploiting this notion of equivalence (which is implemented as an optional feature of
+%the CNF generator), then every mention below to SAT variable $Good(s, a, s')$ needs to be read as $Good(s_{\star}, s_{\star}')$,
+%where $(s_{\star}, a, s_{\star}')$ is the \emph{representative} transition of the equivalence class to which $(s, a, s')$ belongs.
+
+%\paragraph{``Bad'' transitions.}
+%We use \badtx{} to denote the set of transitions that have been determined at preprocessing as necessarily
+%\emph{not} good.
+%At the moment, this set contains all transitions that go from an alive to an unsolvable state and, if using
+%equivalence relations, all those other transitions in whose equivalence class there is some other ``bad'' transition.
+
+\section{Motivating Example}
+
+We will now consider a grid-world in which the agent has to reach a goal.
+The grid-world is made of cell, organized in rows and columns.
 The sorts used are: $cell$, $row$, $column$ and .
@@
 The same philosophy would apply to the predicates $adjacent\_col(column, column)$ or $adjacent\_row(row, row)$.
+$cell\_has\_v()$ and $adjacent\_row/col()$ represent domain knowledge that needs to be encoded at design time.
+
+\section{Using the algorithm}
+
+In this section we describe the end-to-end process of the steps necessary to use the algorithm~\footnote{The code of our project: ~\url{https://github.com/iOrb/gpl}}.
+To run it we must first have a simulator of the domain in which we can execute an action and see the next state.
+We also have to take into account that we want to expand the whole state space, so we have to know to which states the adveraries can go.
+
+\begin{enumerate}
+  \item First we must decide which predicates we are going to use, e.g., $cell\_has\_v()$ .
+Then we will have to define these predicates programmatically, we have done it with Tarski~\footnote{Tarski is a framework for the specification, modeling and manipulation of AI planning problems.
+Code:~\url{https://github.com/aig-upf/tarski}}.
+This defines our language.
+
+  \item Then we need to be able to transform any state of the problem into a set of atoms taking into account our predicates.
+
+  \item Finally, we define the experiment, introducing the configuration parameters of the simulation environment if any.
+We can also modify the parameters of our approach, for example the maximum complexity of the features, which are generated incrementally based on the defined language.
+And we are ready to execute it, obtain the policy and test it in diferent instances.
+\end{enumerate}
 
@@
 The initial state of the example test instance is taken from the infinite set of possible instances in the domain.
+
+Examples of games in which the learned policies are executed against other agents can be found in the appendix of the article.
 
@@
 execute the action $shoot$.
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-    # m.mm.m # m.mm.m # m.mm.m # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # m.mm.m # m.mm.m # m.mm.. # m.mm.m # m.mm.. # m.mm.. # .m.mm. # .m.mm. # .m.mm. # ..m.mm #
-    # m.mm.m # m.mm.. # m.mm.. # m.mm.. # m.mm.. # m.mm.. # .m.mm. # .m.mm. # .m.m.. # ..m.m. #
-    # ...... # ...... # ...... # m.mm.. # m.mm.. # m.mm.. # .m.mm. # .m.m.. # .m.m.. # ..m.m. #
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # .....A # .....A # .....A # .....A # .....A # ....A. # ....A. # ....A. # ....A. # ....A. # ...
-
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # ..m.mm # ..m.mm # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # ..m.m. # ..m... # ..m.mm # ..m..m # ..m..m # ...... # ...... # ...... # ...... # ...... #
-    # ..m... # ..m... # ..m... # ..m... # ..m... # ..m..m # ..m... # ..m... # ...m.. # ...m.. #
-    # ...... # ...... # ..m... # ..m... # ..m... # ..m... # ..m... # ..m... # ...m.. # ...m.. #
-    # ...... # ...... # ...... # ...... # ...... # ..m... # ..m... # ..m... # ...m.. # ...m.. #
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
-... # ....A. # ....A. # ....A. # ....A. # .....A # .....A # .....A # ....A. # ....A. # ...A.. # ...
-
-    # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... #
-    # ...m.. # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... #
-    # ...m.. # ...m.. # ...m.. # ...... #
-    # ...... # ...m.. # ...... # ...... #
-    # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... #
-    # ...... # ...... # ...... # ...... #
-... # ...A.. # ...A.. # ...A.. # ...A.. #
-\end{Verbatim}
 
@@
 
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
- # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
- # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
- # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
- # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
- # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
- # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
- # t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
- # t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
- # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
- # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
- # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
- # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
- # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
-\end{Verbatim}
-
 \subsection{Delivery}
@@
 
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  p.... # p.... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
-  ..... # .A... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
-  A.... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... # ..... # ..... # ..... #
-  ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..pA. # ...A. # ..... # ..... # ..... #
-  ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ...pA # ....A # ....A #
-\end{Verbatim}
-
 \subsection{Shoot}
@@
 The first rule can also be read as, it is good for the agent to approach the adversary horizontally.
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  # A....... # .A...... # ..A..... # ..A..... # ...A.... # ....A... # ....A... # .....A.. # ......A. #
-  # ........ # ........ # ........ # ........ # ........ # ........ # .....T.. # ......T. # ......T. #
-  # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
-  # .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ........ # ........ # ........ #
-  # ........ # ........ # ........ # .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ...
-
-     # ......A. # .....A.. # .....A.. #
-     # ........ # ........ # ........ #
-     # .....T.. # .....T.. # ........ #
-     # ........ # ........ # ........ #
-  ...# ........ # ........ # ........ #
-
-\end{Verbatim}
 
@@
 
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  .  .  .  .  .  K  .  .  #  .  .  .  .  .  .  .  K  .  .  #
-# .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  Q  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-\end{Verbatim}
-
 \subsection{Checkmate in one with Rook}
@@
 To check that the policy is complete, it is tested on all possible, for each board size $NxM$ where both $N$ and $M$ are numbers no greater than twenty randomly selected.
-
-\subsubsection{Example of Game}
-\begin{Verbatim}[fontsize=\footnotesize]
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  .  .  .  .  .  K  .  k  #  .  .  .  .  .  .  .  K  .  k  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-  # .  .  R  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  R  #
-  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
-\end{Verbatim}
 
@@
 
-\newpage
-
-\subsection{Dealing with real robots}
-
-First it is necessary to have a simulator of the robot's environment discretised.
+%\subsection{Dealing with real robots}
+
+%First it is necessary to have a simulator of the robot's environment discretised.
 The policy would be learned with the algorithm described in the paper without involving the robot.
@@
 
-So, to be able to execute the policies on real robots, it is only necessary to have a simulator and an algorithm to translate the state of the robot into a state executable by the simulator.
-
-For example, with a turtle robot that has to pick up a certain number of packages and take them to a certain place.
-We only need a grid simulator, where the objects "package", "agent" and "destination" exist.
+%So, to be able to execute the policies on real robots, it is only necessary to have a simulator and an algorithm to translate the state of the robot into a state executable by the simulator.
+
+%For example, with a turtle robot that has to pick up a certain number of packages and take them to a certain place.
+We only need a grid sifmulator, where the objects "package", "agent" and "destination" exist.
 The simulator must be able to execute the actions to move the robot, pick and drop.
@@
 
-Of course, you could give the initial state translated to the simulator and have the learned policy execute a sequence of actions up to the goal.
+%Of course, you could give the initial state translated to the simulator and have the learned policy execute a sequence of actions up to the goal.
 But this method makes us more vulnerable to the noise that the real world produces.
@@
 
-Note that for the algorithm to work it must be possible to win from the initial state of the problem no matter what the opponent does.
+Notice that for the algorithm to work it must be possible to win from the initial state of the problem no matter what the opponent does.
 So in domains where the agent has two actions per turn, which are "Space Invader" and "Delivery".
@@
 A requirement for the algorithm to work correctly is that the strategy can be described using the grammar, then in domains where the strategy is very complex it will be necessary to increase the complexity of the language.
-In this paper we propose a method for dealing with adversarial domains, which manages to find policies that beat the adversary from any initial state where this is possible.
+In this paper we propose a method for dealing with multi-agent domains, which manages to find policies that beat the adversary from any initial state where this is possible.
 This approach is a step in the explainability of reinforcement-produced policies, and it is also a step towards having transferable policies that capture the representation of the problem.
@@
 %\subsection{Discussion}
+
+\newpage
+
+\section{Apendix}
+
+Here we show traces of the example domains, in which the learned policy is executed on small instances, against other agents and on larger instances.
+
+Recall that the objects that can be found in the layouts are equivalent to:
+\begin{Verbatim}[fontsize=\footnotesize]
+  A: Agent
+  D: destination
+  T: adversary
+  K: white-king
+  Q: white-queen
+  R: white-rook
+  k: black-king
+  m: martian
+  p: pet
+  t: token
+\end{Verbatim}
+
+\subsection{Space Invaders}
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # m  m  .  m #
+  # m  m  .  m #
+  # .  .  .  . #
+  # .  .  .  . #
+  # .  .  .  . #
+  # .  .  .  . #
+  # .  .  A  . #
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+    # m.mm.m # m.mm.m # m.mm.m # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # m.mm.m # m.mm.m # m.mm.. # m.mm.m # m.mm.. # m.mm.. # .m.mm. # .m.mm. # .m.mm. # ..m.mm #
+    # m.mm.m # m.mm.. # m.mm.. # m.mm.. # m.mm.. # m.mm.. # .m.mm. # .m.mm. # .m.m.. # ..m.m. #
+    # ...... # ...... # ...... # m.mm.. # m.mm.. # m.mm.. # .m.mm. # .m.m.. # .m.m.. # ..m.m. #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # .....A # .....A # .....A # .....A # .....A # ....A. # ....A. # ....A. # ....A. # ....A. # ...
+
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ..m.mm # ..m.mm # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ..m.m. # ..m... # ..m.mm # ..m..m # ..m..m # ...... # ...... # ...... # ...... # ...... #
+    # ..m... # ..m... # ..m... # ..m... # ..m... # ..m..m # ..m... # ..m... # ...m.. # ...m.. #
+    # ...... # ...... # ..m... # ..m... # ..m... # ..m... # ..m... # ..m... # ...m.. # ...m.. #
+    # ...... # ...... # ...... # ...... # ...... # ..m... # ..m... # ..m... # ...m.. # ...m.. #
+    # ...... # ...... # ...... # .ee..... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
+... # ....A. # ....A. # ....A. # ....A. # .....A # .....A # .....A # ....A. # ....A. # ...A.. # ...
+
+    # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+    # ...m.. # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+    # ...m.. # ...m.. # ...m.. # ...... #
+    # ...... # ...m.. # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+    # ...... # ...... # ...... # ...... #
+... # ...A.. # ...A.. # ...A.. # ...A.. #
+\end{Verbatim}
+
+\subsection{Nim}
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  . #
+  # t  . #
+  # t  . #
+  # t  t #
+  # t  t #
+  # t  t #
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+ # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+ # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
+\end{Verbatim}
+
+\subsection{Delivery}
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  .  .  .  .  A #
+  # .  D  .  .  .  . #
+  # .  .  .  .  .  . #
+  # .  .  .  .  .  . #
+  # .  .  p  .  .  . #
+  # .  .  .  .  .  . #
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  p.... # p.... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
+  ..... # .A... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
+  A.... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... # ..... # ..... # ..... #
+  ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..pA. # ...A. # ..... # ..... # ..... #
+  ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ...pA # ....A # ....A #
+\end{Verbatim}
+
+\subsection{Shoot}
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # . . . . #
+  # A . . . #
+  # . . T . #
+  # . . . . #
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # A....... # .A...... # ..A..... # ..A..... # ...A.... # ....A... # ....A... # .....A.. # ......A. #
+  # ........ # ........ # ........ # ........ # ........ # ........ # .....T.. # ......T. # ......T. #
+  # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ # ........ #
+  # .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ........ # ........ # ........ #
+  # ........ # ........ # ........ # .....T.. # .....T.. # .....T.. # ........ # ........ # ........ # ...
+
+     # ......A. # .....A.. # .....A.. #
+     # ........ # ........ # ........ #
+     # .....T.. # .....T.. # ........ #
+     # ........ # ........ # ........ #
+  ...# ........ # ........ # ........ #
+
+\end{Verbatim}
+
+\subsection{Checkmate in one with Queen}
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  k  .  .  . #
+  # .  .  .  .  . #
+  # .  K  .  .  . #
+  # .  .  .  .  . #
+  # .  .  .  .  Q #
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  K  .  .  #  .  .  .  .  .  .  .  K  .  .  #
+# .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  Q  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+# .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+\end{Verbatim}
+
+\subsection{Checkmate in one with Rook}
+
+\subsubsection{Training instances}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  k  .  .  . #
+  # .  .  .  .  . #
+  # .  K  .  .  . #
+  # .  .  .  .  . #
+  # .  .  .  .  R #
+\end{Verbatim}
+
+\subsubsection{Example of Game}
+\begin{Verbatim}[fontsize=\footnotesize]
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  K  .  k  #  .  .  .  .  .  .  .  K  .  k  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+  # .  .  R  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  R  #
+  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
+\end{Verbatim}
+
+\newpage
 
